---
title: "Matching BHRe episodes to CNR laboratory records"
subtitle: "A step-by-step linkage report (facility name required)"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    theme: flatly
    df_print: paged
params:
  tol_months: 6
  name_sim_threshold: 0.90
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.width = 7, fig.height = 4)
library(here)
knitr::opts_knit$set(root.dir = here::here())
library(dplyr); library(tidyr); library(stringr); library(purrr)
library(lubridate); library(stringi); library(readr); library(readxl)
library(ggplot2); library(knitr); library(scales); library(stringdist)
```

# What this report does and what changed

We link **BHRe episodes** (one row per reported hospital episode) to **CNR
records** (one row per bacterial strain sequenced by the reference lab). There is
no shared ID, so we match on shared information and label every kept match with a
confidence level.

This version is deliberately **stricter about the hospital**, because earlier
matches sometimes paired an episode with a strain from a clearly different
facility. The key change: **a match now REQUIRES the hospital to agree.** A pair
is only kept if the hospital identity lines up — either the hospital **name
matches**, or the hospital **name + town** gives a strong fuzzy match to the
CNR's facility name. Matching on date and mechanism alone is no longer enough.

Three rules changed:

1. **Who is included.** An episode is considered only if it was referred to a CNR
   (`cnr_referral` is not missing) *or* has a referral date, **and** we can find
   its hospital name (via the FINESS lookup).
2. **Time window widened** to ±`r params$tol_months` months (referral vs CNR
   receipt dates can be far apart).
3. **Hospital is mandatory.** Exact name match, or a high-quality fuzzy match of
   name + town against the CNR facility name. Mechanism must still agree too.

# Load the data

```{r load}
nodes <- readRDS(here("Datasets","Cleaned Model Input Data","node_attributes_enriched.RDS")) %>%
  mutate(finess_geo = as.numeric(finess_geo)) %>%
  filter(!is.na(finess_geo))

cnr  <- read_excel(here("Datasets","Output Data",
                        "CNR_2023_2024_DEIDENTIFIED_shareable_EN_clean.xlsx"))

bhre <- read.csv(here("Datasets","Sante Publique","Cleaned","bhre_2024_hosp.csv"))
bhre <- bhre[, 1:84]
```

```{r helpers, echo=FALSE}
tol_months <- params$tol_months
sim_thr    <- params$name_sim_threshold

ym_int        <- function(y, m) as.integer(y) * 12L + as.integer(m)
strip_accents <- function(x) stri_trans_general(as.character(x), "Latin-ASCII")
has_overlap   <- function(a, b) length(intersect(a, b)) > 0
fin9 <- function(x) str_pad(str_extract(str_replace(as.character(x), "\\.0$", ""),
                                        "[0-9]+"), 9, pad = "0")

# --- mechanism family ---
oxa48_like <- c("OXA-48","OXA-48-LIKE","OXA-181","OXA-204","OXA-244","OXA-162",
                "OXA-232","OXA-484","OXA-163","OXA-245","OXA-370","OXA-405")
carb_family_one <- function(x) {
  x <- toupper(trimws(x))
  if (is.na(x) || x %in% c("", "-")) return(NA_character_)
  if (x %in% oxa48_like || str_starts(x, "OXA-48")) return("OXA48")
  for (p in c("KPC","NDM","VIM","IMP","IMI","GES")) if (str_starts(x, p)) return(p)
  NA_character_
}
families_of <- function(x) unique(na.omit(map_chr(str_trim(str_split(x, "\\+")[[1]]),
                                                  carb_family_one)))
variants_of <- function(x) unique(toupper(str_trim(str_split(x, "\\+")[[1]])))

# --- hospital-name matching ---
# Distinctive tokens = words of length >= 4, minus generic facility words.
name_stop <- c("CH","CHU","CHR","CHG","CHIC","CHS","GH","GHT","HOP","HOPITAL","HOPITAUX",
  "CENTRE","HOSPITALIER","HOSPITALIERE","CLINIQUE","POLYCLINIQUE","GROUPE","GROUPEMENT",
  "SAINT","SAINTE","EHPAD","POLE","UNITE","SERVICE")
norm_str <- function(x) str_squish(str_replace_all(toupper(strip_accents(x)), "[^A-Z0-9 ]", " "))
dtok <- function(x) map(str_split(norm_str(x), " "),
                        ~ unique(.x[nchar(.x) >= 4 & !.x %in% name_stop]))

# Token-set similarity (fuzzywuzzy-style): high when one name's words are a
# subset of the other's, and tolerant of small spelling differences.
tss <- function(a, b) {
  if (length(a) == 0 || length(b) == 0) return(0)
  inter <- intersect(a, b)
  si <- paste(sort(inter), collapse = " ")
  sa <- paste(sort(union(inter, setdiff(a, b))), collapse = " ")
  sb <- paste(sort(union(inter, setdiff(b, a))), collapse = " ")
  cand <- stringsim(sa, sb, method = "jw", p = 0.1)
  if (nchar(si) > 0) cand <- c(cand, stringsim(si, sa, method = "jw", p = 0.1),
                                      stringsim(si, sb, method = "jw", p = 0.1))
  max(cand)
}

mech_cols <- paste0("resistance_mechanism_", c("1_1","1_2","2_1","2_2","3_1","3_2"))
```

# Step 1 — Attach hospital name and town via FINESS

```{r attach}
place_lu <- nodes %>%
  transmute(fin = fin9(finess_geo), facility_name_capact, city) %>%
  filter(!is.na(fin)) %>% distinct(fin, .keep_all = TRUE)

bhre <- bhre %>%
  mutate(fin = fin9(facility_finess_code)) %>%
  left_join(place_lu, by = "fin")
```

# Step 2 — Decide which episodes to include

Keep an episode only if it shows evidence of a CNR referral (**a referral lab
recorded, or a referral date**) **and** we found its hospital name. The time
anchor is the **referral date**; if that is missing we fall back to the
submission date so referred episodes are not lost.

```{r population}
n_total <- nrow(bhre)
bhre <- bhre %>%
  mutate(ref_date = coalesce(as.Date(cnr_referral_date), as.Date(form_issue_date)))

included <- bhre %>%
  filter((!is.na(cnr_referral) | !is.na(cnr_referral_date)) & !is.na(facility_name_capact))
n_included <- n_distinct(included$ehesp_id)
```

Of `r n_total` episodes, **`r n_included`** are included (referred to a CNR, and a
hospital name was found).

> *Note:* to restrict to the EPC carbapenemase CNR only, add
> `& cnr_referral == EPC_LAB` to the filter above. Here we keep all referred
> episodes; the mechanism and hospital rules below still prevent cross-lab
> mismatches.

# Step 3 — Build the clues (BHRe side)

```{r bhre-keys}
bhre_prep <- included %>%
  mutate(
    ref_ym    = ym_int(year(ref_date), month(ref_date)),
    bhre_dept = str_sub(fin, 1, 2),
    bhre_mech = pmap_chr(select(., all_of(mech_cols)),
                         ~ paste(sort(unique(toupper(na.omit(c(...))))), collapse = " | ")),
    bhre_var  = pmap(select(., all_of(mech_cols)), ~ toupper(na.omit(unique(c(...))))),
    bhre_fam  = map(bhre_var, ~ unique(na.omit(map_chr(.x, carb_family_one)))),
    name_ft   = dtok(facility_name_capact),                     # hospital-name words
    town_ft   = dtok(city),                                     # town words
    fac_ft    = map2(name_ft, town_ft, union),                  # name + town words
    name_norm = norm_str(facility_name_capact)
  ) %>%
  filter(!is.na(ref_ym), lengths(bhre_fam) > 0)
n_keyed <- n_distinct(bhre_prep$ehesp_id)
```

# Step 4 — Build the clues (CNR side)

```{r cnr-keys}
cnr_prep <- cnr %>%
  filter(!is_environment %in% TRUE) %>%
  mutate(
    cnr_ym   = ym_int(2000L + as.integer(sample_year), as.integer(sample_month)),
    cnr_dept = coalesce(str_sub(str_extract(as.character(department_code), "[0-9]+"), 1, 2),
                        str_sub(str_extract(as.character(zip_code_facility), "[0-9]+"), 1, 2)),
    cnr_ft    = dtok(facility_name),
    cnr_name_norm = norm_str(facility_name),
    cnr_var  = map(sequencing, variants_of),
    family   = map(sequencing, families_of)
  ) %>%
  filter(lengths(family) > 0, !is.na(cnr_ym)) %>%
  unnest(family)
```

# Step 5 — Match: mechanism + time + **hospital (required)**

A pair must clear **all three** gates:

1. **Same mechanism family.**
2. **Referral month within ±`r tol_months` months** of the CNR receipt month.
3. **Hospital agrees** — the CNR facility name shares at least one distinctive
   word with the BHRe hospital name or town. (This is the mandatory facility gate
   that removes the earlier false matches.)

Among the pairs that pass, we grade the hospital agreement:

- **High** — the hospital **name** matched (exactly, or a strong fuzzy match,
  similarity ≥ `r sim_thr`), i.e. the actual hospital lines up.
- **Medium** — only the **town** matched (same locality, but the hospital name
  itself did not line up), so it is plausibly the same hospital but less certain.

An exact mechanism **variant** match is also recorded (it strengthens a match).

```{r join-score}
bhre_keyed <- bhre_prep %>%
  mutate(ym = map(ref_ym, ~ seq(.x - tol_months, .x + tol_months))) %>%
  select(ehesp_id, ref_date, ref_ym, bhre_dept, city, facility_name_capact,
         bhre_mech, bhre_var, name_ft, town_ft, fac_ft, name_norm,
         family = bhre_fam, ym) %>%
  unnest(family) %>% unnest(ym)

candidates <- bhre_keyed %>%
  inner_join(cnr_prep, by = c("family", "ym" = "cnr_ym"),
             relationship = "many-to-many") %>%
  # GATE 3: hospital must share at least one distinctive word (name or town)
  mutate(hospital_shared = map2_lgl(fac_ft, cnr_ft, has_overlap)) %>%
  filter(hospital_shared) %>%
  mutate(
    month_exact   = ym == ref_ym,
    variant_exact = map2_lgl(bhre_var, cnr_var, has_overlap),
    dept_match    = !is.na(bhre_dept) & !is.na(cnr_dept) & bhre_dept == cnr_dept,
    name_hit      = map2_lgl(name_ft, cnr_ft, has_overlap),   # matched on hospital NAME
    town_hit      = map2_lgl(town_ft, cnr_ft, has_overlap),   # matched on TOWN
    name_exact    = nzchar(name_norm) & name_norm == cnr_name_norm,
    name_sim      = map2_dbl(fac_ft, cnr_ft, tss),
    confidence = if_else(name_exact | (name_hit & name_sim >= sim_thr) | name_sim >= 0.95,
                         "High", "Medium") %>% factor(levels = c("High","Medium")),
    matched_on = if_else(name_hit, "hospital name", "town")
  )
```

# Step 6 — Keep the best hospital match per episode

For each episode we keep its strongest pairs (name matches beat town-only
matches; variant agreement breaks ties). An episode may still link to several CNR
strains from that hospital — this is expected and kept.

```{r best}
bhre_cnr_matches <- candidates %>%
  mutate(priority = 4L*(confidence == "High") + 2L*variant_exact + 1L*name_hit) %>%
  group_by(ehesp_id) %>% filter(priority == max(priority)) %>% ungroup() %>%
  transmute(ehesp_id, patient_id, specimen_id, confidence, matched_on,
            name_sim = round(name_sim, 3), variant_exact, dept_match, month_exact,
            ref_date, family, bhre_mech, cnr_sequencing = sequencing,
            bhre_facility_name = facility_name_capact, cnr_facility_name = facility_name,
            bhre_city = city, bhre_dept, cnr_dept,
            cnr_sample_month = sample_month, cnr_sample_year = sample_year,
            cnr_species = species)

episode_methods <- bhre_cnr_matches %>%
  group_by(ehesp_id) %>%
  summarise(confidence = first(confidence),
            matched_on = if_else(any(matched_on == "hospital name"), "hospital name", "town"),
            variant_agrees = any(variant_exact),
            n_cnr_specimens = n_distinct(specimen_id), .groups = "drop")
```

# Results

## Episodes through the pipeline

```{r r1}
n_matched <- n_distinct(bhre_cnr_matches$ehesp_id)
tibble(step = c("Episodes in file",
                "Included (referred + hospital name found)",
                "Ready to match (had a date and a known mechanism)",
                "Matched (hospital + mechanism + time all agree)",
                "   - High (hospital name matched)",
                "   - Medium (town matched only)"),
       episodes = c(n_total, n_included, n_keyed, n_matched,
                    sum(episode_methods$confidence == "High"),
                    sum(episode_methods$confidence == "Medium"))) %>%
  kable(caption = "Episode counts")
```

## What the match was based on

```{r r2}
episode_methods %>% count(matched_on, confidence) %>%
  pivot_wider(names_from = confidence, values_from = n, values_fill = 0) %>%
  kable(caption = "Matched on hospital name vs town, by confidence (episodes)")
```

```{r r2plot, echo=FALSE}
episode_methods %>% count(matched_on, confidence) %>%
  ggplot(aes(matched_on, n, fill = confidence)) +
  geom_col() +
  labs(x = NULL, y = "episodes", fill = NULL,
       title = "Matches by hospital clue and confidence") +
  theme_minimal(base_size = 12)
```

## Mechanism variant agreement

```{r r3}
tibble(measure = c("Matched episodes",
                   "   of which exact mechanism variant also agrees"),
       n = c(n_matched, sum(episode_methods$variant_agrees))) %>%
  kable(caption = "How often the exact variant matched too")
```

## One episode can match several strains

```{r r4}
tibble(measure = c("Episodes matching exactly one CNR strain",
                   "Episodes matching more than one CNR strain",
                   "Different CNR strains linked",
                   "Total episode-strain pairs kept",
                   "Typical (median) strains per episode"),
       value = c(sum(episode_methods$n_cnr_specimens == 1),
                 sum(episode_methods$n_cnr_specimens > 1),
                 n_distinct(bhre_cnr_matches$specimen_id),
                 nrow(bhre_cnr_matches),
                 median(episode_methods$n_cnr_specimens))) %>%
  kable(caption = "Match multiplicity (expected, not an error)")
```

## Sample of High-confidence matches

```{r r5}
bhre_cnr_matches %>% filter(confidence == "High") %>%
  select(ref_date, bhre_facility_name, cnr_facility_name, bhre_city, name_sim,
         family, bhre_mech, cnr_sequencing) %>%
  head(100)
```

# Save the results

```{r write, eval=FALSE}
write_csv(bhre_cnr_matches, here("Datasets","Output Data","bhre_cnr_matches.csv"))
write_csv(episode_methods,  here("Datasets","Output Data","bhre_cnr_episode_methods.csv"))
```

# Things to keep in mind

- The hospital is now a **hard requirement**, so matches on date + mechanism alone
  (the previous source of false pairs) are gone. Everything kept shares a real
  hospital-name or town word with the CNR record.
- **High** means the hospital *name* lined up; **Medium** means only the *town*
  did — two different hospitals in the same town could in principle match at
  Medium, so treat Medium as "same locality, probably same hospital".
- The ±`r tol_months`-month window is wide, so an episode naturally picks up
  several strains from its hospital across that period. Narrow `params$tol_months`
  if you want tighter timing.
- `params$name_sim_threshold` (currently `r sim_thr`) controls how close a fuzzy
  name match must be. Raise it toward 1 for even stricter name matching.
  
  
  
  Sampling type 
  Microorganism
  Date
  
  What we need from CNR is the MLST
  
