---
title: "ARCANE — AMR Transmissibility Calibration"
subtitle: "Within-Hospital Beta Estimation via Steady-State Prevalence"
author: "MESuRS/Cnam"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  powerpoint_presentation:
    slide_level: 2
    fig_width: 10
    fig_height: 5.2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, dpi=150)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
library(knitr)
```

```{r load-data}
LOCAL_ROOT <- "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/calibration_jobs"
RDS_FILE   <- file.path(LOCAL_ROOT, "Outputs", "prevalence", "local", "results_local.rds")

if (!file.exists(RDS_FILE)) stop("Run optim_prevalence_local.R first.\nExpected: ", RDS_FILE)

res          <- readRDS(RDS_FILE)
scalar_df    <- res$scalar_df
type_df      <- res$type_df
beta_summary <- res$beta_summary
amr_mapping  <- res$amr_mapping

# AMR long targets for reference lines
amr_long <- tribble(
  ~pathogen,  ~prev_low, ~prev_mid, ~prev_high,
  "MRSA",      0.010,     0.115,     0.250,
  "VRE",       0.005,     0.080,     0.180,
  "ESBL-E",    0.020,     0.120,     0.300,
  "CRE",       0.002,     0.030,     0.100,
  "CRAB",      0.010,     0.070,     0.200
) %>%
  pivot_longer(starts_with("prev_"),
               names_to="tier", names_prefix="prev_",
               values_to="target_prevalence") %>%
  mutate(tier = factor(tier, c("low","mid","high"),
                        labels = c("Low","Mid","High")))

NAVY  <- "0D3B66"
TEAL  <- "1A7A8A"
GOLD  <- "F4A623"
tier_pal <- c(Low="#009E73", Mid="#E69F00", High="#D55E00")

type_pal <- c(
  "MCO"="#0057B8","SSR"="#C1392B","MCO/SSR"="#9B1D8A",
  "PSY"="#F5A623","HAD"="#00B4D8","Unknown"="#555555"
)

theme_ppt <- function(base_size=14) {
  theme_bw(base_size=base_size) +
    theme(plot.title       = element_text(face="bold", size=base_size+1),
          plot.subtitle    = element_text(colour="grey40", size=base_size-1),
          panel.grid.minor = element_blank(),
          legend.position  = "right",
          strip.background = element_rect(fill="grey93"),
          strip.text       = element_text(face="bold"))
}
```

# Overview

## What we calibrated

- **Model:** Stochastic SIS metapopulation on the PMSI inter-hospital transfer network
- **Parameter:** Within-hospital transmission rate beta (per day)
- **Method:** Grid search — run model to steady state, measure endemic prevalence
- **Beta grid:** `r sprintf("%.3f", min(scalar_df$beta_within))` to `r sprintf("%.3f", max(scalar_df$beta_within))` (`r length(unique(scalar_df$beta_within))` values)
- **Replicates:** `r max(scalar_df$rep_id)` per beta value
- **Run length:** `r res$params$MAX_DAYS` days (always run to end)
- **Steady state:** CV of daily prevalence < 10% in last `r res$params$SS_WINDOW` days for >= 80% of hospitals

---

**Targets:** ECDC EARS-Net 2022 — three tiers (Low / Mid / High) for 5 AMR pathogens

| Pathogen | Low | Mid | High |
|---|---|---|---|
| MRSA | 1% | 11.5% | 25% |
| VRE | 0.5% | 8% | 18% |
| ESBL-E | 2% | 12% | 30% |
| CRE | 0.2% | 3% | 10% |
| CRAB | 1% | 7% | 20% |

# Calibration Quality

## Steady-state achievement by beta

```{r ss-rate, fig.height=5}
beta_summary %>%
  ggplot(aes(x=beta_within, y=prop_ss*100, fill=prop_ss)) +
  geom_col(width=diff(range(beta_summary$beta_within)) /
             length(unique(beta_summary$beta_within)) * 0.8) +
  geom_hline(yintercept=80, linetype="dashed", colour="#e74c3c",
             linewidth=0.9) +
  geom_text(aes(label=paste0(round(prop_ss*100), "%")),
            vjust=-0.4, size=3.5) +
  scale_fill_gradient(low="#aed6f1", high="#1a5276", guide="none") +
  scale_x_continuous(labels=function(x) sprintf("%.3f",x)) +
  scale_y_continuous(limits=c(0,112), expand=expansion(mult=c(0,0))) +
  labs(title="% of replicates reaching steady state by beta",
       subtitle="Dashed = 80% threshold. Higher beta reaches SS more consistently.",
       x="beta (per day)", y="% reaching steady state") +
  theme_ppt() +
  theme(axis.text.x=element_text(angle=45, hjust=1))
```

## Prevalence at end of simulation

```{r prev-distribution, fig.height=5}
scalar_df %>%
  mutate(beta_label=sprintf("%.3f", beta_within)) %>%
  ggplot(aes(x=reorder(beta_label, beta_within),
             y=overall_prevalence*100)) +
  geom_boxplot(fill="#aed6f1", colour="#1a5276",
               width=0.6, outlier.shape=21, outlier.size=1.5) +
  scale_y_continuous(labels=function(x) paste0(x,"%")) +
  labs(title="Distribution of network-wide prevalence across replicates",
       subtitle="Box = IQR across replicates | Each box = one beta value",
       x="beta (per day)", y="Overall prevalence (%)") +
  theme_ppt() +
  theme(axis.text.x=element_text(angle=45, hjust=1))
```

# Beta-Prevalence Relationship

## How beta drives endemic prevalence

```{r beta-prev-curve, fig.height=5}
ggplot(beta_summary, aes(x=beta_within)) +
  geom_ribbon(aes(ymin=prev_q25*100, ymax=prev_q75*100),
              fill="#56B4E9", alpha=0.3) +
  geom_line(aes(y=prev_median*100), colour="#0072B2",
            linewidth=1.3) +
  geom_point(aes(y=prev_median*100), colour="#0072B2", size=3) +
  geom_hline(data=amr_long %>% filter(pathogen=="ESBL-E"),
             aes(yintercept=target_prevalence*100, colour=tier),
             linetype="dashed", linewidth=1.0) +
  scale_colour_manual(values=tier_pal, name="ESBL-E tier") +
  scale_x_continuous(labels=function(x) sprintf("%.3f",x)) +
  scale_y_continuous(labels=function(x) paste0(x,"%")) +
  labs(title="Beta vs steady-state prevalence",
       subtitle="Median +/- IQR | Dashed = ESBL-E Low/Mid/High targets",
       x="beta (per day)", y="Network prevalence (%)") +
  theme_ppt() +
  theme(axis.text.x=element_text(angle=45, hjust=1))
```

## Nationwide incidence by beta

```{r incidence-curve, fig.height=5}
ggplot(beta_summary, aes(x=beta_within, y=inc_median)) +
  geom_area(fill="#f0b27a", alpha=0.4) +
  geom_line(colour="#e67e22", linewidth=1.3) +
  geom_point(colour="#e67e22", size=3) +
  geom_text(aes(label=round(inc_median,2)), vjust=-0.7, size=3.3) +
  scale_x_continuous(labels=function(x) sprintf("%.3f",x)) +
  scale_y_continuous(expand=expansion(mult=c(0,0.2))) +
  labs(title="Nationwide incidence by beta",
       subtitle=paste0("Median across replicates | ", res$params$INC_WINDOW,
                        "-day lookback"),
       x="beta (per day)",
       y="Incidence (per 1,000 bed-days)") +
  theme_ppt() +
  theme(axis.text.x=element_text(angle=45, hjust=1))
```

## Prevalence trajectories across all betas

```{r prev-heatmap, fig.height=5}
# One row per rep, visualised as a heatmap of prevalence by beta
scalar_df %>%
  mutate(beta_label=sprintf("%.3f", beta_within)) %>%
  ggplot(aes(x=reorder(beta_label, beta_within),
             y=factor(rep_id), fill=overall_prevalence*100)) +
  geom_tile(colour="white", linewidth=0.3) +
  geom_text(aes(label=round(overall_prevalence*100, 1)),
            size=2.4, colour="white") +
  scale_fill_gradientn(
    colours=c("#eaf2ff","#2980b9","#1a5276","#0d2d4d"),
    name="Prevalence\n(%)") +
  labs(title="Steady-state prevalence — each cell is one replicate",
       subtitle="Darker = higher endemic prevalence | Horizontal = rep variation",
       x="beta (per day)", y="Replicate") +
  theme_ppt(12) +
  theme(axis.text.x=element_text(angle=45, hjust=1),
        panel.grid=element_blank())
```

## Facility-type incidence by beta

```{r type-incidence, fig.height=5.5}
type_df %>%
  group_by(beta_within, type) %>%
  summarise(inc_med=median(inc_1000, na.rm=TRUE), .groups="drop") %>%
  mutate(beta_label=sprintf("%.3f", beta_within)) %>%
  ggplot(aes(x=reorder(beta_label, beta_within),
             y=inc_med, colour=type, group=type)) +
  geom_line(linewidth=1.1) +
  geom_point(size=2.5) +
  scale_colour_manual(values=type_pal, na.value="#555555",
                      name="Facility type") +
  scale_y_continuous(expand=expansion(mult=c(0,0.1))) +
  labs(title="Facility-type incidence across the beta grid",
       subtitle="Median across replicates | per 1,000 bed-days",
       x="beta (per day)", y="Incidence (per 1,000 bed-days)") +
  theme_ppt(12) +
  theme(axis.text.x=element_text(angle=45, hjust=1),
        legend.position="right")
```

# AMR Tier Mapping

## Which beta hits which pathogen prevalence?

```{r amr-heatmap, fig.height=5}
amr_mapping %>%
  mutate(
    label=sprintf("b=%.4f\n%.1f%%", beta_within, prev_median*100),
    fit_col=case_when(
      fit=="Excellent" ~ "#1a9641",
      fit=="Good"      ~ "#a6d96a",
      fit=="Fair"      ~ "#fdae61",
      TRUE             ~ "#d73027"
    )
  ) %>%
  ggplot(aes(x=tier,
             y=reorder(pathogen, -beta_within),
             fill=prev_median*100)) +
  geom_tile(colour="white", linewidth=1.5) +
  geom_text(aes(label=label), size=3.8, colour="white", fontface="bold") +
  scale_fill_gradientn(
    colours=c("#009E73","#E69F00","#D55E00"),
    name="Simulated\nprevalence (%)") +
  scale_x_discrete(position="top") +
  labs(title="Best-fit beta per AMR pathogen and prevalence tier",
       subtitle="Values show: recommended beta (top), achieved prevalence (bottom)",
       x="Prevalence tier", y=NULL) +
  theme_minimal(base_size=14) +
  theme(panel.grid=element_blank(),
        plot.title=element_text(face="bold"),
        axis.text.y=element_text(face="italic", size=13))
```

## Recommended beta values — full table

```{r amr-table}
amr_mapping %>%
  select(pathogen, tier, target_prevalence, beta_within,
         prev_median, inc_median, fit) %>%
  mutate(
    target_prevalence = paste0(round(target_prevalence*100, 1), "%"),
    prev_median       = paste0(round(prev_median*100, 1), "%"),
    beta_within       = formatC(beta_within, format="e", digits=3),
    inc_median        = round(inc_median, 3)
  ) %>%
  arrange(pathogen, tier) %>%
  kable(col.names=c("Pathogen","Tier","Target prev.",
                     "Recommended beta","Achieved prev.",
                     "Incidence","Fit"),
        align=c("l","l","r","r","r","r","c"))
```

# Recommended Betas

## Low-transmissibility scenario (VRE / CRE range)

```{r low-betas}
low_betas <- amr_mapping %>%
  filter(tier=="Low") %>%
  arrange(pathogen) %>%
  select(pathogen, beta_within, prev_median, inc_median, fit)

low_betas %>%
  mutate(beta_within=formatC(beta_within, format="e", digits=3),
         prev_median=paste0(round(prev_median*100,1),"%"),
         inc_median=round(inc_median,3)) %>%
  kable(col.names=c("Pathogen","Beta","Achieved prevalence",
                     "Incidence (per 1k bd)","Fit"),
        align=c("l","r","r","r","c"),
        caption="Low-tier betas: representing pathogens with low endemic burden")
```

Beta range: **`r formatC(min(low_betas$beta_within), format='e', digits=2)`** to **`r formatC(max(low_betas$beta_within), format='e', digits=2)`**

## Mid-transmissibility scenario (MRSA / ESBL-E range)

```{r mid-betas}
mid_betas <- amr_mapping %>%
  filter(tier=="Mid") %>%
  arrange(pathogen) %>%
  select(pathogen, beta_within, prev_median, inc_median, fit)

mid_betas %>%
  mutate(beta_within=formatC(beta_within, format="e", digits=3),
         prev_median=paste0(round(prev_median*100,1),"%"),
         inc_median=round(inc_median,3)) %>%
  kable(col.names=c("Pathogen","Beta","Achieved prevalence",
                     "Incidence (per 1k bd)","Fit"),
        align=c("l","r","r","r","c"),
        caption="Mid-tier betas: moderate endemic burden pathogens")
```

Beta range: **`r formatC(min(mid_betas$beta_within), format='e', digits=2)`** to **`r formatC(max(mid_betas$beta_within), format='e', digits=2)`**

## High-transmissibility scenario (MRSA / ESBL-E high range)

```{r high-betas}
high_betas <- amr_mapping %>%
  filter(tier=="High") %>%
  arrange(pathogen) %>%
  select(pathogen, beta_within, prev_median, inc_median, fit)

high_betas %>%
  mutate(beta_within=formatC(beta_within, format="e", digits=3),
         prev_median=paste0(round(prev_median*100,1),"%"),
         inc_median=round(inc_median,3)) %>%
  kable(col.names=c("Pathogen","Beta","Achieved prevalence",
                     "Incidence (per 1k bd)","Fit"),
        align=c("l","r","r","r","c"),
        caption="High-tier betas: high endemic burden pathogens")
```

Beta range: **`r formatC(min(high_betas$beta_within), format='e', digits=2)`** to **`r formatC(max(high_betas$beta_within), format='e', digits=2)`**

## Summary: beta ranges for seeding study

```{r summary-betas, fig.height=4.5}
amr_mapping %>%
  ggplot(aes(x=reorder(pathogen, beta_within),
             y=beta_within, colour=tier, shape=tier)) +
  geom_point(size=5, alpha=0.9) +
  geom_line(aes(group=tier), linewidth=0.8, alpha=0.6) +
  scale_colour_manual(values=tier_pal, name="Tier") +
  scale_shape_manual(values=c(Low=15, Mid=17, High=19), name="Tier") +
  scale_y_continuous(labels=scientific) +
  coord_flip() +
  labs(title="Recommended beta values by pathogen and tier",
       subtitle="Use these as beta inputs for the seeding simulation study",
       x=NULL, y="beta (per day)") +
  theme_ppt() +
  theme(legend.position="right")
```

# Next Steps

## From calibration to seeding study

- **Calibrated beta values** provide the transmission input for the ARCANE seeding study
- **Low / Mid / High scenarios** represent plausible ranges across AMR pathogens
- **Next:** seed a novel ARB into each candidate introduction facility under each beta scenario and track spread across the French hospital transfer network

---

**Three seeding simulation arms:**

1. **Low beta** (pi_vec = 0.001, N_seed = 5) — conservative spread, high extinction probability
2. **Mid beta** (pi_vec = 0.001, N_seed = 5) — moderate spread, some facilities sustain transmission
3. **High beta** (pi_vec = 0.001, N_seed = 5) — substantial spread, network-wide dissemination risk

Seed locations tested: highest in-degree, highest out-degree, highest betweenness, largest hospital, largest outgoing transfers, random MCO / SSR / MCO-SSR

*`r format(Sys.time(), "%B %Y")` | ARCANE Project — Task 4.3 | MESuRS/Cnam*
