---
title: "Matching BHRe episodes to CNR laboratory records"
subtitle: "A step-by-step linkage report"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    theme: flatly
    df_print: paged
params:
  tol_months: 1
  date_fallback_form_issue: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.width = 7, fig.height = 4)
library(here)
knitr::opts_knit$set(root.dir = here::here())   # run from the project root, not this file's folder
library(dplyr); library(tidyr); library(stringr); library(purrr)
library(lubridate); library(stringi); library(readr); library(readxl)
library(ggplot2); library(knitr); library(scales)
```

# What this report does

We have two separate datasets that describe the same real-world events from two
angles, but they share **no common ID number**:

- **BHRe episodes** — each row is a hospital *episode* reported to the national
  surveillance system (e-SIN). It tells us the hospital, the dates, the bacteria
  and its resistance mechanism, and whether the strain was sent to a national
  reference laboratory.
- **CNR records** — each row is a single *bacterial strain* that a hospital sent
  to the reference laboratory (CNR), where it was sequenced in detail.

Our goal is to figure out, for each BHRe episode, **which CNR strain(s) it
corresponds to**. Because there is no shared ID, we match on the information the
two datasets *do* have in common — when the strain was sent, what resistance
mechanism it has, and which hospital it came from. Since no single clue is
perfect, every match we keep is labelled with a **confidence level** (High or
Medium; weak "Low" matches are thrown away).

# Load the data

Three files are read in. `nodes` is a reference table that lets us look up a
hospital's **name and town** from its FINESS code (the BHRe episode file itself
does not contain the hospital name).

```{r load}
nodes <- readRDS(here("Datasets","Cleaned Model Input Data","node_attributes_enriched.RDS")) %>%
  mutate(finess_geo = as.numeric(finess_geo)) %>%
  filter(!is.na(finess_geo))

cnr  <- read_excel(here("Datasets","Output Data",
                        "CNR_2023_2024_DEIDENTIFIED_shareable_EN_clean.xlsx"))

bhre <- read.csv(here("Datasets","Sante Publique","Cleaned","bhre_2024_hosp.csv"))
bhre <- bhre[, 1:84] 



# keep only the original BHRe episode columns
```

```{r helpers, echo=FALSE}
#Months Tolerance
tol_months <- params$tol_months
EPC_LAB <- "CNR des ent\u00e9robact\u00e9ries productrices de carbap\u00e9n\u00e8mases (EPC) au Kremlin-Bic\u00eatre"

ym_int        <- function(y, m) as.integer(y) * 12L + as.integer(m)   # a month-of-history index
strip_accents <- function(x) stri_trans_general(as.character(x), "Latin-ASCII")
has_overlap   <- function(a, b) length(intersect(a, b)) > 0
# turn a FINESS code into a clean 9-digit string (keeps leading zeros)
fin9 <- function(x) str_pad(str_extract(str_replace(as.character(x), "\\.0$", ""),
                                        "[0-9]+"), 9, pad = "0")

# Map a detailed mechanism name to its broad gene "family".
# All the OXA-48-type variants are grouped together; the rest go by prefix.
oxa48_like <- c("OXA-48","OXA-48-LIKE","OXA-181","OXA-204","OXA-244","OXA-162",
                "OXA-232","OXA-484","OXA-163","OXA-245","OXA-370","OXA-405")
carb_family_one <- function(x) {
  x <- toupper(trimws(x))
  if (is.na(x) || x %in% c("", "-")) return(NA_character_)
  if (x %in% oxa48_like || str_starts(x, "OXA-48")) return("OXA48")
  for (p in c("KPC","NDM","VIM","IMP","IMI","GES")) if (str_starts(x, p)) return(p)
  NA_character_
}
families_of <- function(x) unique(na.omit(map_chr(str_trim(str_split(x, "\\+")[[1]]),
                                                  carb_family_one)))
variants_of <- function(x) unique(toupper(str_trim(str_split(x, "\\+")[[1]])))

# Break a hospital/town name into meaningful words, dropping generic words
# like "CH", "HOPITAL", "CENTRE" so they can't cause false matches.
place_stop <- c("CH","CHU","CHR","CHG","CHIC","CHS","GH","GHT","HL","HOP","HOPITAL",
  "HOPITAUX","CENTRE","HOSPITALIER","HOSPITALIERE","CLINIQUE","POLYCLINIQUE","GROUPE",
  "GROUPEMENT","DE","DU","DES","LA","LE","LES","SUR","ET","SAINT","ST","STE","SAINTE",
  "EHPAD","SSR","MCO","HAD","PSY")

tokenize_place <- function(x) {
  x <- str_squish(str_replace_all(toupper(strip_accents(x)), "[^A-Z0-9]", " "))
  map(str_split(x, " "), ~ unique(.x[nchar(.x) >= 3 & !.x %in% place_stop]))
}

mech_cols <- paste0("resistance_mechanism_", c("1_1","1_2","2_1","2_2","3_1","3_2"))
```

# Step 1 — Add the hospital name and town to each episode

The BHRe file has a FINESS code but no hospital name or town. We use the `nodes`
reference table to attach both, matching on the FINESS code.

```{r attach}
place_lu <- nodes %>%
  transmute(fin = fin9(finess_geo), facility_name_capact, city) %>%
  filter(!is.na(fin)) %>%
  distinct(fin, .keep_all = TRUE)

bhre <- bhre %>%
  mutate(fin = fin9(facility_finess_code)) %>%
  left_join(place_lu, by = "fin")


```

# Step 2 — Keep only episodes sent to the EPC reference lab

The `cnr_referral` field records *which* reference lab a strain was sent to. Only
strains sent to the **EPC carbapenemase CNR (Kremlin-Bicêtre)** appear in our CNR
dataset, so we keep only those episodes. Strains sent elsewhere (for example the
enterococci lab in Rennes) cannot possibly be in this CNR file, so they are set
aside.

```{r population}
n_epc <- sum(bhre$cnr_referral == EPC_LAB, na.rm = TRUE)
epc <- bhre %>% filter(cnr_referral == EPC_LAB)
```

**`r n_epc`** episodes were sent to the EPC CNR.

# Step 3 — Work out the clues we will match on (BHRe side)

For every episode we prepare the pieces of information used for matching:

- **When it was sent** — the date the strain was referred to the CNR
  (`cnr_referral_date`). This is the right date to use because the CNR's
  `sample_month`/`sample_year` are actually the **date the strain was received**
  at the lab, which lines up with the referral date, not the original sampling
  date.
- **The resistance mechanism** — both the broad family (e.g. NDM, VIM, OXA-48
  group) and the exact variant (e.g. NDM-5).
- **The hospital's department** — the first two digits of its FINESS code.
- **The hospital name and town** — broken into meaningful words for name-matching.

```{r bhre-keys}
epc <- epc %>%
  mutate(
    ref_date = if (isTRUE(params$date_fallback_form_issue))
                 coalesce(as.Date(cnr_referral_date), as.Date(form_issue_date))
               else as.Date(cnr_referral_date),
    ref_ym    = ym_int(year(ref_date), month(ref_date)),
    bhre_dept = str_sub(fin, 1, 2),
    bhre_mech = pmap_chr(select(., all_of(mech_cols)),
                         ~ paste(sort(unique(toupper(na.omit(c(...))))), collapse = " | ")),
    bhre_var  = pmap(select(., all_of(mech_cols)), ~ toupper(na.omit(unique(c(...))))),
    bhre_fam  = map(bhre_var, ~ unique(na.omit(map_chr(.x, carb_family_one)))),
    name_tok  = tokenize_place(facility_name_capact),
    city_tok  = tokenize_place(city)
  )

n_have_refdate <- sum(!is.na(as.Date(epc$cnr_referral_date)))
bhre_prep <- epc %>% filter(!is.na(ref_ym), lengths(bhre_fam) > 0)
n_keyed <- n_distinct(bhre_prep$ehesp_id)
```

**Important coverage point.** A referral date is only recorded for
**`r n_have_refdate`** of the `r n_epc` referred episodes
(`r percent(n_have_refdate / n_epc, 1)`). Episodes with no referral date cannot be
placed in time and are dropped. After also requiring a recognised carbapenemase
family, **`r n_keyed`** episodes are ready to match. (If you would rather fill the
gap, set `params$date_fallback_form_issue = TRUE` to use the form-submission date
when the referral date is missing.)

# Step 4 — Prepare the same clues on the CNR side

We do the equivalent on the CNR records. One record can list two mechanisms
("NDM-5 + OXA-48"); we split these so the record counts under both families.

```{r cnr-keys}
cnr_prep <- cnr %>%
  filter(!is_environment %in% TRUE) %>%                 # ignore environmental swabs
  mutate(
    cnr_ym   = ym_int(2000L + as.integer(sample_year), as.integer(sample_month)),
    cnr_dept = coalesce(str_sub(str_extract(as.character(department_code), "[0-9]+"), 1, 2),
                        str_sub(str_extract(as.character(zip_code_facility), "[0-9]+"), 1, 2)),
    cnr_name_tok = tokenize_place(facility_name),
    cnr_var  = map(sequencing, variants_of),
    family   = map(sequencing, families_of)
  ) %>%
  filter(lengths(family) > 0, !is.na(cnr_ym)) %>%
  unnest(family)
```

# Step 5 — Make the match and score it

**The rule for proposing a match:** an episode and a CNR record are only paired if
they have the **same mechanism family** *and* the referral month is **within
±`r tol_months` month** of the CNR receipt month. This is the non-negotiable
minimum.

**Scoring the strength of a match:** on top of that, we add points for extra
agreement. The more independent clues line up, the higher the score.

| Extra agreement                         | Points |
|-----------------------------------------|:------:|
| exact mechanism variant matches         |   2    |
| hospital **name** matches (tier 1)      |   3    |
| hospital name matches the **town** (tier 2) | 2  |
| same department                         |   1    |
| exact same month                        |   1    |

**Confidence:** `High` = 4 points or more; `Medium` = 2–3; `Low` = 1 or less.
Low matches are removed.

```{r join-score}
bhre_keyed <- bhre_prep %>%
  mutate(ym = map(ref_ym, ~ seq(.x - tol_months, .x + tol_months))) %>%
  select(ehesp_id, ref_date, ref_ym, bhre_dept, city, facility_name_capact,
         bhre_mech, bhre_var, name_tok, city_tok, family = bhre_fam, ym) %>%
  unnest(family) %>% unnest(ym)

candidates <- bhre_keyed %>%
  inner_join(cnr_prep, by = c("family", "ym" = "cnr_ym"),
             relationship = "many-to-many") %>%
  mutate(
    month_exact   = ym == ref_ym,
    variant_exact = map2_lgl(bhre_var, cnr_var, has_overlap),
    dept_match    = !is.na(bhre_dept) & !is.na(cnr_dept) & bhre_dept == cnr_dept,
    name_t1 = map2_lgl(cnr_name_tok, name_tok, has_overlap),   # CNR name vs hospital name
    name_t2 = map2_lgl(cnr_name_tok, city_tok, has_overlap),   # CNR name vs town
    name_tier  = case_when(name_t1 ~ "tier1_name", name_t2 ~ "tier2_city", TRUE ~ NA_character_),
    name_score = case_when(name_t1 ~ 3L, name_t2 ~ 2L, TRUE ~ 0L),
    score = 2L*variant_exact + name_score + dept_match + month_exact,
    confidence = case_when(score >= 4 ~ "High", score >= 2 ~ "Medium", TRUE ~ "Low") %>%
                 factor(levels = c("High","Medium","Low")),
    match_keys = pmap_chr(list(variant_exact, name_tier, dept_match, month_exact),
      function(v,nt,d,m) paste(c("family+month", if (v) "variant",
        if (!is.na(nt)) nt, if (d) "dept", if (m) "exact-month")[c(TRUE,v,!is.na(nt),d,m)],
        collapse="+"))
  )
```

# Step 6 — Keep the best match(es) per episode

For each episode we keep its highest-scoring CNR record(s) and drop anything that
only reached Low confidence. **An episode is allowed to match several CNR
records** — this is expected and correct, because a hospital often sends several
strains to the CNR in the same month and there is no patient-level key to single
one out.

```{r best}
bhre_cnr_matches <- candidates %>%
  group_by(ehesp_id) %>% mutate(is_best = score == max(score)) %>%
  filter(is_best, confidence != "Low") %>% ungroup() %>%
  transmute(ehesp_id, patient_id, specimen_id, confidence, score, name_tier, match_keys,
            ref_date, family, bhre_mech, cnr_sequencing = sequencing,
            bhre_facility_name = facility_name_capact, cnr_facility_name = facility_name,
            bhre_city = city, bhre_dept, cnr_dept,
            cnr_sample_month = sample_month, cnr_sample_year = sample_year,
            cnr_species = species)

episode_methods <- bhre_cnr_matches %>%
  group_by(ehesp_id) %>%
  summarise(confidence = first(confidence),
            name_method = case_when(
              any(name_tier == "tier1_name", na.rm = TRUE) ~ "tier1_name",
              any(name_tier == "tier2_city", na.rm = TRUE) ~ "tier2_city",
              TRUE ~ "none_no_name"),
            used_variant = any(str_detect(match_keys, "variant")),
            used_dept    = any(str_detect(match_keys, "dept")),
            used_month   = any(str_detect(match_keys, "exact-month")),
            n_cnr_specimens = n_distinct(specimen_id), .groups = "drop")
```

# Results

## How many episodes matched

```{r r1}
n_matched <- n_distinct(bhre_cnr_matches$ehesp_id)
tibble(step = c("Episodes sent to the EPC CNR",
                "Ready to match (had a referral date and a known mechanism)",
                "Matched (High or Medium; Low removed)",
                "   - High confidence",
                "   - Medium confidence"),
       episodes = c(n_epc, n_keyed, n_matched,
                    sum(episode_methods$confidence == "High"),
                    sum(episode_methods$confidence == "Medium"))) %>%
  kable(caption = "Episodes through the matching pipeline")
```

## Which method carried each match

Each matched episode is credited to the strongest hospital clue it used: the
hospital **name** (tier 1), the **town** (tier 2), or **neither** (matched on
family + department + month only).

```{r r2}
episode_methods %>%
  mutate(name_method = recode(name_method,
    tier1_name  = "Matched on hospital name",
    tier2_city  = "Matched on town",
    none_no_name= "No name clue (family + dept + month)")) %>%
  count(name_method, confidence) %>%
  pivot_wider(names_from = confidence, values_from = n, values_fill = 0) %>%
  kable(caption = "How each episode's best match was made")
```

```{r r2plot, echo=FALSE}
episode_methods %>%
  mutate(name_method = recode(name_method,
    tier1_name  = "Hospital name",
    tier2_city  = "Town",
    none_no_name= "No name clue")) %>%
  count(name_method, confidence) %>%
  ggplot(aes(reorder(name_method, n), n, fill = confidence)) +
  geom_col() + coord_flip() +
  labs(x = NULL, y = "episodes", fill = NULL,
       title = "Matches by the clue that carried them") +
  theme_minimal(base_size = 12)
```

## Which clues were used

```{r r3}
tibble(clue = c("Exact mechanism variant", "Same department", "Exact same month"),
       episodes_using_it = c(sum(episode_methods$used_variant),
                             sum(episode_methods$used_dept),
                             sum(episode_methods$used_month))) %>%
  kable(caption = paste0("Of the ", n_matched,
        " matched episodes, how many used each clue (all also matched family + month)"))
```

## One episode can match several strains

```{r r4}
tibble(measure = c("Episodes matching exactly one CNR strain",
                   "Episodes matching more than one CNR strain",
                   "Different CNR strains linked in total",
                   "Total episode-strain pairs kept",
                   "Typical (median) strains per episode"),
       value = c(sum(episode_methods$n_cnr_specimens == 1),
                 sum(episode_methods$n_cnr_specimens > 1),
                 n_distinct(bhre_cnr_matches$specimen_id),
                 nrow(bhre_cnr_matches),
                 median(episode_methods$n_cnr_specimens))) %>%
  kable(caption = "Match multiplicity (this is expected, not an error)")
```

## A look at some High-confidence matches

```{r r5}
bhre_cnr_matches %>% filter(confidence == "High") %>%
  select(ref_date, family, bhre_mech, cnr_sequencing,
         bhre_facility_name, cnr_facility_name, bhre_city, match_keys) %>%
  head(100)
```

# Save the results

```{r write, eval=FALSE}
write_csv(bhre_cnr_matches, here("Datasets","Output Data","bhre_cnr_matches.csv"))
write_csv(episode_methods,  here("Datasets","Output Data","bhre_cnr_episode_methods.csv"))
```

# Things to keep in mind

- Using the **referral date** is the correct choice, but it is missing for a large
  share of episodes, which is why the matched total is smaller than the number of
  referred episodes. The coverage figures above make this explicit.
- Matches with **no name clue** rely on family + department + month only. These
  are the weakest of the kept matches (mostly 2023 CNR records, which carry no
  hospital name). If you need higher certainty, consider requiring an exact
  variant or a name match for those.
- **Department** is a broad clue (about 100 nationwide): it supports a match but
  cannot pin one down on its own.
