---
title: "Dynamic Network Exploration"
output: html_notebook
---


# Exploratory Data Analysis of the Temporal Direct Network Data

```{r setup, echo= FALSE, include = FALSE}
setwd("C:\\Users\\octariar\\Documents\\arcane-temporal-network")
# Loading libraries
library(tidyverse)
library(lubridate)
library(ggplot2)
options(scipen = 999)

# Import the CSV datasets
# Importing from WINDOWS

monthly = read.csv(".\\Datasets\\hbn_direct_transfer_2024\\HBN_monthly_sliding_edgelist_2024.csv")
weekly = read.csv(".\\Datasets\\hbn_direct_transfer_2024\\HBN_weekly_sliding_edgelist_2024.csv")

```


We are running exploratory data analyses of the French transfer networks. OUr data comes from the direct transfers of all France hospitals in 2024, all within a 7-day time frame aggregation within one year. Therefore, our first analysis would be a descriptive analyses of the basic network characteristics.

## Weekly Transfer Window Data 

Let's explore the direct transfers with 7-day (weekly) time window,starting for all year
timespan. 

```{r weekly}

# Explore the data structure
# Let's make sure that the date span is from January to December.

head(weekly)
tail(weekly)

#Assigning seasons to the data

df <- weekly %>%
  mutate(
    window_start = as.Date(window_start),
    month = month(window_start),
    season = case_when(
      month %in% c(12, 1, 2)  ~ "Winter",
      month %in% c(3, 4, 5)   ~ "Spring",
      month %in% c(6, 7, 8)   ~ "Summer",
      month %in% c(9, 10, 11) ~ "Autumn"
    )
  )

# Creating the summary statistics of what i wanted to know about the network over time
# I want to know the Number of connections (edges), hospitals (nodes), 
# the number of total transfers between all hospitals within that week
# the mean and median number of transfers between hospitals
# the minimum and max number of transfers between hospitals
# 
# Group it with the Weekly Window Number, the Start Date of the Window

#FIrst, getting the overall for the year.

# Number of sending hospitals
num_sender = length(unique(df$finessGeo_origin))
num_sender

# Number of receiver hospitals
num_receiver = length(unique(df$finessGeo_target))
num_receiver

#Total number of transfers in the year
num_transfers_allyear = sum(df$weight)
num_transfers_allyear

#Max 10 transfers between pairs of hospitals within a week period
df %>%  slice_max(weight, n=5)

```


## Temporal Analysis of Trends by Weekly Time Window

Looking at the averages and summary statistics trend for day-to-day trends to see the ups and downs 
of the number of nodes, edges, transfers, and otehers

```{weekly summary}
summary_stats <- df %>%
  group_by(weekly_window_number,window_start,  month, season) %>%
  summarise(
    n_edges = n(),
    n_nodes = n_distinct(c(finessGeo_origin, finessGeo_target)),
    total_transfers = sum(weight),
    mean_weight = mean(weight),
    median_weight = median(weight),
    .groups = "drop"
  )

#Calculate density with and remove non-full transfer window
summary_stats <- summary_stats %>%
  mutate(
    density = n_edges / (n_nodes * (n_nodes - 1))
  ) %>% 
  filter(as.Date("2024-12-31") - window_start >= 7)

tail(summary_stats)
 

summary_overall <- summary_stats %>%
  summarise(
    across(
      where(is.numeric),
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        min = ~ min(.x, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE),
        median = ~ median(.x, na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    )
  )

summary_overall = summary_overall %>% 
  pivot_longer(
    cols = everything(),
    names_to = "metric", 
    values_to = "value"
  ) 
summary_overall = summary_overall[-c(1:4), ]


# Plotting the Distribution of Transfers

season_colors <- c(
  "Winter" = "#1f78b4",
  "Spring" = "#33a02c",
  "Summer" = "#ff7f00",
  "Autumn" = "#e31a1c"
)

metrics <- summary_stats %>%
  select(-weekly_window_number, -season) %>%
  colnames()


# Make sure the folder exists
if(!dir.exists("./Plots/")) dir.create("./Plots/")

# Loop over metrics to create plots and save
lapply(metrics, function(metric) {
  
  p <- ggplot(summary_stats, 
              aes(x = window_start,  # assuming this is a Date object
                  y = .data[[metric]],
                  color = season,
                  group = 1)) +
    geom_line(linewidth = 0.5) +
    geom_point(size = 1) +
    scale_color_manual(values = season_colors) +
    scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") + # monthly x-axis
    labs(
      title = paste("Weekly Trend of", metric),
      subtitle = "French Direct Transfer Data, 2024, Weekly Temporal Window", 
      x = "Month",
      y = metric,
      color = "Season"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          element_title(hjust=.5))
  
  # Save as high-res JPEG (4 x 6 inches)
  ggsave(
    filename = paste0("./Plots/", metric, ".jpeg"),
    plot = p,
    width = 6,
    height = 4,
    units = "in",
    dpi = 300
  )
  print(p)
  return(p)
})





```









Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
