---
title: "Dynamic Network Exploration"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


## Exploratory Data Analysis of the Temporal Direct Network Data

```{r setup, echo= FALSE, include = FALSE}
setwd("C:\\Users\\octariar\\Documents\\arcane-temporal-network")
# Loading libraries
library(tidyverse)
library(lubridate)
library(ggplot2)
library(igraph)

options(scipen = 999)

# Import the CSV datasets
# Importing from WINDOWS

monthly = read.csv(".\\Datasets\\hbn_direct_transfer_2024\\HBN_monthly_sliding_edgelist_2024.csv")
weekly = read.csv(".\\Datasets\\hbn_direct_transfer_2024\\HBN_weekly_sliding_edgelist_2024.csv")

```


We are running exploratory data analyses of the French transfer networks. OUr data comes from the direct transfers of all France hospitals in 2024, all within a 7-day time frame aggregation within one year. Therefore, our first analysis would be a descriptive analyses of the basic network characteristics.

### Weekly Transfer Window Data 

Let's explore the direct transfers with 7-day (weekly) time window,starting for all year
timespan. 

```{r weekly}

# Explore the data structure
# Let's make sure that the date span is from January to December.

head(weekly)
tail(weekly)

#Assigning seasons to the data

df <- weekly %>%
  mutate(
    window_start = as.Date(window_start),
    month = month(window_start),
    season = case_when(
      month %in% c(12, 1, 2)  ~ "Winter",
      month %in% c(3, 4, 5)   ~ "Spring",
      month %in% c(6, 7, 8)   ~ "Summer",
      month %in% c(9, 10, 11) ~ "Autumn"
    )
  )

# Creating the summary statistics of what i wanted to know about the network over time
# I want to know the Number of connections (edges), hospitals (nodes), 
# the number of total transfers between all hospitals within that week
# the mean and median number of transfers between hospitals
# the minimum and max number of transfers between hospitals
# 
# Group it with the Weekly Window Number, the Start Date of the Window

#FIrst, getting the overall for the year.

# Number of sending hospitals
num_sender = length(unique(df$finessGeo_origin))
num_sender

# Number of receiver hospitals
num_receiver = length(unique(df$finessGeo_target))
num_receiver

#Total number of transfers in the year
num_transfers_allyear = sum(df$weight)
num_transfers_allyear

#Max 10 transfers between pairs of hospitals within a week period
df %>%  slice_max(weight, n=5)

```
### Temporal Analysis of Trends by Weekly Time Window

Looking at the averages and summary statistics trend for day-to-day trends to see the ups and downs 
of the number of nodes, edges, transfers, and otehers

```{r weekly summary, echo = FALSE}

summary_stats <- df %>%
  group_by(weekly_window_number,window_start,  month, season) %>%
  summarise(
    n_edges = n(), #Number of edges
    n_nodes = n_distinct(c(finessGeo_origin, finessGeo_target)), # Number of nodes
    total_transfers = sum(weight), #Total transfers
    mean_weight = mean(weight), # mean transfers
    median_weight = median(weight), # median transfers 
    .groups = "drop"
  )

#Calculate density with and remove non-full transfer window
summary_stats <- summary_stats %>%
  mutate(
    density = n_edges / (n_nodes * (n_nodes - 1))
  ) %>% 
  filter(as.Date("2024-12-31") - window_start >= 7)

tail(summary_stats)
 

summary_overall <- summary_stats %>%
  summarise(
    across(
      where(is.numeric),
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        min = ~ min(.x, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE),
        median = ~ median(.x, na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    )
  )

summary_overall = summary_overall %>% 
  pivot_longer(
    cols = everything(),
    names_to = "metric", 
    values_to = "value"
  ) 
summary_overall = summary_overall[-c(1:4), ]


# Plotting the Distribution of Transfers

season_colors <- c(
  "Winter" = "#1f78b4",
  "Spring" = "#33a02c",
  "Summer" = "#ff7f00",
  "Autumn" = "#e31a1c"
)

metrics <- summary_stats %>%
  select(-weekly_window_number, -season, -month, -window_start) %>%
  colnames()

#Labeling each metrics for easier plot titling

metric_labels = c (
  n_edges = "Number of Edges - connections between hospitals",
  n_nodes = "NUmber of Active Nodes",
  total_transfers = "Transfers between hospitals",
  mean_weight = "Mean number of transfers",
  median_weight = "Median number of transfers",
  density = "Temporal Network Density"
  
)

# Make sure the folder exists
if(!dir.exists("./Plots/")) dir.create("./Plots/")

# Loop over metrics to create plots and save
lapply(metrics, function(metric) {
  
   nice_label <- metric_labels[metric]
   
   p <- ggplot(summary_stats, 
              aes(x = window_start,
                  y = .data[[metric]],
                  color = season,
                  group = 1)) +
    geom_line(linewidth = 0.5) +
    geom_point(size = 1) +
    scale_color_manual(values = season_colors) +
    scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
    labs(
      title = paste("Weekly Trend of", nice_label),
      subtitle = "French Direct Transfer Data, 2024, Weekly Temporal Window", 
      x = "Month",
      y = nice_label,
      color = "Season"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5)
          )
  
   ggsave(
    filename = paste0("./Plots/", metric, ".jpeg"),
    plot = p,
    width = 6,
    height = 4,
    units = "in",
    dpi = 300
  )
  
  return(p)
})
```

### Calculate the centrality measures statistics for the network data

```{r network stats}

# Define a function to calculate network-level statistics
calculate_network_metrics <- function(df) {
  
  # Initialize an empty list to store the results
  results <- list()
  
  # Loop over each unique time window
  for(t in unique(df$window_start)) {
    
    # Filter data for the current time window
    time_df <- df %>% filter(window_start == t)
    
    # Create a directed graph for the current time window with edge weights
    g <- graph_from_data_frame(time_df, directed = TRUE, vertices = NULL)
    E(g)$weight <- time_df$weight  # Add the weight attribute to the edges
    
    # Calculate network-level metrics
    network_stats <- data.frame(
      time_window = as.Date(t),
      num_nodes = vcount(g),
      num_edges = ecount(g),
      avg_degree = mean(degree(g)),
      density = edge_density(g),
      avg_path_length = tryCatch({
        # Compute shortest path lengths (weighted)
        sp_lengths <- shortest.paths(g, mode = "all", weights = E(g)$weight)
        # Remove infinite distances (no path found)
        sp_lengths[sp_lengths == Inf] <- NA
        mean(sp_lengths, na.rm = TRUE)
      }, error = function(e) NA),
      clustering_coef = tryCatch({
        # Compute local clustering coefficient for weighted directed graph
        transitivity(g, type = "local", weights = E(g)$weight)
      }, error = function(e) NA),
      num_connected_components = components(g)$no
    )
    
    # Store the results
    results[[as.character(t)]] <- network_stats
  }
  
  # Combine results for all time windows into one dataframe
  final_results <- bind_rows(results)
  
  return(final_results)
}

# Run the function and get the network-level statistics
network_metrics_df <- calculate_network_metrics(df)


#Export the dataset as result
#
# Make sure the folder exists
if(!dir.exists("./Outputs/")) dir.create("./Outputs/")
write.csv(network_metrics_df, file = "./Outputs/network_metrics_direct_weekly_2024.csv")
```