---
title: "Dynamic Network Exploration"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


## Exploratory Data Analysis of the Temporal Direct Network Data

```{r setup, echo= FALSE, include = FALSE}

# FIRST: MAKE SURE YOU OPEN THIS CODE FROM THE ARCANE-TEMPORAL-NETWORK PROJECT
# SECOND: make sure you download  the transfer datasets here #https://ehespfr-my.sharepoint.com/personal/shrichand_bhuria_ehesp_fr/_layouts/15/onedrive.aspx?id=%2Fpersonal%2Fshrichand%5Fbhuria%5Fehesp%5Ffr%2FDocuments%2FHBN%5F2024%5Fdata%5Fsharing&ga=1 

# Download it into the Datasets folder. I can't sync it into GitHub because the files were too large
# Loading libraries
library(tidyverse)
library(lubridate)
library(ggplot2)
library(igraph)
library(here)

options(scipen = 999)
# Import the CSV datasets
# Importing from WINDOWS
monthly = read_csv(here("Datasets", "hbn_direct_transfer_2024","HBN_monthly_sliding_edgelist_2024.csv" ))
weekly = read_csv(here("Datasets", "hbn_direct_transfer_2024","HBN_weekly_sliding_edgelist_2024.csv" ))
```

We are running exploratory data analyses of the French transfer networks. OUr data comes from the direct transfers of all France hospitals in 2024, all within a 7-day time frame aggregation within one year. Therefore, our first analysis would be a descriptive analyses of the basic network characteristics.

### Weekly Transfer Window Data 

Let's explore the direct transfers with 7-day (weekly) time window,starting for all year
timespan. 

```{r weekly}

# Explore the data structure
# Let's make sure that the date span is from January to December.

head(weekly)
tail(weekly)

#Assigning seasons to the data

df <- weekly %>%
  mutate(
    window_start = as.Date(window_start),
    month = month(window_start),
    season = case_when(
      month %in% c(12, 1, 2)  ~ "Winter",
      month %in% c(3, 4, 5)   ~ "Spring",
      month %in% c(6, 7, 8)   ~ "Summer",
      month %in% c(9, 10, 11) ~ "Autumn"
    )
  )

# Creating the summary statistics of what i wanted to know about the network over time
# I want to know the Number of connections (edges), hospitals (nodes), 
# the number of total transfers between all hospitals within that week
# the mean and median number of transfers between hospitals
# the minimum and max number of transfers between hospitals
# 
# Group it with the Weekly Window Number, the Start Date of the Window

#FIrst, getting the overall for the year.

# Number of sending hospitals
num_sender = length(unique(df$finessGeo_origin))
num_sender

# Number of receiver hospitals
num_receiver = length(unique(df$finessGeo_target))
num_receiver

#Total number of transfers in the year
num_transfers_allyear = sum(df$weight)
num_transfers_allyear

#Max 10 transfers between pairs of hospitals within a week period
df %>%  slice_max(weight, n=5)

```
### Temporal Analysis of Trends by Weekly Time Window

Looking at the averages and summary statistics trend for day-to-day trends to see the ups and downs 
of the number of nodes, edges, transfers, and otehers

```{r weekly summary, echo = FALSE}

summary_stats <- df %>%
  group_by(weekly_window_number,window_start,  month, season) %>%
  summarise(
    n_edges = n(), #Number of edges
    n_nodes = n_distinct(c(finessGeo_origin, finessGeo_target)), # Number of nodes
    total_transfers = sum(weight), #Total transfers
    mean_weight = mean(weight), # mean transfers
    median_weight = median(weight), # median transfers 
    .groups = "drop"
  )

#Calculate density with and remove non-full transfer window
summary_stats <- summary_stats %>%
  mutate(
    density = n_edges / (n_nodes * (n_nodes - 1))
  ) %>% 
  filter(as.Date("2024-12-31") - window_start >= 7)

tail(summary_stats)
 

summary_overall <- summary_stats %>%
  summarise(
    across(
      where(is.numeric),
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        min = ~ min(.x, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE),
        median = ~ median(.x, na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    )
  )

summary_overall = summary_overall %>% 
  pivot_longer(
    cols = everything(),
    names_to = "metric", 
    values_to = "value"
  ) 
summary_overall = summary_overall[-c(1:4), ]


# Plotting the Distribution of Transfers

season_colors <- c(
  "Winter" = "#1f78b4",
  "Spring" = "#33a02c",
  "Summer" = "#ff7f00",
  "Autumn" = "#e31a1c"
)

metrics <- summary_stats %>%
  select(-weekly_window_number, -season, -month, -window_start) %>%
  colnames()

#Labeling each metrics for easier plot titling

metric_labels = c (
  n_edges = "Number of Edges - connections between hospitals",
  n_nodes = "NUmber of Active Nodes",
  total_transfers = "Transfers between hospitals",
  mean_weight = "Mean number of transfers",
  median_weight = "Median number of transfers",
  density = "Temporal Network Density"
  
)

# Make sure the folder exists
if(!dir.exists("./Plots/")) dir.create("./Plots/")

# Loop over metrics to create plots and save
lapply(metrics, function(metric) {
  
   nice_label <- metric_labels[metric]
   
   p <- ggplot(summary_stats, 
              aes(x = window_start,
                  y = .data[[metric]],
                  color = season,
                  group = 1)) +
    geom_line(linewidth = 0.5) +
    geom_point(size = 1) +
    scale_color_manual(values = season_colors) +
    scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
    labs(
      title = paste("Weekly Trend of", nice_label),
      subtitle = "French Direct Transfer Data, 2024, Weekly Temporal Window", 
      x = "Month",
      y = nice_label,
      color = "Season"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5)
          )
  
   ggsave(
    filename = paste0(here ("Plots"), metric, ".jpeg"),
    plot = p,
    width = 6,
    height = 4,
    units = "in",
    dpi = 300
  )
  
  return(p)
})
```

### Calculate the centrality measures statistics for the network data

```{r network stats}
# packages used
library(dplyr)     # filter, group_by, summarise, arrange
library(purrr)     # map_dfr
library(igraph)    # graph_from_data_frame, degree, edge_density, distances, transitivity, components


calculate_network_metrics <- function(df) {

  df %>%
    mutate(
      window_start = as.Date(window_start),
      weight = as.numeric(weight)
    ) %>%
    group_by(window_start) %>%
    group_split() %>%
    map_dfr(function(time_df) {

      g <- igraph::graph_from_data_frame(
        d = time_df %>% select(finessGeo_origin, finessGeo_target, weight),
        directed = TRUE,
        vertices = NULL
      )

      # ---------- helper: weighted mean distance (finite, excluding zeros) ----------
      avg_path_length <- tryCatch({
        dmat <- igraph::distances(g, mode = "all", weights = igraph::E(g)$weight)
        dvec <- as.vector(dmat)
        dvec <- dvec[is.finite(dvec) & dvec > 0]
        if (length(dvec) == 0) NA_real_ else mean(dvec)
      }, error = function(e) NA_real_)

      # ---------- clustering / transitivity (single scalars) ----------
      trans_global <- tryCatch(
        igraph::transitivity(g, type = "global"),
        error = function(e) NA_real_
      )

      local_clust <- tryCatch(
        igraph::transitivity(g, type = "local", isolates = "zero"),
        error = function(e) rep(NA_real_, igraph::vcount(g))
      )
      trans_local_mean <- mean(local_clust, na.rm = TRUE)
      trans_local_median <- stats::median(local_clust, na.rm = TRUE)

      # ---------- reciprocity (directed) ----------
      reciprocity <- tryCatch(
        igraph::reciprocity(g, ignore.loops = TRUE),
        error = function(e) NA_real_
      )

      # ---------- components ----------
      n_comp_weak <- igraph::components(g, mode = "weak")$no
      n_comp_strong <- igraph::components(g, mode = "strong")$no

      # ---------- degree / strength summaries ----------
      deg_in  <- igraph::degree(g, mode = "in")
      deg_out <- igraph::degree(g, mode = "out")
      str_in  <- igraph::strength(g, mode = "in",  weights = igraph::E(g)$weight)
      str_out <- igraph::strength(g, mode = "out", weights = igraph::E(g)$weight)

      # ---------- centralization ----------
      cent_in  <- tryCatch(igraph::centr_degree(g, mode = "in",  normalized = TRUE)$centralization,
                           error = function(e) NA_real_)
      cent_out <- tryCatch(igraph::centr_degree(g, mode = "out", normalized = TRUE)$centralization,
                           error = function(e) NA_real_)

      # ---------- diameter (finite) ----------
      diameter_w <- tryCatch({
        dmat <- igraph::distances(g, mode = "all", weights = igraph::E(g)$weight)
        max(dmat[is.finite(dmat)], na.rm = TRUE)
      }, error = function(e) NA_real_)

      # ---------- assortativity by degree (directed) ----------
      assort_deg <- tryCatch(
        igraph::assortativity_degree(g, directed = TRUE),
        error = function(e) NA_real_
      )

      # ---------- Burt constraint (mean) ----------
      constraint_mean <- tryCatch(
        mean(igraph::constraint(g), na.rm = TRUE),
        error = function(e) NA_real_
      )

      tibble(
        time_window = unique(time_df$window_start),

        # size
        num_nodes = igraph::vcount(g),
        num_edges = igraph::ecount(g),

        # density / connectivity
        density = igraph::edge_density(g),
        num_connected_components_weak = n_comp_weak,
        num_connected_components_strong = n_comp_strong,
        reciprocity = reciprocity,

        # degrees
        avg_degree_total = mean(igraph::degree(g)),
        avg_degree_in = mean(deg_in),
        avg_degree_out = mean(deg_out),
        max_degree_in = max(deg_in, na.rm = TRUE),
        max_degree_out = max(deg_out, na.rm = TRUE),

        # strengths (weighted degrees)
        avg_strength_in = mean(str_in, na.rm = TRUE),
        avg_strength_out = mean(str_out, na.rm = TRUE),
        max_strength_in = max(str_in, na.rm = TRUE),
        max_strength_out = max(str_out, na.rm = TRUE),

        # paths
        avg_path_length = avg_path_length,
        diameter_weighted = diameter_w,

        # transitivity / clustering
        transitivity_global = trans_global,
        transitivity_local_mean = trans_local_mean,
        transitivity_local_median = trans_local_median,

        # centralization / structure
        degree_centralization_in = cent_in,
        degree_centralization_out = cent_out,
        assortativity_degree = assort_deg,
        constraint_mean = constraint_mean
      )
    }) %>%
    arrange(time_window)
}

#network_metrics_df <- calculate_network_metrics(df)
#saveRDS(network_metrics_df, file = here("Outputs", "network_metrics_df.rds"))
readRDS(here("Outputs", "network_metrics_df.rds"))

# checks
nrow(network_metrics_df)
dplyr::n_distinct(df$window_start)
```

## Graphing all the Stats
```{r graph daybyday}
# packages used
library(dplyr)      # select, mutate, arrange
library(tidyr)      # pivot_longer
library(ggplot2)    # ggplot, geoms, scales, theme
library(stringr)    # str_replace_all (optional)
library(here)       # here()
library(purrr)      # walk

season_colors <- c(
  "Winter" = "#1f78b4",
  "Spring" = "#33a02c",
  "Summer" = "#ff7f00",
  "Autumn" = "#e31a1c"
)

# --- 1) Use your new metrics df (network_metrics_df) ---
plot_df <- network_metrics_df %>%
  mutate(
    season = case_when(
      format(time_window, "%m") %in% c("12","01","02") ~ "Winter",
      format(time_window, "%m") %in% c("03","04","05") ~ "Spring",
      format(time_window, "%m") %in% c("06","07","08") ~ "Summer",
      TRUE ~ "Autumn"
    ),
    season = factor(season, levels = c("Winter","Spring","Summer","Autumn"))
  ) %>%
  arrange(time_window)

# --- 2) Labels for ALL metrics you want to plot ---
metric_labels <- c(
  num_nodes = "Number of active nodes",
  num_edges = "Number of edges",
  density = "Edge density",
  num_connected_components_weak = "Connected components (weak)",
  num_connected_components_strong = "Connected components (strong)",
  reciprocity = "Reciprocity",
  avg_degree_total = "Average degree (total)",
  avg_degree_in = "Average in-degree",
  avg_degree_out = "Average out-degree",
  max_degree_in = "Max in-degree",
  max_degree_out = "Max out-degree",
  avg_strength_in = "Average in-strength (weighted)",
  avg_strength_out = "Average out-strength (weighted)",
  max_strength_in = "Max in-strength (weighted)",
  max_strength_out = "Max out-strength (weighted)",
  avg_path_length = "Average shortest-path length (weighted)",
  diameter_weighted = "Network diameter (weighted)",
  transitivity_global = "Transitivity (global)",
  transitivity_local_mean = "Transitivity (mean local)",
  transitivity_local_median = "Transitivity (median local)",
  degree_centralization_in = "Degree centralization (in)",
  degree_centralization_out = "Degree centralization (out)",
  assortativity_degree = "Assortativity by degree",
  constraint_mean = "Burt constraint (mean)"
)

# --- 3) Choose which metrics to plot (only those present) ---
metrics_to_plot <- intersect(names(metric_labels), names(plot_df))

# --- 4) Make folder ---
plots_dir <- here("Plots")
if (!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE)

# --- 5) Long format + one plot per metric + save ---
plot_long <- plot_df %>%
  select(time_window, season, all_of(metrics_to_plot)) %>%
  pivot_longer(
    cols = all_of(metrics_to_plot),
    names_to = "metric",
    values_to = "value"
  ) %>%
  mutate(
    metric_label = unname(metric_labels[metric])
  )

purrr::walk(unique(plot_long$metric), function(m) {

  tmp <- plot_long %>% filter(metric == m)
  nice_label <- unique(tmp$metric_label)

  p <- ggplot(tmp, aes(x = time_window, y = value, color = season, group = 1)) +
    geom_line(linewidth = 0.5, na.rm = TRUE) +
    geom_point(size = 1, na.rm = TRUE) +
    scale_color_manual(values = season_colors, drop = FALSE) +
    scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
    labs(
      title = paste("Weekly Trend of", nice_label),
      subtitle = "French Direct Transfer Data, 2024, Weekly Temporal Window",
      x = "Month",
      y = nice_label,
      color = "Season"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      plot.title = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5)
    )
print(p)
  ggsave(
    filename = file.path(plots_dir, paste0(m, ".jpeg")),
    plot = p,
    width = 6,
    height = 4,
    units = "in",
    dpi = 300
  )
})


```

## Visualizing Dynamic Temporal Networks 
```{r temporal network viz, include = FALSE}

# 
# library(tidyverse)   # dplyr
# library(tidygraph)   # tbl_graph, activate
# library(ggraph)      # ggraph
# library(gganimate)   # transition_states, animate
# library(igraph)      # as.igraph (optional)
# library(grid)        # unit
# library(here)        # here
# # install.packages("av")
# library(av) 
# # df = your full edge list
# # cols: finessGeo_origin, finessGeo_target, weight, window_start, window_end, weekly_window_number
# 
# df2 <- df %>%
#   mutate(
#     window_start = as.Date(window_start),
#     window_end   = as.Date(window_end),
#     weekly_window_number = as.integer(weekly_window_number)
#   )
# 
# # 1) Unique windows
# windows <- df2 %>%
#   distinct(weekly_window_number, window_start, window_end) %>%
#   arrange(window_start)
# 
# # 2) Create a 7-day grid over window_start range
# grid <- tibble(
#   grid_date = seq(min(windows$window_start), max(windows$window_start), by = "7 days")
# )
# 
# # 3) For each grid_date, pick the nearest window_start (stable and deterministic)
# sampled_windows <- grid %>%
#   mutate(
#     weekly_window_number = map_int(
#       grid_date,
#       ~ windows %>%
#         mutate(dist = abs(as.numeric(window_start - .x))) %>%
#         slice_min(dist, with_ties = FALSE) %>%
#         pull(weekly_window_number)
#     )
#   ) %>%
#   left_join(windows, by = "weekly_window_number") %>%
#   distinct(weekly_window_number, window_start, window_end) %>%
#   arrange(window_start) %>%
#   mutate(
#     week_label = paste0(
#       "Week ", weekly_window_number, " (", window_start, " to ", window_end, ")"
#     )
#   )
# # 4) Filter edges to only those sampled windows
# df_sampled <- df2 %>%
#   inner_join(sampled_windows %>% select(weekly_window_number, week_label),
#              by = "weekly_window_number")
# 
# 
# # ---- Stable layout across all sampled windows ----
# all_nodes <- df_sampled %>%
#   select(name = finessGeo_origin) %>%
#   bind_rows(df_sampled %>% select(name = finessGeo_target)) %>%
#   distinct()
# 
# base_graph <- igraph::graph_from_data_frame(
#   d = df_sampled %>% distinct(finessGeo_origin, finessGeo_target) %>%
#     transmute(from = finessGeo_origin, to = finessGeo_target),
#   directed = TRUE,
#   vertices = all_nodes
# )
# 
# set.seed(1)
# 
# layout_tbl <- igraph::layout_with_fr(base_graph) %>%
#   as_tibble(.name_repair = "minimal") %>%
#   setNames(c("x", "y")) %>%
#   bind_cols(all_nodes)
# 
# nodes_anim <- layout_tbl %>% transmute(name, x, y)
# 
# edges_anim <- df_sampled %>%
#   transmute(
#     from = finessGeo_origin,
#     to   = finessGeo_target,
#     weight,
#     week_label
#   )
# 
# # ---- 1) HARD CUT: keep only top N edges per frame (tune N = 50–300) ----
# N_EDGES <- 150
# 
# edges_anim_fast2 <- edges_anim%>%
#   group_by(week_label) %>%
#   slice_max(order_by = weight, n = N_EDGES, with_ties = FALSE) %>%
#   ungroup()
# 
# # IMPORTANT: rename edge columns to 'from'/'to' for tbl_graph
# edges_tbl <- edges_anim_fast2 %>%
#   transmute(
#     from = from,
#     to =to,
#     weight,
#     week_label
#   )
# 
# nodes_tbl <- nodes_anim %>%
#   transmute(
#     name,
#     x, y
#   )
# 
# # 2) Build tbl_graph (keeps edge attributes for animation)
# g_tbl <- tbl_graph(nodes = nodes_tbl, edges = edges_tbl, directed = TRUE)
# 
# # 3) Plot: manual layout uses node x/y columns inside tbl_graph
# p_fast <- ggraph(g_tbl, layout = "manual", x = x, y = y) +
#   geom_edge_link(aes(width = weight), alpha = 0.6) +   # no arrows, no end_cap
#   geom_node_point(size = 2.2) +
#   scale_edge_width(range = c(0.1, 2.0)) +
#   theme_void() +
#   transition_states(week_label, transition_length = 1, state_length = 1) +
#   ease_aes("linear")
# 
# dir.create(here("Outputs"), showWarnings = FALSE, recursive = TRUE)
# 
# anim <- animate(
#   p_fast,
#   nframes = 60,
#   fps = 10,
#   width = 550,
#   height = 400,
#   renderer = av_renderer(here("Outputs", "network_fast.mp4"))
# )

```
