---
title: "Dynamic Network Exploration"
output:
  html_document:
    df_print: paged
    mathjax: default
---

---
title: "Math Test"
output:
  html_document:
    mathjax: default
---


## Exploratory Data Analysis of the Temporal Direct Network Data

```{r setup, include = FALSE}

# FIRST: MAKE SURE YOU OPEN THIS CODE FROM THE ARCANE-TEMPORAL-NETWORK PROJECT
# SECOND: make sure you download  the transfer datasets here #https://ehespfr-my.sharepoint.com/personal/shrichand_bhuria_ehesp_fr/_layouts/15/onedrive.aspx?id=%2Fpersonal%2Fshrichand%5Fbhuria%5Fehesp%5Ffr%2FDocuments%2FHBN%5F2024%5Fdata%5Fsharing&ga=1 

# Download it into the Datasets folder. I can't sync it into GitHub because the files were too large
# Loading libraries
library(tidyverse)
library(lubridate)
library(ggplot2)
library(igraph)
library(here)
library(purrr)     # map_dfr
library(igraph)
library(patchwork)   # side-by-side layout


options(scipen = 999)
# Import the CSV datasets
# Importing from WINDOWS
monthly = read_csv(here("Datasets", "hbn_direct_transfer_2024","HBN_monthly_sliding_edgelist_2024.csv" ))
weekly = read_csv(here("Datasets", "hbn_direct_transfer_2024","HBN_weekly_sliding_edgelist_2024.csv" ))
```

We are running exploratory data analyses of the French transfer networks. OUr data comes from the direct transfers of all France hospitals in 2024, all within a 7-day time frame aggregation within one year. Therefore, our first analysis would be a descriptive analyses of the basic network characteristics.

### Weekly Transfer Window Data 

Let's explore the direct transfers with 7-day (weekly) time window,starting for all year
timespan. 

```{r reading hospital data, include = FALSE}

#Available here: https://drees2-sgsocialgouv.opendatasoft.com/explore/dataset/708_bases-statistiques-sae/information/
# CAPACT24 appears to refer to a capacity variable for full inpatient hospitalization, specifically the number of installed beds for hospitalisation complète (24 hours or more) in the relevant unit or activity table. The SAE variable list snippet for 2024 shows the label beginning with “Nombre de lits installés en hospitalisation complète…”, and the SAE documentation explains that the survey collects establishments’ capacities, activity, technical platforms, and staffing through thematic tables.

capact24 <- read_delim(here("Datasets", "CAPACT_PM_PNM","Bases CSV", "capact24.csv"), 
                         delim = ";", escape_double = FALSE, trim_ws = TRUE, 
                        locale = locale(encoding = "Latin1"))  #so it can read French vocals
#save capact into comma-separated CSV
write.csv(capact24, file = here("Datasets", "CAPACT24.csv"))

#Reading in Finess Georgaphical Coords data
finess_geo = read.csv(here("Datasets", "finessGeo_data.csv"))
head(finess_geo)
```

```{r weekly, echo = FALSE, warning = FALSE}
# Packages
library(dplyr)
library(lubridate)
library(tibble)

summarize_transfer_network <- function(data, output_name = NULL, unique_edges = TRUE) {
  
  summary_df <- data %>%
    mutate(
      window_start = as.Date(window_start),
      month = month(window_start),
      season = case_when(
        month %in% c(12, 1, 2)  ~ "Winter",
        month %in% c(3, 4, 5)   ~ "Spring",
        month %in% c(6, 7, 8)   ~ "Summer",
        month %in% c(9, 10, 11) ~ "Autumn",
        TRUE ~ NA_character_
      )
    ) %>%
    group_by(window_start, month, season) %>%
    summarise(
      n_edges = if (unique_edges) {
        n_distinct(paste(finessGeo_origin, finessGeo_target, sep = "_"))
      } else {
        n()
      },
      n_senders = n_distinct(finessGeo_origin),
      n_receivers = n_distinct(finessGeo_target),
      n_nodes = n_distinct(c(finessGeo_origin, finessGeo_target)),
      total_transfers = sum(weight, na.rm = TRUE),
      mean_transfers = mean(weight, na.rm = TRUE),
      median_transfers = median(weight, na.rm = TRUE),
      min_transfers = min(weight, na.rm = TRUE),
      max_transfers = max(weight, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    arrange(window_start)
  
  if (!is.null(output_name)) {
    assign(output_name, summary_df, envir = .GlobalEnv)
  }
  
  return(summary_df)
}

weekly1  <- summarize_transfer_network(weekly,  output_name = "summary_weekly",  unique_edges = TRUE)
monthly1 <- summarize_transfer_network(monthly, output_name = "summary_monthly", unique_edges = TRUE)
```
### Temporal Analysis of Trends by Weekly Time Window

Looking at the averages and summary statistics trend for day-to-day trends to see the ups and downs 
of the number of nodes, edges, transfers, and otehers

```{r weekly summary, echo = FALSE}
library(rlang)

make_summary_stats <- function(data,
                               window_id,
                               end_date = "2024-12-31",
                               min_remaining_days = 7) {
  
  window_id <- enquo(window_id)
  
  summary_stats <- data %>%
    mutate(
      window_start = as.Date(window_start),
      month = lubridate::month(window_start),
      season = dplyr::case_when(
        month %in% c(12, 1, 2)  ~ "Winter",
        month %in% c(3, 4, 5)   ~ "Spring",
        month %in% c(6, 7, 8)   ~ "Summer",
        month %in% c(9, 10, 11) ~ "Autumn"
      )
    ) %>%
    group_by(!!window_id, window_start, month, season) %>%
    summarise(
      n_edges = n(),
      n_nodes = n_distinct(c(finessGeo_origin, finessGeo_target)),
      total_transfers = sum(weight, na.rm = TRUE),
      mean_weight = mean(weight, na.rm = TRUE),
      median_weight = median(weight, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      density = n_edges / (n_nodes * (n_nodes - 1))
    ) %>%
    filter(as.Date(end_date) - window_start >= min_remaining_days)
  
  return(summary_stats)
}

make_summary_overall <- function(summary_data, id_col) {
  
  id_col <- enquo(id_col)
  
  summary_overall <- summary_data %>%
    select(-!!id_col, -window_start, -month, -season) %>%
    summarise(
      across(
        where(is.numeric),
        list(
          mean = ~ mean(.x, na.rm = TRUE),
          min = ~ min(.x, na.rm = TRUE),
          max = ~ max(.x, na.rm = TRUE),
          median = ~ median(.x, na.rm = TRUE)
        ),
        .names = "{.col}_{.fn}"
      )
    ) %>%
    pivot_longer(
      cols = everything(),
      names_to = "metric",
      values_to = "value"
    )
  
  return(summary_overall)
}

season_colors <- c(
  "Winter" = "#1f78b4",
  "Spring" = "#33a02c",
  "Summer" = "#ff7f00",
  "Autumn" = "#e31a1c"
)

metric_labels <- c(
  n_edges = "Number of Edges - connections between hospitals",
  n_nodes = "Number of Active Nodes",
  total_transfers = "Transfers between hospitals",
  mean_weight = "Mean number of transfers",
  median_weight = "Median number of transfers",
  density = "Temporal Network Density"
)

plot_summary_metrics <- function(summary_data,
                                 id_col,
                                 period_label = "Weekly",
                                 output_prefix = "weekly",
                                 output_folder = "Plots") {
  
  id_col <- enquo(id_col)
  
  metrics <- summary_data %>%
    select(-!!id_col, -season, -month, -window_start) %>%
    colnames()
  
  if (!dir.exists(here::here(output_folder))) {
    dir.create(here::here(output_folder), recursive = TRUE)
  }
  
  plot_list <- lapply(metrics, function(metric) {
    
    nice_label <- metric_labels[[metric]]
    
    p <- ggplot(
      summary_data,
      aes(
        x = window_start,
        y = .data[[metric]],
        color = season,
        group = 1
      )
    ) +
      geom_line(linewidth = 0.5) +
      geom_point(size = 1) +
      scale_color_manual(values = season_colors) +
      scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
      labs(
        title = paste(period_label, "Trend of", nice_label),
        subtitle = paste(
          "French Direct Transfer Data, 2024,",
          period_label,
          "Temporal Window"
        ),
        x = "Month",
        y = nice_label,
        color = "Season"
      ) +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)
      )
    
    ggsave(
      filename = here::here(output_folder, paste0(output_prefix, "_", metric, ".jpeg")),
      plot = p,
      width = 6,
      height = 4,
      units = "in",
      dpi = 300
    )
    
    return(p)
  })
  
  names(plot_list) <- metrics
  return(plot_list)
}

# Run for weekly
summary_weekly <- make_summary_stats(
  data = weekly,
  window_id = weekly_window_number
)

overall_weekly <- make_summary_overall(
  summary_data = summary_weekly,
  id_col = weekly_window_number
)

plots_weekly <- plot_summary_metrics(
  summary_data = summary_weekly,
  id_col = weekly_window_number,
  period_label = "Weekly",
  output_prefix = "weekly"
)

# Run for monthly
summary_monthly <- make_summary_stats(
  data = monthly,
  window_id = monthly_window_number
)

overall_monthly <- make_summary_overall(
  summary_data = summary_monthly,
  id_col = monthly_window_number
)

plots_monthly <- plot_summary_metrics(
  summary_data = summary_monthly,
  id_col = monthly_window_number,
  period_label = "Monthly",
  output_prefix = "monthly"
)
```

### Calculate the centrality measures statistics for the network data

```{r network stats, include = FALSE}
# packages used
   # graph_from_data_frame, degree, edge_density, distances, transitivity, components
calculate_network_metrics <- function(df) {

  df %>%
    mutate(
      window_start = as.Date(window_start),
      weight = as.numeric(weight)
    ) %>%
    group_by(window_start) %>%
    group_split() %>%
    map_dfr(function(time_df) {

      g <- igraph::graph_from_data_frame(
        d = time_df %>% dplyr::select(finessGeo_origin, finessGeo_target, weight),
        directed = TRUE,
        vertices = NULL
      )

      # ---------- helper: weighted mean distance (finite, excluding zeros) ----------
      avg_path_length <- tryCatch({
        dmat <- igraph::distances(g, mode = "all", weights = igraph::E(g)$weight)
        dvec <- as.vector(dmat)
        dvec <- dvec[is.finite(dvec) & dvec > 0]
        if (length(dvec) == 0) NA_real_ else mean(dvec)
      }, error = function(e) NA_real_)

      # ---------- clustering / transitivity (single scalars) ----------
      trans_global <- tryCatch(
        igraph::transitivity(g, type = "global"),
        error = function(e) NA_real_
      )

      local_clust <- tryCatch(
        igraph::transitivity(g, type = "local", isolates = "zero"),
        error = function(e) rep(NA_real_, igraph::vcount(g))
      )
      trans_local_mean <- mean(local_clust, na.rm = TRUE)
      trans_local_median <- stats::median(local_clust, na.rm = TRUE)

      # ---------- reciprocity (directed) ----------
      reciprocity <- tryCatch(
        igraph::reciprocity(g, ignore.loops = TRUE),
        error = function(e) NA_real_
      )

      # ---------- components ----------
      n_comp_weak <- igraph::components(g, mode = "weak")$no
      n_comp_strong <- igraph::components(g, mode = "strong")$no

      # ---------- degree / strength summaries ----------
      deg_in  <- igraph::degree(g, mode = "in")
      deg_out <- igraph::degree(g, mode = "out")
      str_in  <- igraph::strength(g, mode = "in",  weights = igraph::E(g)$weight)
      str_out <- igraph::strength(g, mode = "out", weights = igraph::E(g)$weight)

      # ---------- centralization ----------
      cent_in  <- tryCatch(igraph::centr_degree(g, mode = "in",  normalized = TRUE)$centralization,
                           error = function(e) NA_real_)
      cent_out <- tryCatch(igraph::centr_degree(g, mode = "out", normalized = TRUE)$centralization,
                           error = function(e) NA_real_)

      # ---------- diameter (finite) ----------
      diameter_w <- tryCatch({
        dmat <- igraph::distances(g, mode = "all", weights = igraph::E(g)$weight)
        max(dmat[is.finite(dmat)], na.rm = TRUE)
      }, error = function(e) NA_real_)

      # ---------- assortativity by degree (directed) ----------
      assort_deg <- tryCatch(
        igraph::assortativity_degree(g, directed = TRUE),
        error = function(e) NA_real_
      )

      # ---------- Burt constraint (mean) ----------
      constraint_mean <- tryCatch(
        mean(igraph::constraint(g), na.rm = TRUE),
        error = function(e) NA_real_
      )

      tibble(
        time_window = unique(time_df$window_start),

        # size
        num_nodes = igraph::vcount(g),
        num_edges = igraph::ecount(g),

        # density / connectivity
        density = igraph::edge_density(g),
        num_connected_components_weak = n_comp_weak,
        num_connected_components_strong = n_comp_strong,
        reciprocity = reciprocity,

        # degrees
        avg_degree_total = mean(igraph::degree(g)),
        avg_degree_in = mean(deg_in),
        avg_degree_out = mean(deg_out),
        max_degree_in = max(deg_in, na.rm = TRUE),
        max_degree_out = max(deg_out, na.rm = TRUE),

        # strengths (weighted degrees)
        avg_strength_in = mean(str_in, na.rm = TRUE),
        avg_strength_out = mean(str_out, na.rm = TRUE),
        max_strength_in = max(str_in, na.rm = TRUE),
        max_strength_out = max(str_out, na.rm = TRUE),

        # paths
        avg_path_length = avg_path_length,
        diameter_weighted = diameter_w,

        # transitivity / clustering
        transitivity_global = trans_global,
        transitivity_local_mean = trans_local_mean,
        transitivity_local_median = trans_local_median,

        # centralization / structure
        degree_centralization_in = cent_in,
        degree_centralization_out = cent_out,
        assortativity_degree = assort_deg,
        constraint_mean = constraint_mean
      )
    }) %>%
    arrange(time_window)
}
#These two lines run the function but it runs very slowly 
#therefore, it is commented out and instead i am saving it as rds and load it from the dataset

# network_metrics_weekly <- calculate_network_metrics(weekly)
# network_metrics_monthly <- calculate_network_metrics(monthly)

# saveRDS(network_metrics_weekly, file = here("Outputs", "network_metrics_weekly.rds"))
# saveRDS(network_metrics_monthly, file = here("Outputs", "network_metrics_monthly.rds"))

#runnin
network_metrics_weekly =  readRDS(here("Outputs", "network_metrics_weekly.rds"))
network_metrics_monthly = readRDS(here("Outputs", "network_metrics_monthly.rds"))
```

## Network metrics definitions (weighted, directed hospital transfer network)
Let $G_t = (V_t, E_t)$ be the **directed, weighted** hospital transfer network for time window $t$.

- **Nodes** ($V_t$): hospitals (e.g., `finessGeo`)
- **Edges** ($E_t$): directed transfers from origin $\rightarrow$ target within the window
- **Edge weight** ($w_{ij,t}$): number of transfers from hospital $i$ to hospital $j$ in window $t$
- A “present” edge means $w_{ij,t} > 0$

---

## `n_nodes` — Number of active nodes

**Definition:**

$$
n_{nodes}(t) = \left|V_t\right|
$$

**Interpretation:** Number of hospitals that appear in the network during window $t$ as an origin and/or target with at least one transfer.

---

## `n_edges` — Number of directed edges

**Definition:**

$$
n_{edges}(t) = \left|E_t\right|
$$

where each directed pair $(i \rightarrow j)$ with $w_{ij,t} > 0$ counts as one edge.

**Interpretation:** Number of distinct **origin $\rightarrow$ destination** transfer connections observed in window $t$, regardless of volume.

---

## `total_transfers` — Total transfer volume (sum of weights)

**Definition:**

$$
\mathrm{total\_transfers}(t) = \sum_{(i \rightarrow j)\in E_t} w_{ij,t}
$$

**Interpretation:** Total number of patient transfers captured in window $t$ across all directed connections.

---

## `mean_weight` — Mean edge weight

**Definition:**

$$
\mathrm{mean\_weight}(t) = \frac{1}{\left|E_t\right|}\sum_{(i \rightarrow j)\in E_t} w_{ij,t}
$$

**Interpretation:** Average number of transfers per observed directed connection in window $t$. Higher values imply that, on average, connections carry heavier transfer traffic.

---

## `median_weight` — Median edge weight

**Definition:**

The median of the set

$$
\left\{ w_{ij,t} : (i \rightarrow j)\in E_t \right\}.
$$

**Interpretation:** Typical transfer volume per observed directed connection, less sensitive to extreme high-volume routes than `mean_weight`.

---

## `density` — Directed network density (unweighted definition)

**Definition** (standard directed density without self-loops):

$$
\mathrm{density}(t) = \frac{\left|E_t\right|}{\left|V_t\right|\left(\left|V_t\right|-1\right)}
$$

**Interpretation:** Proportion of all possible directed hospital-to-hospital connections that are observed (have at least one transfer) in window $t$.

- Values near 0: sparse network (few observed routes)
- Values near 1: highly connected network (many observed routes)

**Note:** This density is **about presence/absence of edges**, not transfer volume. Even in a weighted network, density is usually defined on the binary graph.

---

## Optional clarifications

- **Directed:** $(i \rightarrow j)$ is different from $(j \rightarrow i)$
- **Weighted:** edges carry magnitudes (number of transfers)
- **Active node:** a hospital with at least one incoming or outgoing transfer in that window
- **Edge counted once per pair per window:** multiple transfers on the same route contribute to the weight, not to additional edges



## Graphing all the Stats
```{r graph daybyday, echo = FALSE,  fig.width=16, fig.height=5, out.width="100%"}

season_colors <- c(
  "Winter" = "#1f78b4",
  "Spring" = "#33a02c",
  "Summer" = "#ff7f00",
  "Autumn" = "#e31a1c"
)

metric_labels <- c(
  num_nodes                      = "Number of active nodes",
  num_edges                      = "Number of edges",
  density                        = "Edge density",
  num_connected_components_weak  = "Connected components (weak)",
  num_connected_components_strong= "Connected components (strong)",
  reciprocity                    = "Reciprocity",
  avg_degree_total               = "Average degree (total)",
  avg_degree_in                  = "Average in-degree",
  avg_degree_out                 = "Average out-degree",
  max_degree_in                  = "Max in-degree",
  max_degree_out                 = "Max out-degree",
  avg_strength_in                = "Average in-strength (weighted)",
  avg_strength_out               = "Average out-strength (weighted)",
  max_strength_in                = "Max in-strength (weighted)",
  max_strength_out               = "Max out-strength (weighted)",
  avg_path_length                = "Average shortest-path length (weighted)",
  diameter_weighted              = "Network diameter (weighted)",
  transitivity_global            = "Transitivity (global)",
  transitivity_local_mean        = "Transitivity (mean local)",
  transitivity_local_median      = "Transitivity (median local)",
  degree_centralization_in       = "Degree centralization (in)",
  degree_centralization_out      = "Degree centralization (out)",
  assortativity_degree           = "Assortativity by degree",
  constraint_mean                = "Burt constraint (mean)"
)

# Helper: build a long-format tibble ready for plotting
prepare_plot_df <- function(data, date_col = "time_window") {
  data %>%
    mutate(
      !!date_col := as.Date(.data[[date_col]]),
      season = case_when(
        format(.data[[date_col]], "%m") %in% c("12", "01", "02") ~ "Winter",
        format(.data[[date_col]], "%m") %in% c("03", "04", "05") ~ "Spring",
        format(.data[[date_col]], "%m") %in% c("06", "07", "08") ~ "Summer",
        TRUE ~ "Autumn"
      ),
      season = factor(season, levels = c("Winter", "Spring", "Summer", "Autumn"))
    ) %>%
    arrange(.data[[date_col]]) %>%
    select(all_of(date_col), season,
           all_of(intersect(names(metric_labels), names(.)))) %>%
    pivot_longer(
      cols = -c(all_of(date_col), season),
      names_to  = "metric",
      values_to = "value"
    ) %>%
    mutate(metric_label = unname(metric_labels[metric]))
}

# Helper: build a single ggplot for one metric / one period
build_plot <- function(df_long, metric_name, date_col, period_label) {
  tmp        <- df_long %>% filter(metric == metric_name)
  nice_label <- unique(tmp$metric_label)

  ggplot(tmp, aes(x = .data[[date_col]], y = value,
                  color = season, group = 1)) +
    geom_line(linewidth = 0.5, na.rm = TRUE) +
    geom_point(size = 1,       na.rm = TRUE) +
    scale_color_manual(values = season_colors, drop = FALSE) +
    scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
    labs(
      title    = paste(period_label, "–", nice_label),
      subtitle = "French Direct Transfer Data, 2024",
      x        = "Month",
      y        = nice_label,
      color    = "Season"
    ) +
    theme_minimal() +
    theme(
      axis.text.x  = element_text(angle = 45, hjust = 1),
      plot.title   = element_text(hjust = 0.5, size = 10),
      plot.subtitle= element_text(hjust = 0.5, size = 8)
    )
}

# Prepare long-format data for both resolutions
df_weekly  <- prepare_plot_df(network_metrics_weekly,  date_col = "time_window")
df_monthly <- prepare_plot_df(network_metrics_monthly, date_col = "time_window")

# Shared set of metrics present in both datasets
shared_metrics <- intersect(unique(df_weekly$metric),
                             unique(df_monthly$metric))

# Output folder for saved files
plots_dir <- here::here("Plots")
if (!dir.exists(plots_dir)) dir.create(plots_dir, recursive = TRUE)

# Render one side-by-side panel per metric
walk(shared_metrics, function(m) {

  p_weekly  <- build_plot(df_weekly,  m, "time_window", "Weekly")
  p_monthly <- build_plot(df_monthly, m, "time_window", "Monthly")

  # Weekly on the LEFT, Monthly on the RIGHT
  # shared legend is pulled to the right via patchwork
  combined <- (p_weekly | p_monthly) +
    plot_layout(guides = "collect") &
    theme(legend.position = "right")

  print(combined)          # renders inline in the HTML output

  ggsave(
    filename = file.path(plots_dir, paste0("combined_", m, ".jpeg")),
    plot     = combined,
    width    = 16,
    height   = 5,
    units    = "in",
    dpi      = 300
  )
})

```
```{r annual-network-interactive, fig.width=16, fig.height=10, out.width="100%", warning=FALSE, message=FALSE}
library(dplyr)
library(igraph)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(visNetwork)
library(ggiraph)
library(ggplot2)
library(scales)
library(grid)

# ── 1. REGION CODE → LABEL ────────────────────────────────────────────────────
region_labels <- c(
  "11" = "Île-de-France",            "24" = "Centre-Val de Loire",
  "27" = "Bourgogne-Franche-Comté",  "28" = "Normandie",
  "32" = "Hauts-de-France",          "44" = "Grand Est",
  "52" = "Pays de la Loire",         "53" = "Bretagne",
  "75" = "Nouvelle-Aquitaine",       "76" = "Occitanie",
  "84" = "Auvergne-Rhône-Alpes",     "93" = "Provence-Alpes-Côte d'Azur",
  "94" = "Corse",                    "01" = "Guadeloupe",
  "02" = "Martinique",               "03" = "Guyane",
  "04" = "La Réunion",               "06" = "Mayotte"
)

# ── 2. BUILD NODE TABLE ───────────────────────────────────────────────────────
capact_nodes <- capact24 %>%
  mutate(LIT = as.numeric(LIT)) %>%
  group_by(fi) %>%
  summarise(
    rs          = first(rs),
    dep         = first(dep),
    reg         = first(as.character(reg)),
    total_beds  = sum(LIT, na.rm = TRUE),
    #disciplines = paste(sort(unique(DISCIPLINE)), collapse = ", "),
    .groups     = "drop"
  ) %>%
  mutate(
    region = coalesce(region_labels[reg], paste0("Région ", reg))
  )

table(capact_nodes$disciplines)

nodes <- finess_geo %>%
  dplyr::rename(fi = finessgeo, x = coordxet, y = coordyet) %>%
  select(fi, x, y) %>%
  filter(!is.na(x), !is.na(y)) %>%
  sf::st_as_sf(coords = c("x", "y"), crs = 2154) %>%   # Lambert-93
  sf::st_transform(4326) %>%                           # convert to lon/lat
  mutate(
    lon = sf::st_coordinates(.)[, 1],
    lat = sf::st_coordinates(.)[, 2]
  ) %>%
  sf::st_drop_geometry() %>%
  inner_join(capact_nodes, by = "fi")

# ── 3. ANNUAL CUMULATIVE EDGES ────────────────────────────────────────────────
annual_edges <- weekly %>%
  group_by(finessGeo_origin, finessGeo_target) %>%
  summarise(total_weight = sum(weight, na.rm = TRUE), .groups = "drop") %>%
  filter(finessGeo_origin != finessGeo_target)

# ── 4. FILTER TO STRONG EDGES FOR FASTER RENDER ──────────────────────────────
# Keep only edges > 1 transfer, then top 10% by weight
# Change 0.90 to 0.75 if you want more edges
edges_gt1 <- annual_edges %>%
  filter(total_weight > 1)

top_threshold <- quantile(edges_gt1$total_weight, 0.90, na.rm = TRUE)

edges_strong <- edges_gt1 %>%
  filter(total_weight >= top_threshold) %>%
  arrange(desc(total_weight))

active_ids <- unique(c(edges_strong$finessGeo_origin, edges_strong$finessGeo_target))

nodes_strong <- nodes %>%
  filter(fi %in% active_ids)

# ── 5. JITTER ONLY NODES WITH IDENTICAL COORDINATES ──────────────────────────
# Small deterministic offsets arranged in a circle around the original point.
# This affects ONLY duplicated coordinates.

jitter_radius <- 0.03
# Increase to 2500 or 3000 if overlaps remain.
# This assumes your coordinates are in a projected CRS with meter-like units.
# If your coords are already lon/lat degrees, use something tiny like 0.02 instead.

nodes_strong_jitter <- nodes_strong %>%
  group_by(lon, lat) %>%
  mutate(
    n_overlap = n(),
    dup_index = row_number(),
    angle = if_else(
      n_overlap == 1,
      0,
      2 * pi * (dup_index - 1) / n_overlap
    ),
    lon_plot = if_else(
      n_overlap == 1,
      lon,
      lon + jitter_radius * cos(angle)
    ),
    lat_plot = if_else(
      n_overlap == 1,
      lat,
      lat + jitter_radius * sin(angle)
    )
  ) %>%
  ungroup()

# ── 6. JOIN EDGES WITH JITTERED NODE ATTRIBUTES ──────────────────────────────
edges_geo <- edges_strong %>%
  inner_join(
    nodes_strong_jitter %>%
      select(fi, lon_from = lon_plot, lat_from = lat_plot,
             region_from = region, name_from = rs,
             disciplines_from = disciplines, beds_from = total_beds),
    by = c("finessGeo_origin" = "fi")
  ) %>%
  inner_join(
    nodes_strong_jitter %>%
      select(fi, lon_to = lon_plot, lat_to = lat_plot,
             region_to = region, name_to = rs,
             disciplines_to = disciplines, beds_to = total_beds),
    by = c("finessGeo_target" = "fi")
  )


#DIAGNOSTIC if the lat and long is correct
#Comment out if it's correct now
# nodes_strong_jitter %>%
#   summarise(
#     min_lon_plot = min(lon_plot, na.rm = TRUE),
#     max_lon_plot = max(lon_plot, na.rm = TRUE),
#     min_lat_plot = min(lat_plot, na.rm = TRUE),
#     max_lat_plot = max(lat_plot, na.rm = TRUE)
#   )
# 
# edges_geo %>%
#   summarise(
#     min_lon_from = min(lon_from, na.rm = TRUE),
#     max_lon_from = max(lon_from, na.rm = TRUE),
#     min_lat_from = min(lat_from, na.rm = TRUE),
#     max_lat_from = max(lat_from, na.rm = TRUE),
#     min_lon_to   = min(lon_to, na.rm = TRUE),
#     max_lon_to   = max(lon_to, na.rm = TRUE),
#     min_lat_to   = min(lat_to, na.rm = TRUE),
#     max_lat_to   = max(lat_to, na.rm = TRUE)
 # )
```


```{r next viz section}

# ── 7. COLOUR PALETTE BY REGION ───────────────────────────────────────────────
province_levels <- sort(unique(nodes_strong_jitter$region))
n_prov          <- length(province_levels)
base_cols       <- brewer.pal(min(max(n_prov, 3), 12), "Paired")
if (n_prov > 12) base_cols <- colorRampPalette(base_cols)(n_prov)

province_colors <- setNames(base_cols[seq_len(n_prov)], province_levels)

# ── 8. FRANCE MAP ─────────────────────────────────────────────────────────────
france <- rnaturalearth::ne_states(country = "France", returnclass = "sf") %>%
  filter(!name %in% c("Guyane", "Martinique", "Guadeloupe",
                      "La Réunion", "Mayotte")) %>%
  sf::st_transform(4326)

#Create a France Outline
france_outline <- france %>%
  summarise(geometry = st_union(geometry))

# If your node coordinates are NOT already in WGS84 lon/lat, you must transform them first.
# For now I preserve your structure exactly as written.

# ── 9. PLOT TABLES ────────────────────────────────────────────────────────────
edges_for_plot <- edges_geo %>%
  mutate(
    ggtitle = paste0(
      "<b>From:</b> ", name_from, " (", region_from, ")<br>",
      "<b>To:</b> ",   name_to,   " (", region_to,   ")<br>",
      "<b>Transfers:</b> ", format(total_weight, big.mark = ",")
    ),
    edge_size = rescale(total_weight, to = c(0.25, 1.4))
  )

nodes_for_plot <- nodes_strong_jitter %>%
  mutate(
    ggtitle = paste0(
      "<b>", rs, "</b><br>",
      "Region: ", region, "<br>",
      "Disciplines: ", disciplines, "<br>",
      "Beds: ", total_beds,
      if_else(n_overlap > 1,
              paste0("<br><i>Shared original location with ", n_overlap - 1, " nearby facility/facilities</i>"),
              "")
    ),
    id = fi,
    node_size = rescale(total_beds, to = c(1.8, 5.2))
  )

# ── 10. GGIRAPH MAP ───────────────────────────────────────────────────────────
mapplot <- ggplot() +
  geom_sf(
    data        = france,
    fill        = "grey80",
    colour      = "grey40",
    linewidth   = 0.3,
    inherit.aes = FALSE
  ) +
  geom_curve_interactive(
    data = edges_for_plot,
    aes(
      x       = lon_from,
      y       = lat_from,
      xend    = lon_to,
      yend    = lat_to,
      tooltip = ggtitle,
      colour  = region_from
    ),
    linewidth = edges_for_plot$edge_size,
    curvature = 0.22,
    alpha     = 0.55,
    arrow     = arrow(length = unit(0.05, "inches"), type = "closed")
  ) +
  scale_colour_manual(
    values = province_colors,
    name   = "Sender Region",
    guide  = "none"
  ) +
  geom_point_interactive(
    data = nodes_for_plot,
    aes(
      x       = lon_plot,
      y       = lat_plot,
      tooltip = ggtitle,
      data_id = id,
      fill    = region
    ),
    colour = "black",
    shape  = 21,
    size   = nodes_for_plot$node_size,
    alpha  = 0.9,
    stroke = 0.3
  ) +
  scale_fill_manual(values = province_colors, name = "Region") +
  coord_sf(
    xlim = c(-5.5, 10),
    ylim = c(41, 52),
    crs  = sf::st_crs(4326)
  ) +
  labs(
    title    = "Annual Hospital Transfer Network — France 2024",
    subtitle = "Top 10% edges by transfer volume. Only overlapping facilities are offset slightly."
  ) +
  theme_void() +
  theme(
    plot.title      = element_text(hjust = 0.5, size = 12, face = "bold"),
    plot.subtitle   = element_text(hjust = 0.5, size = 8, face = "italic"),
    legend.box      = "vertical",
    legend.position = "right"
  ) +
  guides(
    fill = guide_legend(
      "Region",
      override.aes = list(shape = 21, size = 3),
      ncol = 1
    )
  )
girafe(
  ggobj = mapplot,
  width_svg = 12,
  height_svg = 9
) %>%
  girafe_options(
    opts_hover(css = "stroke:black; stroke-width:1.2;"),
    opts_hover_inv(css = "opacity:0.18;"),
    opts_tooltip(
      opacity = 0.95,
      delay_mouseover = 150,
      delay_mouseout = 100,
      use_fill = TRUE,
      css = "background-color:#6B6B6B;
             color:black;
             border:1px solid #3A3A3A;
             border-radius:6px;
             padding:8px;
             font-size:12px;
             font-family:sans-serif;"
    ),
    opts_zoom(min = 1, max = 8),
    opts_sizing(rescale = TRUE, width = 1)
  )
```
