---
title: "ARCANE — France-Wide Beta Calibration Diagnostics"
subtitle: "ESBL Transmission Rate Estimation — All 10 Parallel Runs"
author: "ARCANE Project — MESuRS/Cnam"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    fig_width: 10
    fig_height: 6
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  warning   = FALSE,
  message   = FALSE,
  fig.align = "center"
)
```

```{r libraries}
library(dplyr)
library(ggplot2)
library(tidyr)
library(knitr)
library(kableExtra)
```

---

# Overview

This report analyses all **10 independent France-wide calibration runs**.
Each run is a fully independent Nelder-Mead optimisation started with a
different random seed, allowing us to assess **result stability** (do all runs
agree on the same β?) and **select the best run** (lowest SSE) as the
final France-wide calibration result.

## Why run 10 times?

The Nelder-Mead optimiser is deterministic given a starting point, but the
**objective function is stochastic** — it runs many simulations and averages
them.  Two runs from the same starting point can reach slightly different
results because of random variation in the simulations.  Running 10 independent
jobs with different seeds and starting points gives us:

1. **Robustness:** If all 10 runs agree, we are confident the result is stable
2. **Best result:** The run with the lowest SSE is the most accurate calibration
3. **Uncertainty estimate:** The spread of β values across runs tells us how
   precisely we can identify the transmission rate

---

```{r load-all-results}
OUT_DIR <- file.path(
  "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/optim_cluster_jobs",
  "Outputs", "france"
)

# Find all final_validation.rds across all 10 job folders
rds_files <- list.files(OUT_DIR,
                         pattern   = "final_validation\\.rds$",
                         recursive  = TRUE,
                         full.names = TRUE)
rds_files <- rds_files[!grepl("/compiled/|/analysis/", rds_files)]

if (length(rds_files) == 0) stop("No results found under: ", OUT_DIR)

results <- lapply(rds_files, readRDS)

# Combined validation summary — one row per type × job
all_summaries <- bind_rows(lapply(results, function(r) {
  r$validation_summary %>%
    mutate(job_index = r$job_index,
           sse_total = r$sse_final)
}))

# SSE ranking across jobs
sse_by_job <- all_summaries %>%
  distinct(job_index, sse_total) %>%
  arrange(sse_total) %>%
  mutate(rank = row_number())

best_job    <- sse_by_job$job_index[1]
best_result <- results[[which(sapply(results, `[[`, "job_index") == best_job)]]
best_val    <- best_result$validation_summary

# Colour palette
type_colours <- c(
  "MCO"                             = "#0057B8",
  "SSR"                             = "#C1392B",
  "MCO/SSR"                         = "#9B1D8A",
  "PSY"                             = "#F5A623",
  "HAD"                             = "#00B4D8",
  "Cancer centre (CLCC)"            = "#2ECC71",
  "General public hospital"         = "#0057B8",
  "Private for profit hospital"     = "#E74C3C",
  "Private not-for-profit hospital" = "#9B1D8A",
  "Rehabilitation hospital"         = "#C1392B",
  "University hospital"             = "#F5A623",
  "Unknown"                         = "#555555"
)
```

---

# 1. Run summary

```{r run-summary}
# How many jobs completed?
n_jobs      <- length(results)
n_types     <- length(best_result$incidence_obs)
n_hospitals <- if (!is.null(best_result$H_region)) best_result$H_region else "Full network"

meta <- data.frame(
  Parameter = c(
    "Scope",
    "Jobs completed",
    "Calibration types",
    "Replicates per objective call",
    "Validation replicates",
    "Best job (lowest SSE)",
    "Best SSE",
    "Worst SSE"
  ),
  Value = c(
    "France-wide (all regions pooled)",
    paste(n_jobs, "of 10"),
    paste(names(best_result$incidence_obs), collapse = ", "),
    best_result$n_rep_obj,
    best_result$n_rep_valid,
    paste("Job", best_job),
    round(min(sse_by_job$sse_total), 6),
    round(max(sse_by_job$sse_total), 6)
  )
)

kable(meta, col.names = c("Parameter", "Value"), align = c("l","l")) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE)
```

---

# 2. SSE across all 10 runs

## What this tells us

Each bar shows the **total SSE** (sum of squared errors between simulated and
observed incidence) achieved by one of the 10 independent runs.

**How to read this plot:**

- **Lower SSE = better fit.** The run with the shortest bar found the best
  combination of β values for all facility types simultaneously
- **Bars of similar height** = the optimiser is finding the same solution
  regardless of starting point — the calibration is stable and trustworthy
- **One bar much shorter than the rest** = only one run found the global optimum;
  the others got trapped in local minima.  The result is still valid (we use the
  best run), but it suggests the optimisation landscape is complex
- **All bars very similar and very low** = ideal result: stable, well-identified
  transmission rates
- The **red dashed line** marks the best SSE for reference

```{r sse-all-jobs, fig.height=5}
ggplot(sse_by_job,
       aes(x = reorder(factor(job_index), sse_total), y = sse_total,
           fill = job_index == best_job)) +
  geom_col(width = 0.7) +
  geom_hline(yintercept = min(sse_by_job$sse_total),
             linetype = "dashed", colour = "#E74C3C", linewidth = 0.8) +
  geom_text(aes(label = round(sse_total, 4)), hjust = -0.1, size = 3.5) +
  scale_fill_manual(values = c("FALSE" = "#7fb3d3", "TRUE" = "#0057B8"),
                    labels = c("FALSE" = "Other runs", "TRUE" = "Best run")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.25))) +
  coord_flip() +
  labs(
    title    = "Total SSE by job — France-wide calibration",
    subtitle = "Dark blue = best run (lowest SSE).  Red dashed = best SSE reference.",
    x        = "Job index",
    y        = "Total SSE (sum of squared errors)",
    fill     = NULL
  ) +
  theme_bw(base_size = 13) +
  theme(plot.title      = element_text(face = "bold"),
        legend.position = "bottom",
        panel.grid.minor = element_blank())
```

---

# 3. Beta stability across runs {.tabset}

## What this tells us

This section shows **how much the optimal β estimates vary across the 10 runs**.
This is a critical diagnostic for assessing **parameter identifiability** — can
the data uniquely determine β, or do many different β values fit equally well?

**How to read these plots:**

- **Tight cluster of points** = high stability.  All runs converge to essentially
  the same β for that type.  The parameter is well-identified by the data.
- **Spread of points** = uncertainty.  The optimiser finds different β values
  for that type depending on starting conditions.  This can mean:
  - The objective surface is flat in that direction (multiple β values fit equally)
  - The type has few hospitals in the network so the signal is weak
  - The type's incidence target has high uncertainty (SPARES data sparse)
- The **★ star** marks the best run's β estimate (lowest SSE)
- The **box** shows the interquartile range (middle 50% of estimates across runs)

A well-calibrated result should have tight clusters for all types.

## Beta scatter across runs

```{r beta-scatter, fig.height=5}
beta_all <- all_summaries %>%
  select(job_index, sse_total, type, beta) %>%
  arrange(type, sse_total)

ggplot(beta_all,
       aes(x = reorder(type, beta, FUN = median), y = beta)) +
  geom_boxplot(width = 0.35, outlier.shape = NA,
               fill = "#d6eaf8", colour = "#2980B9", linewidth = 0.6) +
  geom_jitter(aes(colour = factor(job_index)),
              width = 0.12, size = 2.5, alpha = 0.8) +
  geom_point(data = filter(beta_all, job_index == best_job),
             shape = 8, size = 5, colour = "black", stroke = 1.5) +
  scale_y_log10(labels = scales::scientific) +
  scale_colour_viridis_d(name = "Job") +
  labs(
    title    = "Beta estimates across all 10 runs — France-wide",
    subtitle = "★ = best run  |  Box = IQR across runs  |  Log scale",
    x        = "Facility type",
    y        = "β (per day, log scale)"
  ) +
  theme_bw(base_size = 13) +
  theme(plot.title       = element_text(face = "bold"),
        axis.text.x      = element_text(angle = 30, hjust = 1),
        legend.position  = "right",
        panel.grid.minor = element_blank())
```

## Beta summary statistics

```{r beta-stats}
beta_stats <- beta_all %>%
  group_by(type) %>%
  summarise(
    n_runs   = n(),
    beta_min = round(min(beta, na.rm = TRUE), 6),
    beta_q25 = round(quantile(beta, 0.25, na.rm = TRUE), 6),
    beta_med = round(median(beta, na.rm = TRUE), 6),
    beta_q75 = round(quantile(beta, 0.75, na.rm = TRUE), 6),
    beta_max = round(max(beta, na.rm = TRUE), 6),
    beta_cv  = round(100 * sd(beta, na.rm = TRUE) / mean(beta, na.rm = TRUE), 1),
    beta_best = round(beta_all$beta[beta_all$type == type[1] &
                                      beta_all$job_index == best_job][1], 6),
    .groups  = "drop"
  )

beta_stats %>%
  rename(
    "Facility type"    = type,
    "Runs"             = n_runs,
    "Min β"            = beta_min,
    "Q25 β"            = beta_q25,
    "Median β"         = beta_med,
    "Q75 β"            = beta_q75,
    "Max β"            = beta_max,
    "CV% (stability)"  = beta_cv,
    "Best-run β"       = beta_best
  ) %>%
  kable(align = c("l","c","r","r","r","r","r","r","r")) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) %>%
  footnote(general = paste0(
    "CV% = coefficient of variation across the 10 runs. ",
    "Lower CV% = more stable estimate. ",
    "CV% < 10% = very stable; 10–30% = moderate; > 30% = uncertain. ",
    "Best-run β = estimate from the run with lowest total SSE (Job ", best_job, ")."
  ))
```

---

# 4. Best run: observed vs simulated incidence

## What this tells us

This is the primary calibration plot for the **best-performing run** (Job `r best_job`,
SSE = `r round(best_result$sse_final, 6)`).

Each point is a facility type.  The dashed line is perfect fit (simulated =
observed).  Error bars show ±1 standard deviation across `r best_result$n_rep_valid`
independent validation replicates — they represent the **stochastic noise** of
the simulation, not uncertainty in the data.

**Wide error bars** for a type mean the simulation is inherently noisy for that
type — usually because those hospitals are small (few beds) or rare in the
network, so the incidence estimate fluctuates a lot between replicates even at
the optimal β.

**A good calibration** shows all points close to the dashed line, with error
bars that overlap the diagonal.

```{r best-obs-vs-sim}
axis_max <- max(c(best_val$incidence_obs,
                  best_val$incidence_sim_mean + best_val$incidence_sim_sd)) * 1.12

ggplot(best_val,
       aes(x = incidence_obs, y = incidence_sim_mean, colour = type)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey40", linewidth = 0.9) +
  geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                    ymax = incidence_sim_mean + incidence_sim_sd),
                width = 0, linewidth = 0.9, alpha = 0.5) +
  geom_point(size = 5) +
  geom_text(aes(label = type),
            hjust = -0.12, vjust = 0.4, size = 3.5,
            show.legend = FALSE) +
  scale_colour_manual(values = type_colours, na.value = "#555555") +
  scale_x_continuous(limits = c(0, axis_max)) +
  scale_y_continuous(limits = c(0, axis_max)) +
  coord_fixed() +
  labs(
    title    = paste0("Simulated vs. observed incidence — Best run (Job ",
                      best_job, ")"),
    subtitle = paste0("Dashed = perfect fit  |  ±1 SD across ",
                      best_result$n_rep_valid, " replicates  |  SSE = ",
                      round(best_result$sse_final, 4)),
    x        = "Observed incidence (SPARES, per 1,000 bed-days)",
    y        = "Simulated incidence (per 1,000 bed-days)",
    colour   = "Facility type"
  ) +
  theme_bw(base_size = 13) +
  theme(plot.title      = element_text(face = "bold"),
        legend.position = "none",
        panel.grid.minor = element_blank())
```

---

# 5. All 10 runs: observed vs simulated

## What this tells us

This faceted plot shows the calibration result for **every run simultaneously**.
It is the most informative single diagnostic for understanding the reliability
of the calibration across the whole multi-start procedure.

**What to look for:**

- **Consistent patterns across panels** = the result is robust.  Whether or not
  a specific run had the lowest SSE, they all produce similar pictures
- **One or two panels clearly worse** (points far from the diagonal) = those
  runs got stuck; the multi-start strategy correctly identified and discarded them
- **Wildly different patterns** = the calibration is unreliable; β is not
  well-identified by the data and more runs or a wider search may be needed
- The **SSE value in each panel title** lets you quickly see which panels are good fits

```{r all-runs-facet, fig.height=10, fig.width=12}
all_summaries %>%
  mutate(panel_label = paste0("Job ", job_index,
                               "\nSSE = ", round(sse_total, 4),
                               ifelse(job_index == best_job, " ★ BEST", ""))) %>%
  ggplot(aes(x = incidence_obs, y = incidence_sim_mean)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey50") +
  geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                    ymax = incidence_sim_mean + incidence_sim_sd),
                width = 0, alpha = 0.4) +
  geom_point(aes(colour = type), size = 3) +
  facet_wrap(~ panel_label, ncol = 5) +
  scale_colour_manual(values = type_colours, na.value = "#555555", name = "Type") +
  labs(
    title    = "Observed vs simulated incidence — all 10 France-wide runs",
    subtitle = "Dashed = perfect fit  |  ★ = best run  |  Error bars = ±1 SD",
    x        = "Observed (per 1,000 bed-days)",
    y        = "Simulated (per 1,000 bed-days)"
  ) +
  theme_bw(base_size = 11) +
  theme(plot.title       = element_text(face = "bold"),
        legend.position  = "bottom",
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "grey92"),
        strip.text       = element_text(size = 9))
```

---

# 6. Best-run diagnostics {.tabset}

## Quality table

```{r quality-table}
quality <- best_val %>%
  mutate(
    pct_error = round(100 * diff / incidence_obs, 1),
    ratio     = round(incidence_sim_mean / incidence_obs, 3),
    cv_sim    = round(100 * incidence_sim_sd / incidence_sim_mean, 1)
  )

quality %>%
  select(type, beta, incidence_obs, incidence_sim_mean,
         incidence_sim_sd, pct_error, ratio, cv_sim, sse) %>%
  rename(
    "Facility type"         = type,
    "β (per day)"           = beta,
    "Observed"              = incidence_obs,
    "Simulated (mean)"      = incidence_sim_mean,
    "Simulated (SD)"        = incidence_sim_sd,
    "% error"               = pct_error,
    "Sim/Obs ratio"         = ratio,
    "CV% (sim noise)"       = cv_sim,
    "SSE"                   = sse
  ) %>%
  kable(digits = 4, align = c("l","r","r","r","r","r","r","r","r")) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) %>%
  footnote(general = paste0(
    "All incidences per 1,000 bed-days. ",
    "% error = 100 × (simulated − observed) / observed. ",
    "CV% = simulation noise (coefficient of variation across replicates). ",
    "SSE = (simulated − observed)²."
  ))
```

**R² (simulated vs observed):** `r round(cor(best_val$incidence_obs, best_val$incidence_sim_mean)^2, 4)`

**Mean absolute error:** `r round(mean(abs(best_val$diff)), 4)` per 1,000 bed-days

**Total SSE:** `r round(best_result$sse_final, 6)`

## Percentage error

```{r pct-error, fig.height=4}
quality %>%
  ggplot(aes(x = reorder(type, abs(pct_error)), y = pct_error,
             fill = pct_error > 0)) +
  geom_col(width = 0.65) +
  geom_hline(yintercept = 0, linewidth = 0.7) +
  geom_text(
    aes(label = paste0(ifelse(pct_error > 0, "+", ""), pct_error, "%"),
        hjust = ifelse(pct_error > 0, -0.1, 1.1)),
    size = 3.8
  ) +
  scale_fill_manual(values = c("TRUE" = "#E74C3C", "FALSE" = "#2980B9"),
                    labels = c("TRUE" = "Over-estimate", "FALSE" = "Under-estimate")) +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  coord_flip() +
  labs(
    title    = paste0("% error — best run (Job ", best_job, ")"),
    subtitle = "% error = 100 × (simulated − observed) / observed",
    x = NULL, y = "% error", fill = NULL
  ) +
  theme_bw(base_size = 13) +
  theme(plot.title = element_text(face = "bold"), legend.position = "bottom",
        panel.grid.minor = element_blank())
```

## Beta estimates

```{r beta-best, fig.height=4}
ggplot(best_val,
       aes(x = reorder(type, beta), y = beta, fill = type)) +
  geom_col(width = 0.65) +
  geom_text(aes(label = formatC(beta, format = "e", digits = 2)),
            hjust = -0.1, size = 3.8) +
  scale_fill_manual(values = type_colours, na.value = "#555555") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.3))) +
  coord_flip() +
  labs(
    title    = paste0("Optimal β per facility type — France-wide (Job ", best_job, ")"),
    subtitle = "Daily within-hospital ESBL transmission rate  |  Search range [1×10⁻⁴, 0.05]",
    x = NULL, y = "β (per day)"
  ) +
  theme_bw(base_size = 13) +
  theme(plot.title = element_text(face = "bold"), legend.position = "none",
        panel.grid.minor = element_blank())
```

---

# 7. Overall assessment

```{r overall-assessment}
sse_ok  <- best_result$sse_final < 0.05
r2_val  <- cor(best_val$incidence_obs, best_val$incidence_sim_mean)^2
r2_ok   <- r2_val > 0.90
mae_val <- mean(abs(best_val$diff))
mae_ok  <- mae_val < 0.5

# Beta stability: CV% across runs per type
cv_vals <- beta_stats$beta_cv
stable  <- all(cv_vals < 30, na.rm = TRUE)

assessment <- data.frame(
  Metric = c("Best total SSE", "R² (sim vs obs)", "Mean abs. error",
             "Runs completed", "Beta stability (max CV%)", "Fit quality"),
  Value = c(
    round(best_result$sse_final, 6),
    round(r2_val, 4),
    paste(round(mae_val, 4), "per 1,000 bed-days"),
    paste(n_jobs, "of 10"),
    paste0(round(max(cv_vals, na.rm = TRUE), 1), "%"),
    ifelse(sse_ok & r2_ok & mae_ok & stable, "✓ Good", "⚠ Review needed")
  ),
  Threshold = c("< 0.05 = good", "> 0.90 = good", "< 0.50 = good",
                "10 = complete", "< 30% = stable", "")
)

assessment %>%
  kable(align = c("l","r","l")) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = FALSE) %>%
  row_spec(6, bold = TRUE,
           background = ifelse(sse_ok & r2_ok & mae_ok & stable,
                               "#d5f5e3", "#fdecea"))
```

---

# 8. Save outputs

```{r save-outputs, results='hide'}
plot_dir <- file.path(OUT_DIR, "analysis")
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)

write.csv2(all_summaries,
           file.path(plot_dir, "all_jobs_validation_summary.csv"),
           row.names = FALSE)
write.csv2(beta_stats,
           file.path(plot_dir, "beta_stability_across_jobs.csv"),
           row.names = FALSE)
write.csv2(quality,
           file.path(plot_dir, "best_job_quality.csv"),
           row.names = FALSE)
write.csv2(sse_by_job,
           file.path(plot_dir, "sse_by_job.csv"),
           row.names = FALSE)

# Save best result as warm start for future runs
warm <- list(
  beta_type_opt   = setNames(best_val$beta, best_val$type),
  objective_value = best_result$sse_final,
  job_index       = best_job,
  datetime        = Sys.time()
)
saveRDS(warm,
        file.path(dirname(OUT_DIR), "warm_start_france.rds"))
```

All tables saved to `Outputs/france/analysis/`.
`warm_start_france.rds` updated with the best β for use in future runs.

---

*Report generated by ARCANE project — MESuRS/Cnam*
*Model: stochastic SIS on PMSI inter-hospital transfer network*
*Calibration target: SPARES ESBL incidence by facility type, France-wide*
