---
title: "ARCANE — France-wide Beta Calibration"
subtitle: "Simulation fit and comparison with regional estimates"
author: "MESuRS/Cnam"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    code_folding: hide
    fig_width: 10
    fig_height: 5.5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE
)
```

```{r libraries}
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(scales)

# Null coalescing operator — returns rhs if lhs is NULL
`%||%` <- function(a, b) if (!is.null(a)) a else b
```

```{r load-data}
# ── Paths ──────────────────────────────────────────────────────────────────────
BASE_DIR <- "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/optim_cluster_jobs"

FRANCE_DIR  <- file.path(BASE_DIR, "Outputs", "france",  "compiled")
REGION_FILE <- file.path(BASE_DIR, "Outputs", "region_cluster", "compiled",
                          "compiled_region.rds")

# ── Load France compiled object ────────────────────────────────────────────────
# Looks for compiled_france_latest.rds first, then any compiled_france_*.rds
latest_file <- file.path(FRANCE_DIR, "compiled_france_latest.rds")
if (file.exists(latest_file)) {
  france_file <- latest_file
} else {
  dated_files <- list.files(FRANCE_DIR, "compiled_france_.*\\.rds$",
                             full.names = TRUE)
  if (length(dated_files) == 0)
    stop("No compiled_france_*.rds in: ", FRANCE_DIR)
  france_file <- tail(sort(dated_files), 1)
}
message("Loading: ", basename(france_file))
cf <- readRDS(france_file)

# ── Load regional compiled object ─────────────────────────────────────────────
has_region <- file.exists(REGION_FILE)
if (has_region) cr <- readRDS(REGION_FILE)

# ── Colour palette ─────────────────────────────────────────────────────────────
type_colours <- c(
  "MCO"     = "#0057B8", "SSR"     = "#C1392B",
  "MCO/SSR" = "#9B1D8A", "PSY"     = "#F5A623",
  "HAD"     = "#00B4D8", "Unknown" = "#555555",
  "Cancer centre (CLCC)"            = "#2ECC71",
  "General public hospital"         = "#0057B8",
  "Private for profit hospital"     = "#E74C3C",
  "Private not-for-profit hospital" = "#9B1D8A",
  "Rehabilitation hospital"         = "#C1392B",
  "University hospital"             = "#F5A623"
)

theme_arcane <- function(base_size = 12) {
  theme_bw(base_size = base_size) +
    theme(plot.title       = element_text(face = "bold", colour = "#0D3B66"),
          plot.subtitle    = element_text(colour = "grey40"),
          panel.grid.minor = element_blank(),
          legend.position  = "right")
}

# ── Extract from correct nested structure ─────────────────────────────────────
# All incidence fields live inside cf$best_result
br <- cf$best_result

beta_france  <- br$beta_type_opt        # named vector: beta per type
inc_obs      <- br$incidence_obs        # named vector: observed incidence
inc_sim      <- br$incidence_final      # named vector: simulated incidence mean
inc_sim_sd   <- br$incidence_final_sd   # named vector: simulated incidence SD

best_sse     <- cf$best_sse
best_job     <- cf$best_job
n_jobs       <- cf$n_jobs
sse_ranking  <- cf$sse_ranking          # data.frame: job_index, sse, file
all_summaries_france <- cf$all_summaries  # all 10 jobs, 60 rows
beta_stats   <- cf$beta_stats           # beta min/med/max/CV across runs

# ── Build france_fit: one row per facility type ───────────────────────────────
types <- names(beta_france)
france_fit <- tibble(
  type         = types,
  beta         = as.numeric(beta_france),
  inc_obs      = as.numeric(inc_obs[types]),
  inc_sim_mean = as.numeric(inc_sim[types]),
  inc_sim_sd   = as.numeric(inc_sim_sd[types])
) %>%
  mutate(
    diff      = inc_sim_mean - inc_obs,
    pct_error = 100 * (inc_sim_mean - inc_obs) / inc_obs,
    sse       = as.numeric(br$sse_final_by_type[types])
  )
```

---

# Part 1 — France-wide calibration

## 1.1 Summary

```{r france-summary-text, results='asis'}
cat(sprintf(
  "**Best job:** %d &nbsp;|&nbsp; **Best SSE:** %.5f &nbsp;|&nbsp;
   **Jobs run:** %d &nbsp;|&nbsp; **Types calibrated:** %d",
  as.integer(best_job), best_sse, as.integer(n_jobs), nrow(france_fit)
))
```

## 1.2 Optimal β per facility type

```{r beta-table}
france_fit %>%
  mutate(
    `β (per day)`            = formatC(beta,          format="e", digits=3),
    `Observed (per 1k bd)`   = round(inc_obs,          3),
    `Simulated (per 1k bd)`  = round(inc_sim_mean,     3),
    `SD`                     = round(inc_sim_sd,       3),
    `Diff`                   = round(diff,             3),
    `% error`                = paste0(round(pct_error, 1), "%"),
    `SSE`                    = round(sse,              5)
  ) %>%
  select(type, `β (per day)`, `Observed (per 1k bd)`,
         `Simulated (per 1k bd)`, `SD`, `Diff`, `% error`, `SSE`) %>%
  kable(align = c("l","r","r","r","r","r","r","r"),
        caption = "France-wide optimal beta per facility type") %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE) %>%
  row_spec(which(abs(france_fit$pct_error) > 20), background = "#fff3cd")
```

<small>Highlighted rows: |% error| > 20%</small>

## 1.3 Observed vs simulated incidence

```{r obs-vs-sim-bar}

france_fit %>%
  pivot_longer(c(inc_obs, inc_sim_mean),
               names_to  = "source",
               values_to = "incidence") %>%
  mutate(
    source = recode(source,
                    inc_obs      = "Observed (SPARES)",
                    inc_sim_mean = "Simulated"),
    ymin = ifelse(source == "Simulated",
                  pmax(incidence - inc_sim_sd, 0), NA_real_),
    ymax = ifelse(source == "Simulated",
                  incidence + inc_sim_sd,           NA_real_)
  ) %>%
  ggplot(aes(x = type, y = incidence, fill = source)) +
  geom_col(position = position_dodge(0.7), width = 0.65, alpha = 0.88) +
  geom_errorbar(aes(ymin = ymin, ymax = ymax),
                position = position_dodge(0.7),
                width = 0.25, linewidth = 0.8, colour = "grey30",
                na.rm = TRUE) +
  scale_fill_manual(values = c("Observed (SPARES)" = "#2980b9",
                                "Simulated"         = "#e67e22"),
                    name = NULL) +
  labs(title    = "Observed vs simulated ESBL-E incidence — France-wide",
      subtitle = "Error bars = +/-1 SD across replicates",
       x = "Facility type", y = "Incidence (per 1,000 bed-days)") +
  theme_arcane() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```

## 1.4 Scatter: observed vs simulated

```{r obs-vs-sim-scatter}
axis_max <- max(c(france_fit$inc_obs,
                   france_fit$inc_sim_mean + france_fit$inc_sim_sd)) * 1.15

ggplot(france_fit, aes(x = inc_obs, y = inc_sim_mean,
                        colour = type, label = type)) +
  geom_abline(slope = 1, intercept = 0,
              linetype = "dashed", colour = "grey40", linewidth = 0.8) +
  geom_errorbar(aes(ymin = pmax(inc_sim_mean - inc_sim_sd, 0),
                    ymax = inc_sim_mean + inc_sim_sd),
                width = 0, alpha = 0.5, linewidth = 0.8) +
  geom_point(size = 5, alpha = 0.9) +
  geom_text(hjust = -0.15, size = 3.5, show.legend = FALSE) +
  scale_colour_manual(values = type_colours, na.value = "#555555") +
  scale_x_continuous(limits = c(0, axis_max)) +
  scale_y_continuous(limits = c(0, axis_max)) +
  coord_fixed() +
  labs(title    = "Simulated vs observed incidence — France-wide",
       subtitle = paste0("SSE = ", round(best_sse, 5),
                          "  |  Dashed = perfect fit"),
       x = "Observed (per 1,000 bed-days)",
       y = "Simulated (per 1,000 bed-days)") +
  theme_arcane() +
  theme(legend.position = "none")
```

## 1.5 % error by type

```{r pct-error}
ggplot(france_fit,
       aes(x = reorder(type, abs(pct_error)), y = pct_error, fill = pct_error)) +
  geom_col(width = 0.65) +
  geom_hline(yintercept = c(-10, 10), linetype = "dashed",
             colour = "grey40", linewidth = 0.7) +
  geom_text(aes(label = paste0(round(pct_error, 1), "%")),
            hjust = ifelse(france_fit$pct_error[order(abs(france_fit$pct_error))] >= 0,
                           -0.15, 1.15),
            size = 3.8) +
  scale_fill_gradient2(low = "#2980b9", mid = "white", high = "#e74c3c",
                       midpoint = 0, guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.2))) +
  coord_flip() +
  labs(title    = "Percentage error by facility type — France-wide",
       subtitle = "Dashed = +/-10% tolerance band",
       x = NULL, y = "% error (simulated − observed) / observed") +
  theme_arcane()
```

## 1.6 SSE across all 10 jobs

```{r sse-jobs}
ggplot(sse_ranking, aes(x = reorder(factor(job_index), sse), y = sse,
                         fill = job_index == best_job)) +
  geom_col(width = 0.7, alpha = 0.88) +
  geom_text(aes(label = round(sse, 5)), hjust = -0.1, size = 3.5) +
  scale_fill_manual(values = c("TRUE" = "#27ae60", "FALSE" = "#2980b9"),
                    guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.25))) +
  coord_flip() +
  labs(title    = "SSE per job — France-wide calibration (all 10 jobs)",
       subtitle = "Green = best job selected | Lower SSE = better fit",
       x = "Job index", y = "SSE") +
  theme_arcane()
```

## 1.7 Observed vs simulated — all 10 jobs

How well did each job fit the observed incidence? Each dot is one type in one job.

```{r all-jobs-obs-sim, fig.height=7}
axis_max_all <- max(c(all_summaries_france$incidence_obs,
                      all_summaries_france$incidence_sim_mean +
                        all_summaries_france$incidence_sim_sd),
                    na.rm = TRUE) * 1.15

all_summaries_france %>%
  mutate(is_best = job_index == best_job,
         job_label = paste0("Job ", job_index,
                             ifelse(job_index == best_job, " ★", ""))) %>%
  ggplot(aes(x = incidence_obs, y = incidence_sim_mean, colour = type)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey40", linewidth = 0.7) +
  geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                    ymax = incidence_sim_mean + incidence_sim_sd),
                width = 0, alpha = 0.35, linewidth = 0.6) +
  geom_point(aes(size = is_best), alpha = 0.85) +
  scale_size_manual(values = c("TRUE" = 4.5, "FALSE" = 2.5), guide = "none") +
  scale_colour_manual(values = type_colours, na.value = "#555555",
                      name = "Type") +
  scale_x_continuous(limits = c(0, axis_max_all)) +
  scale_y_continuous(limits = c(0, axis_max_all)) +
  coord_fixed() +
  facet_wrap(~ reorder(job_label, sse_total), ncol = 5) +
  labs(title    = "Simulated vs observed incidence — all 10 jobs",
       subtitle = "★ = best job (lowest SSE) | Sorted by SSE | Dashed = perfect fit | Error bars = ±1 SD",
       x = "Observed (per 1,000 bed-days)",
       y = "Simulated (per 1,000 bed-days)") +
  theme_arcane(9) +
  theme(strip.background = element_rect(fill = "grey92"),
        strip.text       = element_text(face = "bold", size = 8),
        legend.position  = "bottom")
```

## 1.8 % error by type — all jobs

```{r all-jobs-pct-error, fig.height=6}
all_summaries_france %>%
  mutate(pct_error = 100 * diff / incidence_obs,
         is_best   = job_index == best_job) %>%
  ggplot(aes(x = factor(job_index), y = pct_error, fill = pct_error)) +
  geom_col(width = 0.7) +
  geom_hline(yintercept =  10, linetype = "dashed", colour = "grey50",
             linewidth = 0.7) +
  geom_hline(yintercept =   0, linetype = "solid",  colour = "grey20",
             linewidth = 0.7) +
  geom_hline(yintercept = -10, linetype = "dashed", colour = "grey50",
             linewidth = 0.7) +
  geom_text(aes(label = paste0(round(pct_error, 1), "%"),
                vjust = ifelse(pct_error >= 0, -0.3, 1.2)),
            size = 2.5) +
  scale_fill_gradient2(low = "#2980b9", mid = "white", high = "#e74c3c",
                       midpoint = 0, guide = "none") +
  facet_wrap(~ type, ncol = 3, scales = "free_y") +
  labs(title    = "% error per job by facility type — all 10 jobs",
       subtitle = "Dashed = +/-10% tolerance | Red = over-estimate",
       x = "Job index", y = "% error") +
  theme_arcane(9) +
  theme(strip.background = element_rect(fill = "grey92"),
        strip.text       = element_text(face = "bold", size = 8),
        axis.text.x      = element_text(size = 7))
```

## 1.9 All-jobs summary table

```{r all-jobs-table}
all_summaries_france %>%
  mutate(pct_error = 100 * diff / incidence_obs,
         is_best   = job_index == best_job) %>%
  ggplot(aes(x = factor(job_index), y = pct_error, fill = pct_error)) +
  geom_col(width = 0.7) +
  geom_hline(yintercept =  10, linetype = "dashed", colour = "grey50",
             linewidth = 0.7) +
  geom_hline(yintercept =   0, linetype = "solid",  colour = "grey20",
             linewidth = 0.7) +
  geom_hline(yintercept = -10, linetype = "dashed", colour = "grey50",
             linewidth = 0.7) +
  geom_text(aes(label = paste0(round(pct_error, 1), "%"),
                vjust = ifelse(pct_error >= 0, -0.3, 1.2)),
            size = 2.5) +
  scale_fill_gradient2(low = "#2980b9", mid = "white", high = "#e74c3c",
                       midpoint = 0, guide = "none") +
  facet_wrap(~ type, ncol = 3, scales = "free_y") +
  labs(title    = "% error per job by facility type — all 10 jobs",
       subtitle = "Dashed = +/-10% tolerance | Red = over-estimate",
       x = "Job index", y = "% error") +
  theme_arcane(9) +
  theme(strip.background = element_rect(fill = "grey92"),
        strip.text       = element_text(face = "bold", size = 8),
        axis.text.x      = element_text(size = 7))
```

```{r beta-variability}
all_summaries_france %>%
  ggplot(aes(x = reorder(type, beta, FUN = median), y = beta)) +
  geom_boxplot(width = 0.45, outlier.shape = NA,
               fill = "#d6eaf8", colour = "#2980b9", linewidth = 0.6) +
  geom_jitter(aes(colour = factor(job_index)), width = 0.15, size = 2.5, alpha = 0.8) +
  geom_point(data = france_fit, aes(x = type, y = beta),
             shape = 18, size = 5, colour = "#e74c3c") +
  scale_y_log10(labels = scientific) +
  scale_colour_viridis_d(name = "Job") +
  coord_flip() +
  labs(title    = "Beta estimates across all 10 jobs by facility type",
       subtitle = "◆ = best job (job 2) | Box = IQR across runs | Log scale",
       x = NULL, y = "β (per day, log scale)") +
  theme_arcane()
```

```{r beta-cv-table}
beta_stats %>%
  mutate(
    `b best`   = formatC(beta_best, format = "e", digits = 3),
    `b median` = formatC(beta_med,  format = "e", digits = 3),
    `b min`    = formatC(beta_min,  format = "e", digits = 3),
    `b max`    = formatC(beta_max,  format = "e", digits = 3),
    `CV (%)`   = round(beta_cv, 1)
  ) %>%
  select(type, n_runs, `b best`, `b median`, `b min`, `b max`, `CV (%)`) %>%
  rename("Facility type" = type, "Jobs" = n_runs) %>%
  kable(col.names = c("Facility type", "Jobs",
                      "beta best", "beta median", "beta min", "beta max", "CV (%)"),
        align = c("l","c","r","r","r","r","r"),
        caption = "Beta variability across all 10 France-wide calibration jobs. CV = coefficient of variation.") %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE) %>%
  footnote(general = "Low CV = consistent convergence across jobs. High CV may indicate a flat likelihood surface for that type.")
```

## 1.10 Within-job convergence — starts in best job

Each job runs **`r length(cf$best_result$fit_values)` starting points** (3 structured: warm start, ×1.5, ×0.67; plus 2 random perturbations). Nelder-Mead runs independently from each start and the lowest-SSE start is selected as that job's result.

```{r starts-best-job}
start_df <- tibble(
  start_id  = names(cf$best_result$fit_values),
  sse       = as.numeric(cf$best_result$fit_values),
  is_best   = seq_along(cf$best_result$fit_values) ==
                as.integer(cf$best_result$best_fit_id),
  converged = sapply(cf$best_result$fits,
                     function(s) s$convergence == 0)
) %>%
  mutate(
    start_label = paste0(start_id,
                          ifelse(is_best, " \u2605", ""),
                          ifelse(!converged, " (no conv.)", ""))
  )

ggplot(start_df, aes(x = reorder(start_label, sse), y = sse,
                      fill = is_best)) +
  geom_col(width = 0.65, alpha = 0.88) +
  geom_text(aes(label = round(sse, 5)), hjust = -0.1, size = 3.8) +
  scale_fill_manual(values = c("TRUE" = "#27ae60", "FALSE" = "#2980b9"),
                    guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.25))) +
  coord_flip() +
  labs(title    = paste0("SSE per starting point — best job (job ", best_job, ")"),
       subtitle = "Star = selected start  |  Each start = independent Nelder-Mead trajectory",
       x = NULL, y = "SSE") +
  theme_arcane()
```

```{r starts-table}
start_df %>%
  left_join(
    bind_rows(lapply(names(cf$best_result$fits), function(s) {
      f <- cf$best_result$fits[[s]]
      tibble(start_id         = s,
             nm_evals         = as.integer(f$counts["function"]),
             convergence_code = f$convergence)
    })),
    by = "start_id"
  ) %>%
  mutate(
    sse              = round(sse, 5),
    convergence_flag = case_when(
      convergence_code == 0 ~ "Converged",
      convergence_code == 1 ~ "Max iterations reached",
      TRUE                   ~ paste0("Code ", convergence_code)
    )
  ) %>%
  select(start_label, sse, nm_evals, convergence_flag) %>%
  rename("Start"       = start_label,
         "SSE"         = sse,
         "NM evals"    = nm_evals,
         "Convergence" = convergence_flag) %>%
  kable(align = c("l","r","r","l"),
        caption = paste0("Starting points within best job (job ", best_job,
                          "). NM evals = objective function calls used.")) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = FALSE) %>%
  row_spec(which(start_df$is_best), background = "#d5f5e3") %>%
  footnote(general = paste0(
    "Starts 1-3: structured (warm start, x1.5, x0.67 perturbations). ",
    "Starts 4-5: random perturbations. ",
    "Max iterations reached (code 1) is normal behaviour for Nelder-Mead."
  ))
```

---

# Part 2 — France vs Regional comparison

```{r check-region}
if (!has_region) {
  cat("> **Regional compiled object not found at:**\n>",
      REGION_FILE,
      "\n> Skipping Part 2.")
  knitr::knit_exit()
}
```

```{r prep-regional}
all_summaries <- cr$all_summaries   # type × region with beta, H_region

# Recompute weighted beta summary from regional data
set.seed(42)
n_boot <- 1000
weighted_beta_summary <- all_summaries %>%
  filter(!is.na(beta), !is.na(H_region), beta > 0) %>%
  group_by(type) %>%
  group_modify(function(d, key) {
    w <- d$H_region; log_b <- log(d$beta); n <- nrow(d)
    wgm <- exp(sum(w * log_b) / sum(w))
    boot_wgm <- replicate(n_boot, {
      idx <- sample(seq_len(n), n, replace = TRUE)
      bd <- d[idx, ]; wd <- w[idx]
      exp(sum(wd * log(bd$beta)) / sum(wd))
    })
    data.frame(
      wgm       = round(wgm, 6),
      ci_lo     = round(quantile(boot_wgm, 0.025), 6),
      ci_hi     = round(quantile(boot_wgm, 0.975), 6),
      n_regions = n, stringsAsFactors = FALSE
    )
  }) %>% ungroup()

# Join France estimate into regional summary — both use full type names
comparison <- weighted_beta_summary %>%
  left_join(france_fit %>% select(type, beta_france = beta), by = "type") %>%
  mutate(
    ratio      = round(beta_france / wgm, 3),
    log2_ratio = round(log2(beta_france / wgm), 3),
    agreement  = case_when(
      is.na(beta_france)                              ~ "No France estimate",
      beta_france >= ci_lo & beta_france <= ci_hi     ~ "Within regional 95% CI",
      beta_france <  ci_lo                            ~ "Below regional CI",
      beta_france >  ci_hi                            ~ "Above regional CI",
      TRUE                                            ~ "No regional data"
    )
  )
```

## 2.1 France β vs regional distribution

```{r france-vs-region-boxplot}
# Regional dots + France estimate overlay
ggplot(all_summaries %>% filter(!is.na(beta)),
       aes(x = reorder(type, beta, FUN = median), y = beta)) +
  geom_boxplot(width = 0.45, outlier.shape = NA,
               fill = "#d6eaf8", colour = "#2980b9", linewidth = 0.6) +
  geom_jitter(aes(colour = region), width = 0.18, size = 2.2, alpha = 0.75) +
  geom_point(data = france_fit,
             aes(x = type, y = beta),
             shape = 18, size = 6, colour = "#e74c3c") +
  geom_text(data = france_fit,
            aes(x = type, y = beta,
                label = formatC(beta, format = "e", digits = 1)),
            hjust = -0.2, size = 3.2, colour = "#c0392b") +
  scale_y_log10(labels = scientific) +
  scale_colour_viridis_d(name = "Region", guide = guide_legend(ncol = 2)) +
  coord_flip() +
  labs(title    = "France-wide β estimate vs regional distribution by type",
       subtitle = "◆ = France-wide estimate (red)  |  Dots = individual regions  |  Log scale",
       x = NULL, y = "β (per day, log scale)") +
  theme_arcane(11)
```

## 2.2 France β vs regional weighted geometric mean + 95% CI

```{r france-vs-wgm}
ggplot(comparison %>% filter(!is.na(wgm)),
       aes(x = reorder(type, wgm))) +
  geom_col(aes(y = wgm), fill = "#2980b9", width = 0.5, alpha = 0.7) +
  geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi),
                width = 0.3, linewidth = 1, colour = "#1a5276") +
  geom_point(aes(y = beta_france), shape = 18, size = 5,
             colour = "#e74c3c") +
  geom_text(aes(y = pmax(ci_hi, beta_france) * 1.05,
                label = formatC(beta_france, format = "e", digits = 1)),
            size = 3.2, colour = "#c0392b") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.3)),
                     labels = scientific) +
  coord_flip() +
  labs(title    = "France-wide β vs regional weighted geometric mean",
       subtitle = "Bar = regional wgm  |  Error bars = 95% bootstrap CI  |  ◆ = France estimate",
       x = NULL, y = "β (per day)") +
  theme_arcane()
```

## 2.3 Log₂ ratio: France vs regional wgm

```{r log2-ratio}
ggplot(comparison %>% filter(!is.na(log2_ratio)),
       aes(x = reorder(type, log2_ratio), y = log2_ratio,
           fill = log2_ratio)) +
  geom_col(width = 0.65) +
  geom_hline(yintercept = c(-1, 0, 1), linetype = c("dashed","solid","dashed"),
             colour = c("grey50","grey20","grey50"), linewidth = 0.8) +
  geom_text(aes(label = round(log2_ratio, 2)),
            hjust = ifelse(comparison$log2_ratio[order(comparison$log2_ratio)] >= 0,
                           -0.15, 1.15),
            size = 3.8) +
  scale_fill_gradient2(low = "#2980b9", mid = "white", high = "#e74c3c",
                       midpoint = 0, guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0.25, 0.25))) +
  coord_flip() +
  labs(title    = "France vs regional wgm — log₂ ratio",
       subtitle = "0 = perfect agreement  |  Dashed = ±1 (2-fold difference)",
       x = NULL, y = "log₂(β_France / β_regional_wgm)") +
  theme_arcane()
```

## 2.4 Comparison table

```{r comparison-table}
agreement_colours <- c(
  "Within regional 95% CI" = "#d5f5e3",
  "Below regional CI"      = "#d6eaf8",
  "Above regional CI"      = "#fde8d8",
  "No regional data"       = "#f2f3f4"
)

comparison %>%
  filter(!is.na(wgm)) %>%
  mutate(
    `Regional wgm`  = formatC(wgm,          format = "e", digits = 3),
    `95% CI`        = paste0("[", formatC(ci_lo, format="e", digits=2),
                               " – ", formatC(ci_hi, format="e", digits=2), "]"),
    `France β`      = formatC(beta_france,   format = "e", digits = 3),
    `Ratio F/R`     = round(ratio, 3),
    `log₂(F/R)`     = round(log2_ratio, 3),
    `Regions`       = n_regions
  ) %>%
  select(type, Regions, `Regional wgm`, `95% CI`,
         `France β`, `Ratio F/R`, `log₂(F/R)`, agreement) %>%
  rename("Facility type" = type,
         "Agreement"     = agreement) %>%
  kable(align = c("l","c","r","r","r","r","r","l"),
        caption = paste0("France-wide β vs regional weighted geometric mean. ",
                          "Ratio = France β / regional wgm. ",
                          "Log₂ ratio > 0 means France estimate is higher.")) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE) %>%
  column_spec(8, background = agreement_colours[comparison$agreement[!is.na(comparison$wgm)]])
```

## 2.5 Per-region deviation from France estimate

```{r region-deviation}
all_summaries %>%
  filter(!is.na(beta)) %>%
  left_join(france_fit %>% select(type, beta_france = beta),
            by = "type") %>%
  mutate(log2_dev = log2(beta / beta_france),
         region   = gsub("_", " ", region)) %>%
  ggplot(aes(x = type, y = reorder(region, log2_dev, FUN = median),
             fill = log2_dev)) +
  geom_tile(colour = "white", linewidth = 0.4) +
  geom_text(aes(label = round(log2_dev, 1)), size = 2.5) +
  scale_fill_gradient2(low = "#2980b9", mid = "white", high = "#e74c3c",
                       midpoint = 0, limits = c(-2, 2), oob = squish,
                       name = "log₂(β_region/β_France)") +
  labs(title    = "Regional β deviation from France-wide estimate",
       subtitle = "Red = region higher than France  |  Blue = lower  |  White = agreement",
       x = "Facility type", y = NULL) +
  theme_arcane(10) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1),
        panel.grid   = element_blank())
```

---

# Part 3 — Summary

```{r summary-table}
# Combined summary: France beta + regional context
summary_out <- france_fit %>%
  left_join(comparison %>% select(type, wgm, ci_lo, ci_hi, agreement),
            by = "type") %>%
  mutate(
    `β (France)`    = formatC(beta,     format = "e", digits = 3),
    `β (reg. wgm)`  = formatC(wgm,      format = "e", digits = 2),
    `reg. 95% CI`   = paste0("[", formatC(ci_lo, format="e", digits=1),
                               ", ", formatC(ci_hi, format="e", digits=1), "]"),
    `Inc obs`       = round(inc_obs,      3),
    `Inc sim`       = round(inc_sim_mean, 3),
    `% error`       = paste0(round(pct_error, 1), "%"),
    `Agreement`     = coalesce(agreement, "—")
  ) %>%
  select(type, `β (France)`, `β (reg. wgm)`, `reg. 95% CI`,
         `Inc obs`, `Inc sim`, `% error`, `Agreement`) %>%
  rename("Facility type" = type)

summary_out %>%
  kable(align = c("l","r","r","r","r","r","r","l"),
        caption = "Combined France-wide and regional beta estimates with fit metrics") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) %>%
  footnote(general = paste0(
    "β (France) = optimal beta from France-wide Nelder-Mead calibration. ",
    "β (reg. wgm) = weighted geometric mean across regional calibrations. ",
    "% error = (simulated − observed) / observed × 100."
  ))
```

---

*Generated `r format(Sys.time(), "%Y-%m-%d %H:%M")` from `r basename(france_file)` and `r if(has_region) basename(REGION_FILE) else "no regional file"`.*
