---
title: "ARCANE — Regional Beta Calibration: All Regions"
subtitle: "ESBL Transmission Rate by Region and Facility Type"
author: "ARCANE Project — MESuRS/Cnam"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
    highlight: tango
    fig_width: 12
    fig_height: 7
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center"
)
```

```{r libraries}
library(dplyr)
library(ggplot2)
library(tidyr)
library(knitr)
library(kableExtra)
library(scales)
```

```{r load-compiled}
# Run compile_region.R first, then knit this document.
COMPILED_FILE <- file.path(
  "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/optim_cluster_jobs",
  "Outputs", "region", #_cluster", 
  "compiled", "compiled_region.rds"
)
if (!file.exists(COMPILED_FILE))
  stop("Run compile_region.R first.\nExpected: ", COMPILED_FILE)

compiled      <- readRDS(COMPILED_FILE)
all_summaries <- compiled$all_summaries
all_run_sse   <- compiled$all_run_sse
beta_wide     <- compiled$beta_wide
sse_summary   <- compiled$sse_summary
results       <- compiled$results
all_regions   <- compiled$regions
n_regions     <- compiled$n_regions

# Colour palette for facility types
type_colours <- c(
  "General public hospital"         = "#0057B8",
  "University hospital"             = "#F5A623",
  "Private for profit hospital"     = "#E74C3C",
  "Private not-for-profit hospital" = "#9B1D8A",
  "Rehabilitation hospital"         = "#C1392B",
  "Cancer centre (CLCC)"            = "#2ECC71",
  "MCO"     = "#0057B8", "SSR"     = "#C1392B",
  "MCO/SSR" = "#9B1D8A", "PSY"     = "#F5A623",
  "HAD"     = "#00B4D8", "Unknown" = "#555555"
)
```

```{r recompute-sse-summary}
# Recompute with normalised metrics so Rmd works regardless of compile version
sse_summary <- all_summaries %>%
  group_by(region, H_region, sse_total) %>%
  summarise(n_types = n(), .groups = "drop") %>%
  mutate(
    sse_per_type = round(sse_total / n_types, 6),
    mape = sapply(region, function(r) {
      d <- filter(all_summaries, region == r)
      round(mean(abs(d$diff / d$incidence_obs) * 100, na.rm = TRUE), 2)
    }),
    r2 = sapply(region, function(r) {
      d <- filter(all_summaries, region == r)
      if (nrow(d) < 2) return(NA_real_)
      round(cor(d$incidence_obs, d$incidence_sim_mean,
                use = "complete.obs")^2, 4)
    })
  ) %>%
  arrange(mape)
```

---

# Overview

This report covers **`r n_regions` French administrative regions**, each calibrated
independently using a stochastic SIS network model on the PMSI inter-hospital
transfer network.  Beta (β) — the daily within-hospital ESBL transmission rate —
is estimated separately per **facility type** within each region.

---

# Part 1 — Cross-regional comparison

*Each plot in this section shows all `r n_regions` regions together, making it
easy to spot regional patterns, outliers, and types that are hard to calibrate.*

---

## 1.1 Calibration quality by region (SSE)

**What this shows:** Total SSE (sum of squared errors) for the best optimisation
run in each region.  Lower = closer fit between simulated and observed ESBL
incidence.  Regions with higher SSE may have fewer hospitals, sparser SPARES data,
or more complex epidemiological patterns that are harder to reproduce with a
France-wide model structure.

```{r sse-by-region, fig.height=6}
sse_summary %>%
  mutate(region = gsub("_", " ", region)) %>%
  ggplot(aes(x = reorder(region, mape), y = mape, fill = mape)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = paste0(round(mape, 1), "%")), hjust = -0.1, size = 3.3) +
  scale_fill_gradient(low = "#2ecc71", high = "#e74c3c", guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.25))) +
  coord_flip() +
  labs(
    title    = "Calibration quality by region — MAPE (scale-free)",
    subtitle = paste0("Mean absolute % error between simulated and observed incidence.\n",
                      "Unlike raw SSE, MAPE is not biased by region size or number of types."),
    x = NULL, y = "MAPE (%)"
  ) +
  theme_bw(base_size = 12) +
  theme(plot.title = element_text(face = "bold"),
        panel.grid.minor = element_blank())
```

---

## 1.2 Beta by region and facility type (heatmap)

**What this shows:** The optimal β for every region × facility type combination.
Each cell is the daily within-hospital ESBL transmission rate.  Darker cells =
higher transmission.

- **Patterns across columns** (types): if one type consistently has higher β
  across most regions, that type has inherently faster transmission nationally
- **Patterns across rows** (regions): if one region has consistently higher β
  across all types, that region may have higher overall transmission pressure
  (hygiene infrastructure, antibiotic pressure, patient case mix)
- **Missing cells**: the type was absent or had no SPARES data in that region

```{r beta-heatmap, fig.height=7}
heatmap_data <- all_summaries %>%
  mutate(region = gsub("_", " ", region)) %>%
  filter(!is.na(beta))

ggplot(heatmap_data,
       aes(x = type, y = reorder(region, sse_total),
           fill = beta)) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = formatC(beta, format = "e", digits = 1)),
            size = 2.8) +
  scale_fill_viridis_c(name = "β (per day)", option = "plasma",
                       trans = "log10",
                       labels = scales::scientific) +
  labs(
    title    = "Optimal β per facility type × region",
    subtitle = "Log10 colour scale  |  Empty = no SPARES data for this type in this region",
    x = "Facility type", y = "Region (sorted by SSE, best at top)"
  ) +
  theme_bw(base_size = 11) +
  theme(plot.title    = element_text(face = "bold"),
        axis.text.x   = element_text(angle = 35, hjust = 1),
        legend.position = "right",
        panel.grid    = element_blank())
```

---

## 1.3 Beta distribution across regions by facility type

**What this shows:** For each facility type, the spread of β estimates across all
regions — shown as a boxplot with individual region points.  Wide boxes = high
regional variability (β differs a lot by region). Narrow boxes = the national
signal is consistent.

```{r beta-boxplot, fig.height=6}
all_summaries %>%
  filter(!is.na(beta)) %>%
  mutate(region = gsub("_", " ", region)) %>%
  ggplot(aes(x = reorder(type, beta, FUN = median), y = beta)) +
  geom_boxplot(width = 0.4, outlier.shape = NA,
               fill = "#d6eaf8", colour = "#2980b9", linewidth = 0.6) +
  geom_jitter(aes(colour = gsub("_", " ", region)),
              width = 0.15, size = 2, alpha = 0.8) +
  scale_y_log10(labels = scales::scientific) +
  scale_colour_viridis_d(name = "Region", guide = guide_legend(ncol = 2)) +
  labs(
    title    = "Beta estimates across regions by facility type",
    subtitle = "Each dot = one region  |  Log scale  |  Box = IQR",
    x = NULL, y = "β (per day, log scale)"
  ) +
  coord_flip() +
  theme_bw(base_size = 12) +
  theme(plot.title      = element_text(face = "bold"),
        legend.position = "right",
        panel.grid.minor = element_blank())
```

---

## 1.4 Observed vs simulated incidence — all regions, all types

**What this shows:** Every region × type combination in one scatter plot.
Points on the dashed diagonal = perfect fit.  Colour = region, shape = facility type.
This is the most comprehensive single view of calibration quality.

```{r obs-vs-sim-all, fig.height=7}
all_summaries %>%
  filter(!is.na(incidence_obs) & !is.na(incidence_sim_mean)) %>%
  mutate(region = gsub("_", " ", region)) %>%
  ggplot(aes(x = incidence_obs, y = incidence_sim_mean,
             colour = region)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey40", linewidth = 0.8) +
  geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                    ymax = incidence_sim_mean + incidence_sim_sd),
                width = 0, alpha = 0.35, linewidth = 0.6) +
  geom_point(aes(shape = type), size = 3, alpha = 0.85) +
  scale_colour_viridis_d(name = "Region",
                         guide = guide_legend(ncol = 2, override.aes = list(size=3))) +
  scale_shape_manual(values = c(16,17,15,18,8,4,3,1,0,2,5,6)[
    seq_along(unique(all_summaries$type))],
    name = "Facility type") +
  labs(
    title    = "Simulated vs observed ESBL incidence — all regions and types",
    subtitle = "Dashed = perfect fit  |  Error bars = ±1 SD across replicates",
    x = "Observed (SPARES, per 1,000 bed-days)",
    y = "Simulated (per 1,000 bed-days)"
  ) +
  theme_bw(base_size = 12) +
  theme(plot.title = element_text(face = "bold"),
        legend.position = "right",
        panel.grid.minor = element_blank())
```

---

## 1.5 Observed vs simulated — faceted by region

**What this shows:** Same data as above but split into one panel per region,
making it easier to assess the fit for each region individually.

```{r obs-vs-sim-facet, fig.height=14, fig.width=13}
all_summaries %>%
  filter(!is.na(incidence_obs) & !is.na(incidence_sim_mean)) %>%
  mutate(region_label = paste0(gsub("_", " ", region),
                                "\nSSE = ", round(sse_total, 4))) %>%
  ggplot(aes(x = incidence_obs, y = incidence_sim_mean,
             colour = type)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey50") +
  geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                    ymax = incidence_sim_mean + incidence_sim_sd),
                width = 0, alpha = 0.4) +
  geom_point(size = 3) +
  facet_wrap(~ region_label, ncol = 4, scales = "free") +
  scale_colour_manual(values = type_colours, na.value = "#555555",
                      name = "Type") +
  labs(
    title = "Simulated vs observed incidence — by region",
    x = "Observed (per 1,000 bed-days)",
    y = "Simulated (per 1,000 bed-days)"
  ) +
  theme_bw(base_size = 10) +
  theme(plot.title       = element_text(face = "bold"),
        legend.position  = "bottom",
        strip.background = element_rect(fill = "grey92"),
        panel.grid.minor = element_blank())
```

---

## 1.6 Percentage error by region and type

**What this shows:** How far off the simulation is for each region × type, as
a percentage of the observed rate.  Red = over-estimate, blue = under-estimate,
white = near-perfect.  Reveals systematic biases — e.g. if a type is always
under-estimated in all regions, the model may be missing something structural.

```{r pct-error-heatmap, fig.height=7}
all_summaries %>%
  mutate(pct_error = 100 * diff / incidence_obs,
         region    = gsub("_", " ", region)) %>%
  filter(!is.na(pct_error)) %>%
  ggplot(aes(x = type, y = reorder(region, sse_total),
             fill = pct_error)) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = paste0(ifelse(pct_error > 0, "+", ""),
                               round(pct_error, 1), "%")),
            size = 2.8) +
  scale_fill_gradient2(low = "#2980b9", mid = "white", high = "#e74c3c",
                       midpoint = 0, limits = c(-50, 50), oob = scales::squish,
                       name = "% error") +
  labs(
    title    = "Percentage error by region and facility type",
    subtitle = "Red = over-estimate  |  Blue = under-estimate  |  White = near-perfect",
    x = "Facility type", y = "Region"
  ) +
  theme_bw(base_size = 11) +
  theme(plot.title   = element_text(face = "bold"),
        axis.text.x  = element_text(angle = 35, hjust = 1),
        panel.grid   = element_blank())
```

---

## 1.7 Beta variability across regions by type

**What this shows:** How consistent β is across regions for each facility type.
CV% = coefficient of variation (standard deviation / mean × 100).
A high CV% means β varies a lot between regions — the national estimate may be
masking important regional differences.

```{r beta-cv-table}
compiled$beta_type_stats %>%
  rename(
    "Facility type"        = type,
    "Regions with data"    = n_regions,
    "Min β"                = beta_min,
    "Median β"             = beta_med,
    "Max β"                = beta_max,
    "CV% (regional spread)"= beta_cv
  ) %>%
  kable(align = c("l","c","r","r","r","r")) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) %>%
  footnote(general = paste0(
    "CV% = standard deviation / mean × 100 across regions. ",
    "Low CV% = β is consistent across regions (national estimate is reliable). ",
    "High CV% = large regional variation (region-specific β adds important nuance)."
  ))
```

---

## 1.8 Hospitals per region

```{r hosp-per-region, fig.height=5}
all_summaries %>%
  distinct(region, H_region) %>%
  mutate(region = gsub("_", " ", region)) %>%
  ggplot(aes(x = reorder(region, H_region), y = H_region,
             fill = H_region)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = H_region), hjust = -0.2, size = 3.5) +
  scale_fill_gradient(low = "#aed6f1", high = "#1a5276", guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  coord_flip() +
  labs(title = "Number of hospitals in each regional sub-network",
       subtitle = "After subsetting the national transfer network to within-region transfers",
       x = NULL, y = "Hospitals (H)") +
  theme_bw(base_size = 12) +
  theme(plot.title = element_text(face = "bold"),
        panel.grid.minor = element_blank())
```

---

## 1.8 National beta summary per facility type

**What this shows:** A single national β estimate per facility type, synthesising
all regional calibrations into one number with appropriate uncertainty.

**Weighted geometric mean** (weights = number of hospitals per region):
regions with more hospitals contribute more because their beta estimate is based
on more data and is therefore more reliable.

**Why geometric mean:** Beta is always positive and right-skewed across regions —
the geometric mean (mean of log-beta, back-transformed) is the natural summary
for a rate parameter.

**95% CI from bootstrap:** With only `r n_regions` regions, a normal-distribution
CI is unreliable. The CI is computed by resampling regions 2,000 times in log-space.

**Weighted median + IQR:** Shown alongside as a robustness check — insensitive
to outlier regions.

```{r compute-weighted-beta}
# Computed here so the table works regardless of compile_region.R version
set.seed(42)
n_boot <- 2000

weighted_beta_summary <- all_summaries %>%
  filter(!is.na(beta), !is.na(H_region), beta > 0) %>%
  group_by(type) %>%
  group_modify(function(d, key) {
    w     <- d$H_region
    log_b <- log(d$beta)
    n     <- nrow(d)
    wgm   <- exp(sum(w * log_b) / sum(w))
    w_norm <- pmax(round(w / min(w) * 10), 1L)
    b_rep  <- rep(d$beta, w_norm)
    wmed   <- median(b_rep)
    wq25   <- quantile(b_rep, 0.25)
    wq75   <- quantile(b_rep, 0.75)
    boot_wgm <- replicate(n_boot, {
      idx <- sample(seq_len(n), n, replace = TRUE)
      bd  <- d[idx, ]; wd <- w[idx]
      exp(sum(wd * log(bd$beta)) / sum(wd))
    })
    data.frame(
      n_regions    = n,
      total_weight = round(sum(w)),
      wgm          = round(wgm,                       6),
      ci_lo_95     = round(quantile(boot_wgm, 0.025), 6),
      ci_hi_95     = round(quantile(boot_wgm, 0.975), 6),
      w_median     = round(wmed, 6),
      w_iqr_lo     = round(wq25, 6),
      w_iqr_hi     = round(wq75, 6),
      stringsAsFactors = FALSE
    )
  }) %>%
  ungroup()
```

```{r national-beta-table}
weighted_beta_summary %>%
  mutate(
    `Weighted geom. mean` = formatC(wgm,      format = "e", digits = 3),
    `95% CI`              = paste0("[", formatC(ci_lo_95, format = "e", digits = 2),
                                    " – ",
                                    formatC(ci_hi_95, format = "e", digits = 2), "]"),
    `Weighted median`     = formatC(w_median, format = "e", digits = 3),
    `IQR`                 = paste0("[", formatC(w_iqr_lo, format = "e", digits = 2),
                                    " – ",
                                    formatC(w_iqr_hi, format = "e", digits = 2), "]")
  ) %>%
  select(type, n_regions, total_weight,
         `Weighted geom. mean`, `95% CI`, `Weighted median`, `IQR`) %>%
  rename("Facility type"             = type,
         "Regions"                   = n_regions,
         "Total hospitals (weight)"  = total_weight) %>%
  kable(align = c("l","c","r","r","r","r","r")) %>%
  kable_styling(bootstrap_options = c("striped","hover"), full_width = TRUE) %>%
  footnote(general = paste0(
    "Weighted geometric mean: exp(sum(w_r x log(beta_r)) / sum(w_r)) where w_r = ",
    "hospitals in region r for that type. ",
    "95% CI from 2,000 bootstrap resamplings of regions in log-space. ",
    "Weighted median and IQR computed by repeating each region proportional to its weight."
  ))
```

```{r national-beta-plot, fig.height=5}
weighted_beta_summary %>%
  ggplot(aes(x = reorder(type, wgm), y = wgm)) +
  geom_col(fill = "#2980b9", width = 0.6, alpha = 0.85) +
  geom_errorbar(aes(ymin = ci_lo_95, ymax = ci_hi_95),
                width = 0.25, linewidth = 0.9, colour = "#1a5276") +
  geom_point(aes(y = w_median), shape = 18, size = 4, colour = "#e74c3c") +
  geom_text(aes(label = formatC(wgm, format = "e", digits = 2),
                y = ci_hi_95),
            vjust = -0.6, size = 3.3) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.3))) +
  coord_flip() +
  labs(
    title    = "National β per facility type — weighted geometric mean across regions",
    subtitle = paste0("Bar = weighted geometric mean  |  ",
                      "Error bars = 95% bootstrap CI  |  ",
                      "◆ = weighted median"),
    x = NULL, y = "β (per day)"
  ) +
  theme_bw(base_size = 12) +
  theme(plot.title = element_text(face = "bold"),
        panel.grid.minor = element_blank())
```

---

# Part 2 — Individual region reports

*One section per region with the same diagnostics as the regional Rmd.*

```{r region-loop, results='asis', echo=FALSE, fig.height=5, fig.width=10}
for (rname in all_regions) {

  r     <- results[[rname]]
  val   <- r$validation_summary
  rdisp <- gsub("_", " ", rname)

  cat("\n\n---\n\n")
  cat("## ", rdisp, "\n\n")

  # ── Metadata ────────────────────────────────────────────────────────────────
  cat("**Hospitals in region:**", r$H_region,
      " | **SSE:**", round(r$sse_final, 6),
      " | **Types:**", paste(names(r$incidence_obs), collapse = ", "), "\n\n")

  # ── Observed vs simulated ──────────────────────────────────────────────────
  cat("### Observed vs simulated incidence\n\n")

  axis_max <- max(c(val$incidence_obs,
                    val$incidence_sim_mean + val$incidence_sim_sd),
                  na.rm = TRUE) * 1.15

  p <- ggplot(val, aes(x = incidence_obs, y = incidence_sim_mean,
                       colour = type)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed",
                colour = "grey40", linewidth = 0.9) +
    geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                      ymax = incidence_sim_mean + incidence_sim_sd),
                  width = 0, linewidth = 0.9, alpha = 0.5) +
    geom_point(size = 5) +
    geom_text(aes(label = type), hjust = -0.12, size = 3.3,
              show.legend = FALSE) +
    scale_colour_manual(values = type_colours, na.value = "#555555") +
    scale_x_continuous(limits = c(0, axis_max)) +
    scale_y_continuous(limits = c(0, axis_max)) +
    coord_fixed() +
    labs(title = paste0("Simulated vs observed — ", rdisp),
         subtitle = paste0("SSE = ", round(r$sse_final, 4),
                           "  |  ±1 SD across ", r$n_rep_valid, " replicates"),
         x = "Observed (per 1,000 bed-days)",
         y = "Simulated (per 1,000 bed-days)") +
    theme_bw(base_size = 12) +
    theme(plot.title = element_text(face = "bold"),
          legend.position = "none", panel.grid.minor = element_blank())

  print(p)
  cat("\n\n")

  # ── Beta estimates ──────────────────────────────────────────────────────────
  cat("### Beta estimates\n\n")

  p2 <- ggplot(val, aes(x = reorder(type, beta), y = beta, fill = type)) +
    geom_col(width = 0.65) +
    geom_text(aes(label = formatC(beta, format = "e", digits = 2)),
              hjust = -0.1, size = 3.5) +
    scale_fill_manual(values = type_colours, na.value = "#555555") +
    scale_y_continuous(expand = expansion(mult = c(0, 0.35))) +
    coord_flip() +
    labs(title = paste0("Optimal β — ", rdisp),
         x = NULL, y = "β (per day)") +
    theme_bw(base_size = 12) +
    theme(plot.title = element_text(face = "bold"),
          legend.position = "none", panel.grid.minor = element_blank())

  print(p2)
  cat("\n\n")

  # ── Numerical table ─────────────────────────────────────────────────────────
  cat("### Numerical summary\n\n")

  tbl <- val %>%
    mutate(pct_error = round(100 * diff / incidence_obs, 1)) %>%
    select(type, beta, incidence_obs, incidence_sim_mean,
           incidence_sim_sd, pct_error, sse)

  print(kable(tbl, digits = 4,
              col.names = c("Type", "β", "Observed", "Sim mean",
                            "Sim SD", "% error", "SSE"),
              align = c("l","r","r","r","r","r","r")) %>%
          kable_styling(bootstrap_options = c("striped","condensed"),
                        full_width = FALSE))

  cat("\n\n")
}
```

---

*Report generated by ARCANE project — MESuRS/Cnam*
