---
title: "ARCANE — Regional Beta Calibration"
subtitle: "ESBL Transmission Rate by Region and Facility Type"
author: "MESuRS/Cnam"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  powerpoint_presentation:
    slide_level: 2
    fig_width: 10
    fig_height: 5.5
    reference_doc: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  dpi     = 150
)
```

```{r libraries}
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(knitr)
```

```{r load-data}
COMPILED_FILE <- file.path(
  "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/optim_cluster_jobs",
  "Outputs", "region_cluster", "compiled", "compiled_region.rds"
)
if (!file.exists(COMPILED_FILE))
  stop("Run compile_region.R first.\nExpected: ", COMPILED_FILE)

compiled      <- readRDS(COMPILED_FILE)
all_summaries <- compiled$all_summaries
results       <- compiled$results
all_regions   <- compiled$regions
n_regions     <- compiled$n_regions

type_colours <- c(
  "General public hospital"         = "#0057B8",
  "University hospital"             = "#F5A623",
  "Private for profit hospital"     = "#E74C3C",
  "Private not-for-profit hospital" = "#9B1D8A",
  "Rehabilitation hospital"         = "#C1392B",
  "Cancer centre (CLCC)"            = "#2ECC71",
  "MCO"     = "#0057B8", "SSR"     = "#C1392B",
  "MCO/SSR" = "#9B1D8A", "PSY"     = "#F5A623",
  "HAD"     = "#00B4D8", "Unknown" = "#555555"
)

theme_arcane <- function(base_size = 13) {
  theme_bw(base_size = base_size) +
    theme(
      plot.title       = element_text(face = "bold", colour = "#0D3B66", size = base_size + 1),
      plot.subtitle    = element_text(colour = "grey40", size = base_size - 1),
      panel.grid.minor = element_blank(),
      axis.title       = element_text(colour = "grey30"),
      legend.position  = "right"
    )
}
```

```{r recompute-metrics}
sse_summary <- all_summaries %>%
  group_by(region, H_region, sse_total) %>%
  summarise(n_types = n(), .groups = "drop") %>%
  mutate(
    sse_per_type = round(sse_total / n_types, 6),
    mape = sapply(region, function(r) {
      d <- filter(all_summaries, region == r)
      round(mean(abs(d$diff / d$incidence_obs) * 100, na.rm = TRUE), 2)
    }),
    r2 = sapply(region, function(r) {
      d <- filter(all_summaries, region == r)
      if (nrow(d) < 2) return(NA_real_)
      round(cor(d$incidence_obs, d$incidence_sim_mean, use = "complete.obs")^2, 4)
    })
  ) %>% arrange(mape)

set.seed(42)
n_boot <- 1000
weighted_beta_summary <- all_summaries %>%
  filter(!is.na(beta), !is.na(H_region), beta > 0) %>%
  group_by(type) %>%
  group_modify(function(d, key) {
    w <- d$H_region; log_b <- log(d$beta); n <- nrow(d)
    wgm <- exp(sum(w * log_b) / sum(w))
    boot_wgm <- replicate(n_boot, {
      idx <- sample(seq_len(n), n, replace = TRUE)
      bd <- d[idx, ]; wd <- w[idx]
      exp(sum(wd * log(bd$beta)) / sum(wd))
    })
    data.frame(
      wgm    = round(wgm, 6),
      ci_lo  = round(quantile(boot_wgm, 0.025), 6),
      ci_hi  = round(quantile(boot_wgm, 0.975), 6),
      n_regions = n,
      stringsAsFactors = FALSE
    )
  }) %>% ungroup()
```

# Overview

## Study context

- **Goal:** Estimate β — the daily within-hospital ESBL transmission rate — per facility type
- **Model:** Stochastic SIS on the PMSI inter-hospital transfer network
- **Target:** SPARES ESBL incidence by facility type × region
- **Regions calibrated:** `r n_regions` French administrative regions
- **Runs per region:** 10 independent Nelder-Mead optimisations (best selected)
- **Facility types:** `r paste(unique(all_summaries$type), collapse = ", ")`

# Cross-regional comparison

## Calibration quality by region (MAPE)

```{r mape-bar, fig.height=5.5}
sse_summary %>%
  mutate(region = gsub("_", " ", region)) %>%
  ggplot(aes(x = reorder(region, mape), y = mape, fill = mape)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = paste0(round(mape, 1), "%")), hjust = -0.1, size = 3.8) +
  scale_fill_gradient(low = "#2ecc71", high = "#e74c3c", guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.25))) +
  coord_flip() +
  labs(
    title    = "Calibration quality — MAPE by region",
    subtitle = "Mean absolute % error. Scale-free: not biased by region size or number of types.",
    x = NULL, y = "MAPE (%)"
  ) +
  theme_arcane()
```

## Beta heatmap — type × region

```{r beta-heatmap, fig.height=5.5}
all_summaries %>%
  filter(!is.na(beta)) %>%
  mutate(region = gsub("_", " ", region)) %>%
  left_join(sse_summary %>%
              transmute(region = gsub("_"," ",region), mape),
            by = "region") %>%
  ggplot(aes(x = type, y = reorder(region, mape), fill = beta)) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = formatC(beta, format = "e", digits = 1)), size = 2.6) +
  scale_fill_viridis_c(name = "β (per day)", option = "plasma",
                       trans = "log10", labels = scientific) +
  labs(
    title    = "Optimal β per facility type × region",
    subtitle = "Log10 colour scale  |  Sorted by MAPE (best at top)  |  Empty = no SPARES data",
    x = "Facility type", y = NULL
  ) +
  theme_arcane(11) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1),
        panel.grid  = element_blank())
```

## National beta — weighted geometric mean

```{r national-beta, fig.height=5}
weighted_beta_summary %>%
  ggplot(aes(x = reorder(type, wgm), y = wgm)) +
  geom_col(fill = "#1A7A8A", width = 0.65, alpha = 0.9) +
  geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi),
                width = 0.25, linewidth = 1.1, colour = "#0D3B66") +
  geom_point(size = 3, colour = "#0D3B66") +
  geom_text(aes(label = formatC(wgm, format = "e", digits = 2), y = ci_hi),
            vjust = -0.6, size = 3.5, colour = "#0D3B66") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.3))) +
  coord_flip() +
  labs(
    title    = "National β per facility type",
    subtitle = "Weighted geometric mean | Weights = hospitals per region | Error bars = 95% bootstrap CI",
    x = NULL, y = "β (per day)"
  ) +
  theme_arcane()
```

## Observed vs simulated — all regions

```{r obs-sim-all, fig.height=5.5, fig.width=10}
all_summaries %>%
  filter(!is.na(incidence_obs)) %>%
  left_join(sse_summary %>% select(region, mape), by = "region") %>%
  mutate(region_label = paste0(gsub("_"," ",region),
                                "\nMAPE=", round(mape,1), "%")) %>%
  ggplot(aes(x = incidence_obs, y = incidence_sim_mean, colour = type)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "grey50") +
  geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                    ymax = incidence_sim_mean + incidence_sim_sd),
                width = 0, alpha = 0.4) +
  geom_point(size = 2.5) +
  facet_wrap(~ region_label, ncol = 5, scales = "free") +
  scale_colour_manual(values = type_colours, na.value = "#555555", name = NULL) +
  labs(title = "Simulated vs observed incidence — all regions",
       x = "Observed (per 1,000 bed-days)",
       y = "Simulated (per 1,000 bed-days)") +
  theme_arcane(9) +
  theme(legend.position  = "bottom",
        strip.background = element_rect(fill = "#F0F4F8"),
        strip.text       = element_text(size = 7))
```

## Percentage error — type × region

```{r pct-error, fig.height=5.5}
all_summaries %>%
  mutate(pct_error = 100 * diff / incidence_obs,
         region    = gsub("_", " ", region)) %>%
  filter(!is.na(pct_error)) %>%
  left_join(sse_summary %>%
              transmute(region = gsub("_"," ",region), mape),
            by = "region") %>%
  ggplot(aes(x = type, y = reorder(region, mape), fill = pct_error)) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = paste0(ifelse(pct_error > 0, "+", ""),
                               round(pct_error, 0), "%")), size = 2.6) +
  scale_fill_gradient2(low = "#2980b9", mid = "white", high = "#e74c3c",
                       midpoint = 0, limits = c(-50, 50), oob = squish,
                       name = "% error") +
  labs(title = "% error by region and facility type",
       subtitle = "Red = over-estimate  |  Blue = under-estimate  |  White = near-perfect fit",
       x = "Facility type", y = NULL) +
  theme_arcane(11) +
  theme(axis.text.x = element_text(angle = 35, hjust = 1),
        panel.grid  = element_blank())
```

## Beta variability across regions

```{r beta-boxplot, fig.height=5}
all_summaries %>%
  filter(!is.na(beta)) %>%
  mutate(region = gsub("_", " ", region)) %>%
  ggplot(aes(x = reorder(type, beta, FUN = median), y = beta)) +
  geom_boxplot(width = 0.4, outlier.shape = NA,
               fill = "#d6eaf8", colour = "#2980b9", linewidth = 0.6) +
  geom_jitter(aes(colour = region), width = 0.15, size = 2.5, alpha = 0.8) +
  scale_y_log10(labels = scientific) +
  scale_colour_viridis_d(name = "Region",
                          guide = guide_legend(ncol = 2)) +
  labs(title = "Beta estimates across regions by facility type",
       subtitle = "Each dot = one region  |  Box = IQR  |  Log scale  |  Tight cluster = stable estimate",
       x = NULL, y = "β (per day, log scale)") +
  coord_flip() +
  theme_arcane()
```

## Hospitals per region

```{r hosp-per-region, fig.height=5}
sse_summary %>%
  mutate(region = gsub("_", " ", region)) %>%
  ggplot(aes(x = reorder(region, H_region), y = H_region, fill = H_region)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = H_region), hjust = -0.2, size = 3.8) +
  scale_fill_gradient(low = "#aed6f1", high = "#1a5276", guide = "none") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  coord_flip() +
  labs(title = "Regional sub-network size",
       subtitle = "After subsetting the national transfer network to within-region transfers only",
       x = NULL, y = "Hospitals (H)") +
  theme_arcane()
```

## Fit metrics summary table

```{r fit-table}
sse_summary %>%
  mutate(region = gsub("_", " ", region)) %>%
  select(region, H_region, n_types, mape, r2, sse_per_type) %>%
  arrange(mape) %>%
  kable(
    col.names = c("Region", "Hospitals", "Types", "MAPE (%)", "R²", "SSE/type"),
    digits    = c(0, 0, 0, 2, 3, 4),
    align     = c("l","r","r","r","r","r"),
    caption   = "Sorted by MAPE (best at top). MAPE and R² are scale-free."
  )
```

# Individual Region Reports

```{r region-slides, results='asis', fig.height=5, fig.width=10}
for (rname in all_regions) {

  r     <- results[[rname]]
  val   <- r$validation_summary
  rdisp <- gsub("_", " ", rname)
  rmape <- round(sse_summary$mape[sse_summary$region == rname], 1)
  rr2   <- round(sse_summary$r2[sse_summary$region  == rname], 3)

  # Section header slide for each region
  cat("\n\n## ", rdisp, "\n\n")
  cat(sprintf("H = %d hospitals  |  MAPE = %.1f%%  |  R² = %.3f  |  SSE = %.5f\n\n",
              r$H_region, rmape, rr2, r$sse_final))

  # Observed vs simulated plot
  axis_max <- max(c(val$incidence_obs,
                    val$incidence_sim_mean + val$incidence_sim_sd),
                  na.rm = TRUE) * 1.15

  p_obs <- ggplot(val, aes(x = incidence_obs, y = incidence_sim_mean,
                            colour = type)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "grey40") +
    geom_errorbar(aes(ymin = pmax(incidence_sim_mean - incidence_sim_sd, 0),
                      ymax = incidence_sim_mean + incidence_sim_sd),
                  width = 0, alpha = 0.5, linewidth = 0.9) +
    geom_point(size = 5) +
    geom_text(aes(label = type), hjust = -0.1, size = 3,
              show.legend = FALSE) +
    scale_colour_manual(values = type_colours, na.value = "#555555") +
    scale_x_continuous(limits = c(0, axis_max)) +
    scale_y_continuous(limits = c(0, axis_max)) +
    coord_fixed() +
    labs(title = paste0("Simulated vs observed — ", rdisp),
         subtitle = paste0("SSE = ", round(r$sse_final, 4),
                           "  |  ±1 SD across ", r$n_rep_valid, " replicates"),
         x = "Observed (per 1,000 bed-days)",
         y = "Simulated (per 1,000 bed-days)") +
    theme_arcane() +
    theme(legend.position = "none")

  print(p_obs)
  cat("\n\n")

  # Beta bar chart slide
  cat("\n\n## ", rdisp, " — Beta estimates\n\n")

  p_beta <- ggplot(val, aes(x = reorder(type, beta), y = beta, fill = type)) +
    geom_col(width = 0.65) +
    geom_text(aes(label = formatC(beta, format = "e", digits = 2)),
              hjust = -0.1, size = 3.8) +
    scale_fill_manual(values = type_colours, na.value = "#555555") +
    scale_y_continuous(expand = expansion(mult = c(0, 0.35))) +
    coord_flip() +
    labs(title = paste0("Optimal β by facility type — ", rdisp),
         subtitle = paste0("MAPE = ", rmape, "%  |  R² = ", rr2),
         x = NULL, y = "β (per day)") +
    theme_arcane() +
    theme(legend.position = "none")

  print(p_beta)
  cat("\n\n")
}
```
