---
title: "Dynamic Network Modeling Manuscript Planning Template"
author: "Rany Octaria"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: false
      smooth_scroll: true
    number_sections: false
  pdf_document:
    toc: true
    number_sections: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```



## Project Information 


This section of the Arcane project represents Task 4.2 and 4.3 of the ARCANE proposal.

IN Task 4.2 **Analysing epidemic data to identify AMR seeding events**, we propose an approach to disentangle the relative role in AMR hospital spread of seeding events (e.g., from the environment, the general human population or via importations from foreign countries) vs. between-hospital transmission over the healthcare network. This will be done by analysing observed surveillance data at a regional or country level on specific ARB. 

For each newly “colonised” hospital (that is, a hospital in which a case of colonisation with the ARB has been reported for the first time), we will attempt to identify a potential “infector” hospital over the healthcare network, as we have done previously. A probability of occurrence of a seeding event may then be computed, based on the availability and characteristics of this infector hospital: the delay between reported cases in the infector hospital and the newly colonised hospital, their distance over the network and the number of patients transferred between them. This approach will be applied to epidemic data from both France and Germany over
recent years.

In Task 4.3 **Exploring how seeding events impact AMR spread**, we will also explore how the nature of seeding events may impact the spreading dynamics of pathogens over healthcare networks. To that aim, we will perform numerical simulations starting from a single seeding event using the networkbased dynamic models developed in Task 3 and vary the characteristics of the healthcare institution where the pathogen is seeded, namely: its type (e.g. acute care or long-term care), its place in the network (based on temporal-topological measures, e.g. degree, closeness or betweenness[24]), its geographical area (e.g. in a large or medium-sized city, in a rural or urban area,...). We will then investigate, using multivariate statistical analyses performed on simulated data, the impact of these characteristics on different epidemic patterns, including the risk of a local outbreak becoming global,
the duration before this happens, or the total number (or portion) of contaminated healthcare institutions over a given period of time. Based on these analyses, we will generate risk maps underlining the level of risk associated with a seeding event in a given healthcare institution. This will be performed for different ARBs and for both France and Germany, in order to determine how bacterial characteristics (mostly, carriage duration and transmissibility) and network characteristics impact our conclusions.


```{r libraries, include=FALSE}
library(here)
library(tidyverse)
library(tictoc)
library(furrr)
library(future)
library(dplyr)
library(purrr)
library(igraph)
library(deSolve)

#Run the previous code to clean the network data
source(here("Code", "data-cleaning-network-model.R"))
```

## Data input and preprocessing

Data cleaning codes were loaded in previous codes. We first review the structures of the input datasets. 

The transfer and admission data is sourced from the The PMSI (Programme de médicalisation des systèmes d’information). PMSI is France’s national hospital discharge and activity database. It is a standardized medico-administrative system used to describe hospital care, support financing, and enable epidemiologic and health-services research. In practice, hospitals transmit structured records on stays, diagnoses, procedures, and selected administrative variables using field-specific collections coordinated by ATIH (Agence technique de l’information sur l’hospitalisation). The PMSI covers the main hospital sectors, notably **MCO (médecine, chirurgie, obstétrique), SSR/SMR (soins de suite et de réadaptation, now soins médicaux et de réadaptation), HAD (hospitalisation à domicile), and psychiatry**, where data are collected through the RIM-P (recueil d’informations médicalisé en psychiatrie). In psychiatry, for example, the national collection relies on standardized summaries for inpatient sequences and, for some facilities, outpatient activity as well.

The partner researchers at the École des hautes études en santé publique has aggregated and transformed PMSI database to produce and the admission, facility characteristics, and transfer data shown below.

### Daily admissions data

Daily admissions data shown at each date in 2024 for all finess-geo level facilities. Each finess_geo ID represent one healthcare facility. Many finess_geo IDs may share one finess id if they belong to the same organization. 

```{r view-admissions, echo = FALSE}
adm_daily <- daily_admission %>%
  clean_names() %>%
  mutate(
    date = as.Date(date_entree),
    daily_admissions = as.integer(no_admissions)
  ) %>%
  select(finess_geo, date, daily_admissions)

head(daily_admission)
```

### Transfer data

Prepare the weekly or daily transfer dataset.

```{r clean-transfers, echo= FALSE}
#Getting the date start as the last date
transfers <- weekly %>%
  clean_names() %>%
  mutate(
    finess_geo_origin = as.character(finess_geo_origin),
    finess_geo_target = as.character(finess_geo_target),
    transfer_date = as.Date(window_end),
    weight = as.numeric(weight)
  ) 

head(transfers)
```

### Hospital attributes

Construct the hospital universe and attach bed counts, coordinates, type, region, and other metadata.

```{r hospital-universe, echo=FALSE, warning = FALSE}

head(coords_beds_active)
```

## Helper functions

### Length-of-stay or other stochastic draws

This is currently a placeholder function in case we would need this for future models. However we have been supplied with the data that could generate a true LOS, shall it be needed. This function below defines helper functions for bounded random draws. I'm putting this as a placeholder but we actually don't really need this since we're using the assumption of full occupancy for all hospitals. 

```{r helper-los, include = FALSE}
 # note: im putting this as a pla
# --------------------------------------------------------
# Draw integer LOS from a bounded normal-like distribution
# --------------------------------------------------------
sample_los <- function(n, mean_los = 7, sd_los = 2, min_los = 1, max_los = 15) {
  x <- round(rnorm(n, mean = mean_los, sd = sd_los))
  x <- pmax(min_los, pmin(max_los, x))
  as.integer(x)
}
```

### State initialization


We selected candidate seed hospitals to represent distinct epidemiologically plausible seeding scenarios, including hospitals with high transfer volume, high network centrality, large bed capacity, selected facility types, and randomly chosen hospitals. We then simulated pathogen introduction separately in each seed hospital and summarized downstream spread across simulations to estimate how seeding location influences dissemination. 

We're going to choose multiple seeding hospital in the simulations, including
1. The largest hospital by Bed Size
2. The hospital with largest outgoing transfers and/or incoming transfers
3. The hospital with highest betweenness (bridges)
4. Random hospital (MCO or SSR)
5. Random SSR hospital  --- this is still pending getting the data from Srichand
6. Largest Long-term care hospital (SSR) --- this is still pending getting the data from Srichand.

The table below shows the type of seeding hospitals we use in each scenario, deduplicated if they are the same for more than one seeding rule.

```{r seed-options, echo = FALSE, warning = FALSE}
#--------------------------------------------------
# Build hospital-level metrics for seed selection
#--------------------------------------------------

# In-degree = number of distinct hospitals sending to this hospital
incoming_tbl <- transfers %>%
  distinct(finess_geo_origin, finess_geo_target) %>%
  group_by(finess_geo = finess_geo_target) %>%
  summarise(
    in_degree = n(),
    .groups = "drop"
  )

# Out-degree = number of distinct hospitals receiving from this hospital
outgoing_tbl <- transfers %>%
  distinct(finess_geo_origin, finess_geo_target) %>%
  group_by(finess_geo = finess_geo_origin) %>%
  summarise(
    out_degree = n(),
    .groups = "drop"
  )

# Hospital universe
all_hospitals_tbl <- bind_rows(
  transfers %>% transmute(finess_geo = finess_geo_origin),
  transfers %>% transmute(finess_geo = finess_geo_target)
) %>%
  distinct()

#--------------------------------------------------
# Faster betweenness calculation
#--------------------------------------------------
# Collapse repeated edges first, and collapse by year
transfers_yr = transfers %>% 
  group_by(finess_geo_origin, finess_geo_target) %>% 
  summarise(
    weight = sum(weight)
  )

g_simple <- graph_from_data_frame(transfers_yr, directed = TRUE)

# Faster approximate betweenness using a path-length cutoff
# Increase cutoff for more accuracy, decrease for more speed
centrality_tbl <- tibble(
  finess_geo = V(g_simple)$name,
  betweenness = estimate_betweenness(
    g_simple,
    vids = V(g_simple),
    directed = TRUE,
    cutoff = 5
  )
)

# Combine metrics
seed_metrics <- all_hospitals_tbl %>%
  left_join(incoming_tbl, by = "finess_geo") %>%
  left_join(outgoing_tbl, by = "finess_geo") %>%
  left_join(centrality_tbl, by = "finess_geo") %>%
  mutate(
    in_degree = replace_na(in_degree, 0L),
    out_degree = replace_na(out_degree, 0L),
    betweenness = replace_na(betweenness, 0)
  )
#--------------------------------------------------
# Select one seed hospital by in-degree, out-degree, and betweenness
#--------------------------------------------------


seed_panel <- bind_rows(
  seed_metrics %>%
    slice_max(order_by = in_degree, n = 1, with_ties = FALSE) %>%
    mutate(seed_rule = "highest_in_degree"),
  
  seed_metrics %>%
    slice_max(order_by = out_degree, n = 1, with_ties = FALSE) %>%
    mutate(seed_rule = "highest_out_degree"),
  
  seed_metrics %>%
    slice_max(order_by = betweenness, n = 1, with_ties = FALSE) %>%
    mutate(seed_rule = "highest_betweenness"),
  
  seed_metrics %>%
    slice_sample(n = 1) %>%
    mutate(seed_rule = "random_hospital")
) 

#Seeding based on the largest number of beds

largest_beds = coords_beds_active %>% 
  slice_max(order_by = no_beds, n=1, with_ties = FALSE) %>% 
  mutate(seed_rule = "largest_beds") %>% 
  dplyr::select(seed_rule, finess_geo)

# most admissions
largest_admissions = coords_beds_active %>% 
  slice_max(order_by = no_beds, n=1, with_ties = FALSE) %>% 
  mutate(seed_rule = "largest_admission") %>% 
  dplyr::select(seed_rule, finess_geo)

# Largest outgoing transfers
largest_outgoing_seed <- transfers %>%
  group_by(finess_geo_origin) %>%
  summarise(
    total_outgoing = sum(weight, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  slice_max(order_by = total_outgoing, n = 1, with_ties = FALSE) %>%
  rename(finess_geo = finess_geo_origin) %>%
  mutate(seed_rule = "largest_outgoing_transfers")

largest_outgoing_seed

# Largest incoming transfers
largest_incoming_seed <- transfers %>%
  group_by(finess_geo_target) %>%
  summarise(
    total_incoming = sum(weight, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  slice_max(order_by = total_incoming, n = 1, with_ties = FALSE) %>%
  rename(finess_geo = finess_geo_target) %>%
  mutate(seed_rule = "largest_incoming_transfers")

largest_incoming_seed

seed_panel_final = bind_rows(seed_panel, largest_beds, largest_admissions, 
                       largest_incoming_seed, largest_outgoing_seed) %>% 
  dplyr::select(seed_rule, finess_geo) %>% 
  group_by(finess_geo) %>%
  summarise(
    seed_rule = paste(seed_rule, collapse = " + "),
    .groups = "drop"
  ) %>%
  select(seed_rule, finess_geo)

#Remove dups 
seed_panel_final 
```


```{r initialize-state, echo = FALSE, warning = FALSE}

# -----------------------------------------------------------
# Build hospital universe from all origins and targets
# then attach no_beds
# -----------------------------------------------------------
all_transfer_hospitals <- bind_rows(
  transfers %>% transmute(finess_geo = finess_geo_origin),
  transfers %>% transmute(finess_geo = finess_geo_target)
) %>%
  distinct()

#  getting the list of hospitals involved
# if there's no beds reported, we fill it with the mean number of beds
hospitals <- all_transfer_hospitals %>%
  left_join(
    coords_beds_active %>%
      clean_names() %>%
      transmute(
        finess_geo = as.character(finess_geo),
        no_beds = readr::parse_number(as.character(no_beds))
      ) %>%
      distinct(),
    by = "finess_geo"
  ) %>%
  mutate(
    mean_beds = round(mean(no_beds, na.rm = TRUE)),
    no_beds = if_else(is.na(no_beds), mean_beds, no_beds),
    no_beds = as.integer(round(no_beds))
  ) %>%
  select(finess_geo, no_beds)

# -------------------------------------------------------------------
# Create one occupied bed = one patient at time 0 as the initial infected
# this is simulating a one-patient importation
# Seed infection into one hospital
# -------------------------------------------------------------------
# -----------------------------------------------------------
# Initialize hospital-level state
# -----------------------------------------------------------
initialize_hospital_state <- function(hospitals,
                                      seed_hospital,
                                      n_seed_infected = 1) {
  
  hospitals %>%
    mutate(
      n_infected = if_else(
        finess_geo == seed_hospital,
        pmin(n_seed_infected, no_beds),
        0L
      ),
      prevalence = n_infected / no_beds
    )
}
```

### **Daily infected transfer calculation**

Create the function that converts origin prevalence and transfer weights into infected transfers.

```{r infected-transfers}
# TODO:
# Define compute_daily_infected_transfers()


# -----------------------------------------------------------
# For one day of transfers:
# infected transferred on each edge = round(weight * prevalence_origin)
#
# Then cap total infected outgoing from each hospital so we do not
# transfer out more infected than currently exist in that hospital.
# -----------------------------------------------------------
compute_daily_infected_transfers_fast <- function(state, transfers_day) {
  
  if (nrow(transfers_day) == 0) {
    return(tibble(
      finess_geo_origin = character(),
      finess_geo_target = character(),
      weight = integer(),
      prev_origin = numeric(),
      infected_transfer = integer()
    ))
  }
  
  # fast lookup from state to transfer origins
  idx_origin <- match(transfers_day$finess_geo_origin, state$finess_geo)
  
  prev_origin <- state$prevalence[idx_origin]
  n_infected_origin <- state$n_infected[idx_origin]
  
  prev_origin[is.na(prev_origin)] <- 0
  n_infected_origin[is.na(n_infected_origin)] <- 0L
  
  # stochastic infected transfers on each edge
  infected_transfer_raw <- rbinom(
    n = nrow(transfers_day),
    size = transfers_day$weight,
    prob = prev_origin
  )
  
  infected_transfer <- infected_transfer_raw
  
  # cap by origin hospital so total infected outgoing does not exceed available infected
  split_idx <- split(seq_len(nrow(transfers_day)), transfers_day$finess_geo_origin)
  
  for (idx in split_idx) {
    infected_available <- n_infected_origin[idx[1]]
    proposed_total <- sum(infected_transfer_raw[idx], na.rm = TRUE)
    
    if (infected_available <= 0L || proposed_total <= 0L) {
      infected_transfer[idx] <- 0L
    } else if (proposed_total > infected_available) {
      scaled <- infected_transfer_raw[idx] * infected_available / proposed_total
      base_alloc <- floor(scaled)
      remainder <- scaled - base_alloc
      
      left_to_assign <- infected_available - sum(base_alloc)
      
      if (left_to_assign > 0L) {
        add_one_idx <- order(remainder, decreasing = TRUE)[seq_len(left_to_assign)]
        base_alloc[add_one_idx] <- base_alloc[add_one_idx] + 1L
      }
      
      infected_transfer[idx] <- as.integer(base_alloc)
    }
  }
  
  tibble(
    finess_geo_origin = transfers_day$finess_geo_origin,
    finess_geo_target = transfers_day$finess_geo_target,
    weight = transfers_day$weight,
    prev_origin = prev_origin,
    infected_transfer = as.integer(infected_transfer)
  )
}
# - cap outgoing infected transfers by current infected stock
# - return edge-level infected transfers
```

## Core simulation engine

### One-day aggregate simulation step

Implement the daily update step.Some stochasticity is added to the functions, including 
- a binomial Distribution of whether intra-hospital transmission occurs in each day
- a binomial distribution of whether inter-hospital transmission through transfers occurs for transfers. we introduce randomness in whether the transferred patients are the infected transfers. Later we will also add a reduced probability of transfers are reduced for infected patients.
- A binomial distribution of whether 

```{r simulate-one-day}
# TODO:
# - define simulate_one_day_agg()

# - process transfers for current date
# - update infected counts after transfer
# - implement community replacement if applicable
# - implement clearance
# - implement within-hospital transmission
# - return updated state and daily summaries
simulate_one_day_agg_fast <- function(state,
                                      transfers_day,
                                      current_date,
                                      beta_within = 0.05,
                                      gamma_clear = 1 / 387,
                                      admission_prev = 0) {
  
  infected_transfers <- compute_daily_infected_transfers_fast(
    state = state,
    transfers_day = transfers_day
  )
  
  infected_out <- integer(nrow(state))
  infected_in  <- integer(nrow(state))
  
  if (nrow(infected_transfers) > 0) {
    idx_out <- match(infected_transfers$finess_geo_origin, state$finess_geo)
    idx_in  <- match(infected_transfers$finess_geo_target, state$finess_geo)
    
    out_sum <- tapply(infected_transfers$infected_transfer, idx_out, sum)
    in_sum  <- tapply(infected_transfers$infected_transfer, idx_in, sum)
    
    infected_out[as.integer(names(out_sum))] <- as.integer(out_sum)
    infected_in[as.integer(names(in_sum))]   <- as.integer(in_sum)
  }
  
  infected_replaced_from_community <- rbinom(
    n = nrow(state),
    size = infected_out,
    prob = admission_prev
  )
  
  n_infected_after_transfer <- state$n_infected - infected_out + infected_in + infected_replaced_from_community
  n_infected_after_transfer <- pmax(0L, pmin(n_infected_after_transfer, state$no_beds))
  
  # stochastic clearance
  n_cleared <- rbinom(
    n = nrow(state),
    size = n_infected_after_transfer,
    prob = gamma_clear
  )
  
  n_infected_after_clear <- n_infected_after_transfer - n_cleared
  
  n_susceptible <- state$no_beds - n_infected_after_clear
  
  p_infection <- 1 - exp(-beta_within * (n_infected_after_clear / state$no_beds))
  p_infection <- pmin(pmax(p_infection, 0), 1)
  
  n_new_infected <- rbinom(
    n = nrow(state),
    size = n_susceptible,
    prob = p_infection
  )
  
  n_infected_final <- n_infected_after_clear + n_new_infected
  n_infected_final <- pmax(0L, pmin(n_infected_final, state$no_beds))
  
  state_new <- tibble(
    finess_geo = state$finess_geo,
    no_beds = state$no_beds,
    n_infected = as.integer(n_infected_final),
    prevalence = n_infected_final / state$no_beds
  )
  
  daily_summary <- tibble(
    date = current_date,
    finess_geo = state_new$finess_geo,
    no_beds = state_new$no_beds,
    n_infected = state_new$n_infected,
    prevalence = state_new$prevalence
  )
  
  overall_summary <- tibble(
    date = current_date,
    total_patients = sum(state_new$no_beds),
    total_infected = sum(state_new$n_infected),
    overall_prevalence = sum(state_new$n_infected) / sum(state_new$no_beds),
    n_hospitals_with_case = sum(state_new$n_infected > 0)
  )
  
  list(
    state = state_new,
    daily_summary = daily_summary,
    overall_summary = overall_summary,
    infected_transfers = infected_transfers
  )
}

```

### Full simulation wrapper

Run the model across the full date range.

```{r run-simulation}
library(tidyverse)
library(purrr)


run_sis_simulation_agg_fast <- function(hospitals,
                                        transfers,
                                        start_date,
                                        end_date,
                                        seed_hospital = NULL,
                                        n_seed_infected = 1,
                                        beta_within = 0.05,
                                        gamma_clear = 1 / 387,
                                        admission_prev = 0.001,
                                        seed = 123,
                                        store_transfer_results = FALSE) {
  
  set.seed(seed)
  
  if (is.null(seed_hospital)) {
    seed_hospital <- transfers %>%
      group_by(finess_geo_origin) %>%
      summarise(total_outgoing = sum(weight, na.rm = TRUE), .groups = "drop") %>%
      slice_max(order_by = total_outgoing, n = 1, with_ties = FALSE) %>%
      pull(finess_geo_origin)
  }
  
  state <- initialize_hospital_state(
    hospitals = hospitals,
    seed_hospital = seed_hospital,
    n_seed_infected = n_seed_infected
  )
  
  sim_dates <- seq.Date(
    from = as.Date(start_date),
    to = as.Date(end_date),
    by = "day"
  )
  
  # pre-split transfers once
  transfers_use <- transfers %>%
    mutate(transfer_date = as.Date(transfer_date)) %>%
    select(transfer_date, finess_geo_origin, finess_geo_target, weight)
  
  transfers_by_day <- split(
    transfers_use[, c("finess_geo_origin", "finess_geo_target", "weight")],
    transfers_use$transfer_date
  )
  
  daily_results <- vector("list", length(sim_dates))
  overall_results <- vector("list", length(sim_dates))
  
  if (store_transfer_results) {
    transfer_results <- vector("list", length(sim_dates))
  }
  
  for (i in seq_along(sim_dates)) {
    current_date <- sim_dates[i]
    transfers_day <- transfers_by_day[[as.character(current_date)]]
    
    if (is.null(transfers_day)) {
      transfers_day <- tibble(
        finess_geo_origin = character(),
        finess_geo_target = character(),
        weight = integer()
      )
    }
    
    out <- simulate_one_day_agg_fast(
      state = state,
      transfers_day = transfers_day,
      current_date = current_date,
      beta_within = beta_within,
      gamma_clear = gamma_clear,
      admission_prev = admission_prev
    )
    
    state <- out$state
    daily_results[[i]] <- out$daily_summary
    overall_results[[i]] <- out$overall_summary
    
    if (store_transfer_results) {
      transfer_results[[i]] <- out$infected_transfers %>%
        mutate(date = current_date)
    }
  }
  
  result <- list(
    seed_hospital = seed_hospital,
    state_final = state,
    daily_results = bind_rows(daily_results),
    overall_results = bind_rows(overall_results)
  )
  
  if (store_transfer_results) {
    result$infected_transfer_results <- bind_rows(transfer_results)
  }
  
  result
}


```

## Baseline simulation

### Baseline parameter values

Specify the default values for transmission, clearance, importation, and seed assumptions.

```{r baseline-parameters}
# TODO:
# - define beta_within
# - define gamma_clear
# - define admission_prev
# - define start and end date
# - define n_seed_infected

# Fixed epidemiologic parameters

gamma_clear_val   <- 1 / 387  #Keep it a very long time for now, vary the beta for now 
admission_prev_val <- 0
n_seed_infected_val <- 1


# number of simulation replicates per seed scenario
n_sim_per_regime <- 100

# Simulation settings
sim_start_date <- "2024-01-07"
sim_end_date   <- "2024-12-31"

```


#### Setting Beta Variability

Because the model is currently running on a pathogen agnostic example, we want to
try incorporating different levels of force of transmissions into the model that would cover different types of pathogen 

```{r setting beta-variability}
# -----------------------------------------------------------
# Create one transmissibility draw per sim_id
#
# Each sim_id belongs to one transmission regime:
# - low:  R0 < 1
# - mid:  R0 around 1
# - high: R0 between 1 and 2
#
# beta_within is then computed as:
#   beta_within = R0 * gamma_clear
# -----------------------------------------------------------
# beta_lookup <- tibble(
#   beta_regime = rep(c("low", "mid", "high"), each = n_sim_per_regime),
#   sim_id_within_regime = rep(seq_len(n_sim_per_regime), times = 3)
# ) %>%
#   mutate(
#     sim_id = row_number(),
#     
#     # reproducible RNG seed for the R0 draw
#     beta_seed = 50000 + sim_id,
#     
#     # draw one R0 value within each regime
#     R0_iter = pmap_dbl(
#       list(beta_regime, beta_seed),
#       function(beta_regime, beta_seed) {
#         set.seed(beta_seed)
#         
#         if (beta_regime == "low") {
#           runif(1, min = 0.20, max = 0.95)
#         } else if (beta_regime == "mid") {
#           runif(1, min = 0.95, max = 1.2)
#         } else if (beta_regime == "high") {
#           runif(1, min = 1.20, max = 2)
#         } else {
#           stop("Unknown beta_regime")
#         }
#       }
#     ),
#     
#     # convert R0 to beta using the SIS threshold approximation
#     beta_within_iter = R0_iter * gamma_clear_val
#   )
# 
# beta_lookup %>%
#   group_by(beta_regime) %>%
#   summarise(
#     min_R0 = min(R0_iter),
#     max_R0 = max(R0_iter),
#     min_beta = min(beta_within_iter),
#     max_beta = max(beta_within_iter),
#     .groups = "drop"
#   )''

# ANOTHER APPROACH TO BETA SAMPLING



# -----------------------------------------------------------
# Literature-informed beta regimes (per day)
# Shared across seed types within each sim_id
# -----------------------------------------------------------
n_sim_per_regime <- 50

beta_lookup <- tibble(
  beta_regime = rep(c("low", "mid", "high"), each = n_sim_per_regime),
  sim_id_within_regime = rep(seq_len(n_sim_per_regime), times = 3)
) %>%
  mutate(
    sim_id = row_number(),
    beta_seed = 70000 + sim_id,
    beta_within_iter = pmap_dbl(
      list(beta_regime, beta_seed),
      function(beta_regime, beta_seed) {
        set.seed(beta_seed)
        
        if (beta_regime == "low") {
          runif(1, min = 0.036, max = 0.048)  #Reflecting the beta in Prabasaj's paper for LTACH
        } else if (beta_regime == "mid") {
          runif(1, min = 0.071, max = 0.125) #Beta from Prabasaj Paul's paper for STACH
        } else if (beta_regime == "high") {
          runif(1, min = 0.125, max = 0.25)  #Hypothetical High Beta
        } else {
          stop("Unknown beta_regime")
        }
      }
    )
  )


```

#### Building Simulation Grid

```{r sim-grid}
# -----------------------------------------------------------
# Build the simulation grid
#
# Each row is:
# - one seed scenario
# - one sim_id
#
# All seed types sharing the same sim_id will also share:
# - beta_regime
# - R0_iter
# - beta_within_iter
#
# This makes comparisons across seed types fairer.
# -----------------------------------------------------------

# -----------------------------------------------------------
# Build simulation grid
# Same beta for all seed types within a given sim_id
# -----------------------------------------------------------
simulation_grid <- seed_panel_final %>%
  rename(seed_hospital = finess_geo) %>%
  tidyr::crossing(sim_id = beta_lookup$sim_id) %>%
  left_join(beta_lookup, by = "sim_id") %>%
  mutate(
    sim_seed = 1000 + sim_id
  ) %>%
  mutate(
    seed_hospital_iter = pmap_chr(
      list(seed_rule, seed_hospital, sim_seed),
      function(seed_rule, seed_hospital, sim_seed) {
        if (grepl("random_hospital", seed_rule)) {
          set.seed(sim_seed)
          sample(hospitals$finess_geo, size = 1)
        } else {
          seed_hospital
        }
      }
    )
  )

# inspect
simulation_grid %>%
  select(seed_rule, sim_id, beta_regime, beta_within_iter, sim_seed, seed_hospital_iter) %>%
  arrange(beta_regime, sim_id, seed_rule) %>%
  print(n = 30)

```


#### Baseline Model Run

Execute the baseline simulation.

```{r baseline-run, include = FALSE}
library(dplyr)
library(furrr)
library(future)
library(progressr)

# -----------------------------------------------------------
# Wrapper for one simulation run
# -----------------------------------------------------------
run_one_sim <- function(seed_hospital, sim_seed, beta_within_iter) {
  run_sis_simulation_agg_fast(
    hospitals = hospitals,
    transfers = transfers,
    start_date = sim_start_date,
    end_date   = sim_end_date,
    seed_hospital = seed_hospital,
    n_seed_infected = n_seed_infected_val,
    beta_within = beta_within_iter,
    gamma_clear = gamma_clear_val,
    admission_prev = admission_prev_val,
    seed = sim_seed,
    store_transfer_results = FALSE
  )
}

# -----------------------------------------------------------
# Parallel plan + progress bar
# -----------------------------------------------------------
# plan(multisession, workers = 4)
# handlers("txtprogressbar")
# 
# start_time <- Sys.time()
# 
# with_progress({
#   
#   p <- progressor(steps = nrow(simulation_grid))
#   
#   all_simulations <- simulation_grid %>%
#     mutate(
#       sim = future_pmap(
#         list(seed_hospital_iter, sim_seed, beta_within_iter),
#         function(seed_hospital, sim_seed, beta_within_iter) {
#           
#           res <- run_one_sim(
#             seed_hospital = seed_hospital,
#             sim_seed = sim_seed,
#             beta_within_iter = beta_within_iter
#           )
#           
#           p(sprintf("completed sim_id seed=%s", sim_seed))
#           
#           res
#         },
#         .options = furrr_options(seed = TRUE)
#       )
#     )
# })
# 
# end_time <- Sys.time()
# 
# cat(
#   "\nTotal elapsed time:",
#   round(as.numeric(end_time - start_time, units = "mins"), 2),
#   "minutes\n"
# )
# 
# plan(sequential)
```

## Baseline output summaries and plots

In this section, i'm going to just summarize the big file outputs, later to comment out
the big chunnk with the simulations and then load pre-saved rds files for plotting

```{r summarize outputs, include = FALSE}
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(scales)
library(forcats)
library(here)

# -----------------------------------------------------------
# Create save folder
# -----------------------------------------------------------
save_dir <- here::here("Outputs", "saved_results")

if (!dir.exists(save_dir)) {
  dir.create(save_dir, recursive = TRUE)
}

# -----------------------------------------------------------
# 1. Extract overall simulation results into one long dataset
#
# This is the main plotting-ready dataset.
# Each row = one date within one simulation replicate.
# -----------------------------------------------------------
# overall_results_by_sim <- all_simulations %>%
#   transmute(
#     seed_rule,
#     seed_hospital,
#     seed_hospital_iter,
#     sim_id,
#     sim_seed,
#     beta_regime,
#    # R0_iter,
#     beta_within_iter,
#     overall_results = map(sim, "overall_results")
#   ) %>%
#   unnest(overall_results)
# 
# # quick check
# head(overall_results_by_sim)

# -----------------------------------------------------------
# 2. Define clean seed ordering and labels for plots
# -----------------------------------------------------------
# seed_levels <- c(
#   "highest_in_degree + highest_out_degree",
#   "highest_betweenness",
#   "largest_beds + largest_admission",
#   "largest_incoming_transfers",
#   "largest_outgoing_transfers",
#   "random_hospital"
# )
# 
# seed_labels <- c(
#   "highest_in_degree + highest_out_degree" = "Highest in/out degree",
#   "highest_betweenness" = "Highest betweenness",
#   "largest_beds + largest_admission" = "Largest beds/admissions",
#   "largest_incoming_transfers" = "Largest incoming transfers",
#   "largest_outgoing_transfers" = "Largest outgoing transfers",
#   "random_hospital" = "Random hospital"
# )

# overall_results_by_sim <- overall_results_by_sim %>%
#   mutate(
#     seed_rule = factor(seed_rule, levels = seed_levels),
#     beta_regime = factor(beta_regime, levels = c("low", "mid", "high"))
#   )

# -----------------------------------------------------------
# 3. Summarize trajectories across ALL beta values combined
#
# For each seed type and date:
# - median
# - 25th percentile
# - 75th percentile
# -----------------------------------------------------------
# trajectory_summary_all_beta <- overall_results_by_sim %>%
#   group_by(seed_rule, date) %>%
#   summarise(
#     n_runs = n(),
#     
#     total_infected_median = median(total_infected, na.rm = TRUE),
#     total_infected_q25    = quantile(total_infected, 0.25, na.rm = TRUE),
#     total_infected_q75    = quantile(total_infected, 0.75, na.rm = TRUE),
#     
#     prevalence_median = median(overall_prevalence, na.rm = TRUE),
#     prevalence_q25    = quantile(overall_prevalence, 0.25, na.rm = TRUE),
#     prevalence_q75    = quantile(overall_prevalence, 0.75, na.rm = TRUE),
#     
#     hospitals_with_case_median = median(n_hospitals_with_case, na.rm = TRUE),
#     hospitals_with_case_q25    = quantile(n_hospitals_with_case, 0.25, na.rm = TRUE),
#     hospitals_with_case_q75    = quantile(n_hospitals_with_case, 0.75, na.rm = TRUE),
#     
#     .groups = "drop"
#   ) %>%
#   mutate(
#     seed_label = recode(as.character(seed_rule), !!!seed_labels)
#   )

# -----------------------------------------------------------
# 4. Summarize trajectories within each beta regime
#
# For each beta regime, seed type, and date:
# - median
# - 25th percentile
# - 75th percentile
# -----------------------------------------------------------
# trajectory_summary_by_beta_regime <- overall_results_by_sim %>%
#   group_by(beta_regime, seed_rule, date) %>%
#   summarise(
#     n_runs = n(),
#     
#     total_infected_median = median(total_infected, na.rm = TRUE),
#     total_infected_q25    = quantile(total_infected, 0.25, na.rm = TRUE),
#     total_infected_q75    = quantile(total_infected, 0.75, na.rm = TRUE),
#     
#     prevalence_median = median(overall_prevalence, na.rm = TRUE),
#     prevalence_q25    = quantile(overall_prevalence, 0.25, na.rm = TRUE),
#     prevalence_q75    = quantile(overall_prevalence, 0.75, na.rm = TRUE),
#     
#     hospitals_with_case_median = median(n_hospitals_with_case, na.rm = TRUE),
#     hospitals_with_case_q25    = quantile(n_hospitals_with_case, 0.25, na.rm = TRUE),
#     hospitals_with_case_q75    = quantile(n_hospitals_with_case, 0.75, na.rm = TRUE),
#     
#     .groups = "drop"
#   ) %>%
#   mutate(
#     seed_label = recode(as.character(seed_rule), !!!seed_labels)
#   )
```


```{r saving objects for future, echo=FALSE}
library(dplyr)
library(tidyr)
library(purrr)
library(here)
library(readr)

# ===========================================================
# SAVE CURRENT SIMULATION RUN AS A SELF-CONTAINED BUNDLE
# ===========================================================

# -----------------------------------------------------------
# 1. Create a date stamp in ddmmyy format
# -----------------------------------------------------------
run_date_stamp <- format(Sys.Date(), "%d%m%y")

# -----------------------------------------------------------
# 2. Give this simulation run a short scenario name
# Edit this manually for each new run
# -----------------------------------------------------------
scenario_name <- paste0("beta_varying_", as.character(n_sim_per_regime), "reps")

# -----------------------------------------------------------
# 3. Create a folder for this run
# Example:
# Outputs/saved_results/150426_beta_varying_100rep
# -----------------------------------------------------------
run_id <- paste(run_date_stamp, scenario_name, sep = "_")

run_dir <- here::here("Outputs", "saved_results", run_id)
run_dir
if (!dir.exists(run_dir)) {
  dir.create(run_dir, recursive = TRUE)
}

# -----------------------------------------------------------
# 4. Build a metadata table describing what was done
#
# Add or edit fields here whenever you run a new scenario.
# This is the most important part for future reproducibility.
# -----------------------------------------------------------
# run_metadata <- tibble(
#   run_id = run_id,
#   run_date = as.character(Sys.Date()),
#   scenario_name = scenario_name,
#   scenario_description = paste(
#     "Aggregate SIS hospital-transfer simulation.",
#     "Beta varied by simulation replicate and shared across seed types within sim_id.",
#     "100 repetitions per beta regime.",
#     "Seed comparison across multiple seed rules.",
#     "Stochastic infected transfers, stochastic clearance, and stochastic within-hospital transmission."
#   ),
#   sim_start_date = sim_start_date,
#   sim_end_date = sim_end_date,
#   n_seed_infected = n_seed_infected_val,
#   gamma_clear = gamma_clear_val,
#   admission_prev = admission_prev_val,
#   n_sim_total = nrow(simulation_grid),
#   n_unique_sim_id = dplyr::n_distinct(simulation_grid$sim_id),
#   n_seed_types = dplyr::n_distinct(simulation_grid$seed_rule),
#   beta_regimes = paste(sort(unique(simulation_grid$beta_regime)), collapse = ", "),
#   beta_min = min(simulation_grid$beta_within_iter, na.rm = TRUE),
#   beta_max = max(simulation_grid$beta_within_iter, na.rm = TRUE),
#   beta_mean = mean(simulation_grid$beta_within_iter, na.rm = TRUE),
#   notes = "Saved after simulation completed; includes simulation grid, raw results, and trajectory summaries."
# )

# -----------------------------------------------------------
# 5. Optional: summarise beta ranges by regime
# This is useful for checking exactly what beta values were used.
# -----------------------------------------------------------
# beta_regime_summary <- simulation_grid %>%
#   group_by(beta_regime) %>%
#   summarise(
#     n_runs = n(),
#     beta_min = min(beta_within_iter, na.rm = TRUE),
#     beta_q25 = quantile(beta_within_iter, 0.25, na.rm = TRUE),
#     beta_median = median(beta_within_iter, na.rm = TRUE),
#     beta_q75 = quantile(beta_within_iter, 0.75, na.rm = TRUE),
#     beta_max = max(beta_within_iter, na.rm = TRUE),
#     .groups = "drop"
#   )

# -----------------------------------------------------------
# 6. Build one self-contained R object containing everything
# needed to reload the run later
# -----------------------------------------------------------
# run_bundle <- list(
#   metadata = run_metadata,
#   beta_regime_summary = beta_regime_summary,
#   simulation_grid = simulation_grid,
#   seed_panel_final = seed_panel_final,
#   #all_simulations = all_simulations,
#   overall_results_by_sim = overall_results_by_sim,
#   trajectory_summary_all_beta = trajectory_summary_all_beta,
#   trajectory_summary_by_beta_regime = trajectory_summary_by_beta_regime,
#   session_info = utils::sessionInfo()
# )

# -----------------------------------------------------------
# 7. Save the self-contained bundle
# -----------------------------------------------------------
# saveRDS(
#   run_bundle,
#   file = file.path(run_dir, "run_bundle.rds"),
#   compress = "xz"
# )

# -----------------------------------------------------------
# 8. Save important individual objects separately
# This makes later loading faster and more convenient.
# -----------------------------------------------------------
# saveRDS(
#   all_simulations,
#   file = file.path(run_dir, "all_simulations.rds"),
#   compress = "xz"
# )

# saveRDS(
#   overall_results_by_sim,
#   file = file.path(run_dir, "overall_results_by_sim.rds"),
#   compress = "xz"
# )
# 
# saveRDS(
#   trajectory_summary_all_beta,
#   file = file.path(run_dir, "trajectory_summary_all_beta.rds"),
#   compress = "xz"
# )
# 
# saveRDS(
#   trajectory_summary_by_beta_regime,
#   file = file.path(run_dir, "trajectory_summary_by_beta_regime.rds"),
#   compress = "xz"
# )
# 
# saveRDS(
#   simulation_grid,
#   file = file.path(run_dir, "simulation_grid.rds"),
#   compress = "xz"
# )

# -----------------------------------------------------------
# 9. Save metadata tables as csv for quick human-readable review
# -----------------------------------------------------------
# readr::write_csv(
#   run_metadata,
#   file = file.path(run_dir, "run_metadata.csv")
# )
# 
# readr::write_csv(
#   beta_regime_summary,
#   file = file.path(run_dir, "beta_regime_summary.csv")
# )

# -----------------------------------------------------------
# 10. Print a quick summary of what was saved
# -----------------------------------------------------------
# saved_files <- tibble(
#   file = c(
#     "run_bundle.rds",
#     #"all_simulations.rds",
#     "overall_results_by_sim.rds",
#     "trajectory_summary_all_beta.rds",
#     "trajectory_summary_by_beta_regime.rds",
#     "simulation_grid.rds",
#     "run_metadata.csv",
#     "beta_regime_summary.csv"
#   )
# ) %>%
#   mutate(
#     path = file.path(run_dir, file),
#     size_mb = round(file.info(path)$size / 1024^2, 2)
#   )
# 
# print(run_metadata)
# print(beta_regime_summary)
# print(saved_files)
# 

# 
# run_dir <- here::here("Outputs", "saved_results", "150426_beta_varying_100rep")
# 
# run_bundle <- readRDS(file.path(run_dir, "run_bundle.rds"))
# 
# # pull objects back into the workspace if needed
# run_metadata <- run_bundle$metadata
# simulation_grid <- run_bundle$simulation_grid
# all_simulations <- run_bundle$all_simulations
# overall_results_by_sim <- run_bundle$overall_results_by_sim
# trajectory_summary_all_beta <- run_bundle$trajectory_summary_all_beta
# trajectory_summary_by_beta_regime <- run_bundle$trajectory_summary_by_beta_regime


```


#### Plotting Results as Manuscript Type Graphs (Black and White)

```{r pub style plotting, echo = FALSE, warning = FALSE}



overall_results_by_sim <- readRDS(file.path(run_dir, "overall_results_by_sim.rds"))
trajectory_summary_all_beta <- readRDS(file.path(run_dir, "trajectory_summary_all_beta.rds"))
trajectory_summary_by_beta_regime <- readRDS(file.path(run_dir, "trajectory_summary_by_beta_regime.rds"))
library(ggplot2)

# -----------------------------------------------------------
# 5. Publication-style plotting theme
# -----------------------------------------------------------
theme_pub_traj <- function() {
  theme_minimal(base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      strip.text = element_text(face = "bold", size = 11),
      strip.background = element_rect(fill = "grey95", color = "grey80"),
      axis.title = element_text(face = "bold"),
      axis.text = element_text(color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1),
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(size = 11),
      legend.position = "none",
      panel.border = element_rect(color = "grey60", fill = NA, linewidth = 0.4)
    )
}

# -----------------------------------------------------------
# 6. Plot function for ALL beta values combined
# -----------------------------------------------------------
plot_all_beta <- function(data, y_median, y_q25, y_q75, y_lab, title_text, percent = FALSE) {
  p <- ggplot(
    data,
    aes(x = date, y = .data[[y_median]], group = seed_label)
  ) +
    geom_ribbon(
      aes(
        ymin = .data[[y_q25]],
        ymax = .data[[y_q75]]
      ),
      alpha = 0.20
    ) +
    geom_line(linewidth = 0.9) +
    facet_wrap(~ seed_label, scales = "free_y", ncol = 2) +
    labs(
      title = title_text,
      subtitle = "Median and IQR across all simulation replicates pooled across beta regimes.",
      x = "Simulation date",
      y = y_lab
    ) +
    scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
    theme_pub_traj()
  
  if (percent) {
    p <- p + scale_y_continuous(labels = percent_format(accuracy = 0.1))
  }
  
  p
}

# -----------------------------------------------------------
# 7. Plot function stratified by beta regime
# -----------------------------------------------------------
plot_by_beta_regime <- function(data, y_median, y_q25, y_q75, y_lab, title_text, percent = FALSE) {
  p <- ggplot(
    data,
    aes(x = date, y = .data[[y_median]], group = seed_label)
  ) +
    geom_ribbon(
      aes(
        ymin = .data[[y_q25]],
        ymax = .data[[y_q75]]
      ),
      alpha = 0.20
    ) +
    geom_line(linewidth = 0.8) +
    facet_grid(beta_regime ~ seed_label, scales = "free_y") +
    labs(
      title = title_text,
      subtitle = "Median and IQR across simulation replicates within each beta regime.",
      x = "Simulation date",
      y = y_lab
    ) +
    scale_x_date(date_breaks = "3 months", date_labels = "%b\n%Y") +
    theme_pub_traj()
  
  if (percent) {
    p <- p + scale_y_continuous(labels = percent_format(accuracy = 0.1))
  }
  
  p
}

# -----------------------------------------------------------
# 8. Create plots: ALL beta pooled
# -----------------------------------------------------------
plot_total_infected_all_beta <- plot_all_beta(
  data = trajectory_summary_all_beta,
  y_median = "total_infected_median",
  y_q25 = "total_infected_q25",
  y_q75 = "total_infected_q75",
  y_lab = "Total infected patients",
  title_text = "Total infections over time by seed type"
)

plot_prevalence_all_beta <- plot_all_beta(
  data = trajectory_summary_all_beta,
  y_median = "prevalence_median",
  y_q25 = "prevalence_q25",
  y_q75 = "prevalence_q75",
  y_lab = "Overall prevalence",
  title_text = "Overall prevalence over time by seed type",
  percent = TRUE
)

plot_hospitals_with_case_all_beta <- plot_all_beta(
  data = trajectory_summary_all_beta,
  y_median = "hospitals_with_case_median",
  y_q25 = "hospitals_with_case_q25",
  y_q75 = "hospitals_with_case_q75",
  y_lab = "Hospitals with at least one case",
  title_text = "Hospitals with at least one case over time by seed type"
)

# -----------------------------------------------------------
# 9. Create plots: stratified by low / mid / high beta regime
# -----------------------------------------------------------
plot_total_infected_by_beta <- plot_by_beta_regime(
  data = trajectory_summary_by_beta_regime,
  y_median = "total_infected_median",
  y_q25 = "total_infected_q25",
  y_q75 = "total_infected_q75",
  y_lab = "Total infected patients",
  title_text = "Total infections over time by seed type and beta regime"
)

plot_prevalence_by_beta <- plot_by_beta_regime(
  data = trajectory_summary_by_beta_regime,
  y_median = "prevalence_median",
  y_q25 = "prevalence_q25",
  y_q75 = "prevalence_q75",
  y_lab = "Overall prevalence",
  title_text = "Overall prevalence over time by seed type and beta regime",
  percent = TRUE
)

plot_hospitals_with_case_by_beta <- plot_by_beta_regime(
  data = trajectory_summary_by_beta_regime,
  y_median = "hospitals_with_case_median",
  y_q25 = "hospitals_with_case_q25",
  y_q75 = "hospitals_with_case_q75",
  y_lab = "Hospitals with at least one case",
  title_text = "Hospitals with at least one case over time by seed type and beta regime"
)

# Print plots to view in the RStudio Plots pane
plot_total_infected_all_beta
plot_prevalence_all_beta
plot_hospitals_with_case_all_beta

plot_total_infected_by_beta
plot_prevalence_by_beta
plot_hospitals_with_case_by_beta

# -----------------------------------------------------------
# 10. Save plots to Outputs/saved_results
# -----------------------------------------------------------
ggsave(
  filename = file.path(save_dir, "plot_total_infected_all_beta.png"),
  plot = plot_total_infected_all_beta,
  width = 11,
  height = 8.5,
  dpi = 300
)

ggsave(
  filename = file.path(save_dir, "plot_prevalence_all_beta.png"),
  plot = plot_prevalence_all_beta,
  width = 11,
  height = 8.5,
  dpi = 300
)

ggsave(
  filename = file.path(save_dir, "plot_hospitals_with_case_all_beta.png"),
  plot = plot_hospitals_with_case_all_beta,
  width = 11,
  height = 8.5,
  dpi = 300
)

ggsave(
  filename = file.path(save_dir, "plot_total_infected_by_beta_regime.png"),
  plot = plot_total_infected_by_beta,
  width = 16,
  height = 8.5,
  dpi = 300
)

ggsave(
  filename = file.path(save_dir, "plot_prevalence_by_beta_regime.png"),
  plot = plot_prevalence_by_beta,
  width = 16,
  height = 8.5,
  dpi = 300
)

ggsave(
  filename = file.path(save_dir, "plot_hospitals_with_case_by_beta_regime.png"),
  plot = plot_hospitals_with_case_by_beta,
  width = 16,
  height = 8.5,
  dpi = 300
)



```

#### Plotting the Results in Colorful Graphs

```{r plot colorful, echo = FALSE, warning = FALSE}
# ===========================================================
# PRESENTATION-STYLE / POWERPOINT PLOTS
# ===========================================================

library(ggplot2)
library(dplyr)
library(scales)

# -----------------------------------------------------------
# Create an output folder for presentation-style figures
# -----------------------------------------------------------
ppt_plot_dir <- file.path(save_dir, "ppt_plots")

if (!dir.exists(ppt_plot_dir)) {
  dir.create(ppt_plot_dir, recursive = TRUE)
}

# -----------------------------------------------------------
# Slide-friendly labels and colors
# -----------------------------------------------------------
seed_palette <- c(
  "Highest in/out degree" = "#1b9e77",
  "Highest betweenness" = "#d95f02",
  "Largest beds/admissions" = "#7570b3",
  "Largest incoming transfers" = "#e7298a",
  "Largest outgoing transfers" = "#66a61e",
  "Random hospital" = "#e6ab02"
)

beta_palette <- c(
  "low" = "#4daf4a",
  "mid" = "#377eb8",
  "high" = "#e41a1c"
)

# -----------------------------------------------------------
# PowerPoint theme
#
# Larger fonts, stronger contrast, cleaner look for slides
# -----------------------------------------------------------
theme_ppt_traj <- function() {
  theme_minimal(base_size = 16) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_line(color = "grey85", linewidth = 0.4),
      strip.text = element_text(face = "bold", size = 14, color = "black"),
      strip.background = element_rect(fill = "grey92", color = "grey70"),
      axis.title = element_text(face = "bold", size = 15),
      axis.text = element_text(color = "black", size = 12),
      axis.text.x = element_text(angle = 45, hjust = 1),
      plot.title = element_text(face = "bold", size = 20),
      plot.subtitle = element_text(size = 14),
      legend.title = element_text(face = "bold", size = 13),
      legend.text = element_text(size = 12),
      legend.position = "bottom",
      plot.background = element_rect(fill = "white", color = NA),
      panel.border = element_rect(color = "grey60", fill = NA, linewidth = 0.6)
    )
}

# -----------------------------------------------------------
# Add clean display labels to the trajectory summary objects
# -----------------------------------------------------------
trajectory_summary_all_beta_ppt <- trajectory_summary_all_beta %>%
  mutate(
    seed_label = factor(
      seed_label,
      levels = c(
        "Highest in/out degree",
        "Highest betweenness",
        "Largest beds/admissions",
        "Largest incoming transfers",
        "Largest outgoing transfers",
        "Random hospital"
      )
    )
  )

trajectory_summary_by_beta_regime_ppt <- trajectory_summary_by_beta_regime %>%
  mutate(
    seed_label = factor(
      seed_label,
      levels = c(
        "Highest in/out degree",
        "Highest betweenness",
        "Largest beds/admissions",
        "Largest incoming transfers",
        "Largest outgoing transfers",
        "Random hospital"
      )
    ),
    beta_regime = factor(beta_regime, levels = c("low", "mid", "high"))
  )

# -----------------------------------------------------------
# Function: pooled across all beta values
#
# Colored by seed type, with one panel containing all lines
# This is often better for PowerPoint than many small facets.
# -----------------------------------------------------------
plot_all_beta_ppt <- function(data, y_median, y_q25, y_q75, y_lab, title_text, percent = FALSE) {
  
  p <- ggplot(
    data,
    aes(
      x = date,
      y = .data[[y_median]],
      color = seed_label,
      fill = seed_label
    )
  ) +
    geom_ribbon(
      aes(
        ymin = .data[[y_q25]],
        ymax = .data[[y_q75]]
      ),
      alpha = 0.18,
      color = NA
    ) +
    geom_line(linewidth = 1.2) +
    scale_color_manual(values = seed_palette) +
    scale_fill_manual(values = seed_palette) +
    labs(
      title = title_text,
      subtitle = "Median trajectories with interquartile range ribbons across all beta regimes.",
      x = "Simulation date",
      y = y_lab,
      color = "Seed type",
      fill = "Seed type"
    ) +
    scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
    theme_ppt_traj()
  
  if (percent) {
    p <- p + scale_y_continuous(labels = percent_format(accuracy = 0.1))
  }
  
  p
}

# -----------------------------------------------------------
# Function: stratified by beta regime
#
# Facet by beta regime, still color by seed type
# -----------------------------------------------------------
plot_by_beta_regime_ppt <- function(data, y_median, y_q25, y_q75, y_lab, title_text, percent = FALSE) {
  
  p <- ggplot(
    data,
    aes(
      x = date,
      y = .data[[y_median]],
      color = seed_label,
      fill = seed_label
    )
  ) +
    geom_ribbon(
      aes(
        ymin = .data[[y_q25]],
        ymax = .data[[y_q75]]
      ),
      alpha = 0.15,
      color = NA
    ) +
    geom_line(linewidth = 1.1) +
    facet_wrap(~ beta_regime, ncol = 1, scales = "free_y") +
    scale_color_manual(values = seed_palette) +
    scale_fill_manual(values = seed_palette) +
    labs(
      title = title_text,
      subtitle = "Median trajectories with interquartile range ribbons, stratified by beta regime.",
      x = "Simulation date",
      y = y_lab,
      color = "Seed type",
      fill = "Seed type"
    ) +
    scale_x_date(date_breaks = "3 months", date_labels = "%b\n%Y") +
    theme_ppt_traj()
  
  if (percent) {
    p <- p + scale_y_continuous(labels = percent_format(accuracy = 0.1))
  }
  
  p
}

# -----------------------------------------------------------
# A second PowerPoint option:
# facet by seed type for all beta pooled, but keep color accents
# -----------------------------------------------------------
plot_all_beta_faceted_ppt <- function(data, y_median, y_q25, y_q75, y_lab, title_text, percent = FALSE) {
  
  p <- ggplot(
    data,
    aes(
      x = date,
      y = .data[[y_median]],
      color = seed_label,
      fill = seed_label,
      group = seed_label
    )
  ) +
    geom_ribbon(
      aes(
        ymin = .data[[y_q25]],
        ymax = .data[[y_q75]]
      ),
      alpha = 0.20,
      color = NA
    ) +
    geom_line(linewidth = 1.2) +
    facet_wrap(~ seed_label, scales = "free_y", ncol = 2) +
    scale_color_manual(values = seed_palette) +
    scale_fill_manual(values = seed_palette) +
    labs(
      title = title_text,
      subtitle = "Median and interquartile range across all beta regimes.",
      x = "Simulation date",
      y = y_lab
    ) +
    scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
    theme_ppt_traj() +
    theme(legend.position = "none")
  
  if (percent) {
    p <- p + scale_y_continuous(labels = percent_format(accuracy = 0.1))
  }
  
  p
}

# -----------------------------------------------------------
# Create pooled-across-beta PowerPoint plots
# -----------------------------------------------------------
ppt_total_infected_all_beta <- plot_all_beta_ppt(
  data = trajectory_summary_all_beta_ppt,
  y_median = "total_infected_median",
  y_q25 = "total_infected_q25",
  y_q75 = "total_infected_q75",
  y_lab = "Total infected patients",
  title_text = "Total infections over time by seed type"
)

ppt_prevalence_all_beta <- plot_all_beta_ppt(
  data = trajectory_summary_all_beta_ppt,
  y_median = "prevalence_median",
  y_q25 = "prevalence_q25",
  y_q75 = "prevalence_q75",
  y_lab = "Overall prevalence",
  title_text = "Overall prevalence over time by seed type",
  percent = TRUE
)

ppt_hospitals_with_case_all_beta <- plot_all_beta_ppt(
  data = trajectory_summary_all_beta_ppt,
  y_median = "hospitals_with_case_median",
  y_q25 = "hospitals_with_case_q25",
  y_q75 = "hospitals_with_case_q75",
  y_lab = "Hospitals with at least one case",
  title_text = "Hospitals with at least one case over time by seed type"
)

# -----------------------------------------------------------
# Create faceted pooled-across-beta PowerPoint plots
# -----------------------------------------------------------
ppt_total_infected_all_beta_faceted <- plot_all_beta_faceted_ppt(
  data = trajectory_summary_all_beta_ppt,
  y_median = "total_infected_median",
  y_q25 = "total_infected_q25",
  y_q75 = "total_infected_q75",
  y_lab = "Total infected patients",
  title_text = "Total infections over time by seed type"
)

ppt_prevalence_all_beta_faceted <- plot_all_beta_faceted_ppt(
  data = trajectory_summary_all_beta_ppt,
  y_median = "prevalence_median",
  y_q25 = "prevalence_q25",
  y_q75 = "prevalence_q75",
  y_lab = "Overall prevalence",
  title_text = "Overall prevalence over time by seed type",
  percent = TRUE
)

ppt_hospitals_with_case_all_beta_faceted <- plot_all_beta_faceted_ppt(
  data = trajectory_summary_all_beta_ppt,
  y_median = "hospitals_with_case_median",
  y_q25 = "hospitals_with_case_q25",
  y_q75 = "hospitals_with_case_q75",
  y_lab = "Hospitals with at least one case",
  title_text = "Hospitals with at least one case over time by seed type"
)

# -----------------------------------------------------------
# Create beta-regime-stratified PowerPoint plots
# -----------------------------------------------------------
ppt_total_infected_by_beta <- plot_by_beta_regime_ppt(
  data = trajectory_summary_by_beta_regime_ppt,
  y_median = "total_infected_median",
  y_q25 = "total_infected_q25",
  y_q75 = "total_infected_q75",
  y_lab = "Total infected patients",
  title_text = "Total infections over time by seed type and beta regime"
)

ppt_prevalence_by_beta <- plot_by_beta_regime_ppt(
  data = trajectory_summary_by_beta_regime_ppt,
  y_median = "prevalence_median",
  y_q25 = "prevalence_q25",
  y_q75 = "prevalence_q75",
  y_lab = "Overall prevalence",
  title_text = "Overall prevalence over time by seed type and beta regime",
  percent = TRUE
)

ppt_hospitals_with_case_by_beta <- plot_by_beta_regime_ppt(
  data = trajectory_summary_by_beta_regime_ppt,
  y_median = "hospitals_with_case_median",
  y_q25 = "hospitals_with_case_q25",
  y_q75 = "hospitals_with_case_q75",
  y_lab = "Hospitals with at least one case",
  title_text = "Hospitals with at least one case over time by seed type and beta regime"
)

# -----------------------------------------------------------
# Print plots to the Plots pane
# -----------------------------------------------------------
ppt_total_infected_all_beta
ppt_prevalence_all_beta
ppt_hospitals_with_case_all_beta

ppt_total_infected_all_beta_faceted
ppt_prevalence_all_beta_faceted
ppt_hospitals_with_case_all_beta_faceted

ppt_total_infected_by_beta
ppt_prevalence_by_beta
ppt_hospitals_with_case_by_beta

# -----------------------------------------------------------
# Save PowerPoint-friendly plots
# -----------------------------------------------------------
ggsave(
  filename = file.path(ppt_plot_dir, "ppt_total_infected_all_beta.png"),
  plot = ppt_total_infected_all_beta,
  width = 12,
  height = 7,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_prevalence_all_beta.png"),
  plot = ppt_prevalence_all_beta,
  width = 12,
  height = 7,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_hospitals_with_case_all_beta.png"),
  plot = ppt_hospitals_with_case_all_beta,
  width = 12,
  height = 7,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_total_infected_all_beta_faceted.png"),
  plot = ppt_total_infected_all_beta_faceted,
  width = 12,
  height = 8,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_prevalence_all_beta_faceted.png"),
  plot = ppt_prevalence_all_beta_faceted,
  width = 12,
  height = 8,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_hospitals_with_case_all_beta_faceted.png"),
  plot = ppt_hospitals_with_case_all_beta_faceted,
  width = 12,
  height = 8,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_total_infected_by_beta_regime.png"),
  plot = ppt_total_infected_by_beta,
  width = 14,
  height = 10,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_prevalence_by_beta_regime.png"),
  plot = ppt_prevalence_by_beta,
  width = 14,
  height = 10,
  dpi = 300
)

ggsave(
  filename = file.path(ppt_plot_dir, "ppt_hospitals_with_case_by_beta_regime.png"),
  plot = ppt_hospitals_with_case_by_beta,
  width = 14,
  height = 10,
  dpi = 300
)

# -----------------------------------------------------------
# Save the PowerPoint plot objects so they can be reloaded later
# -----------------------------------------------------------
ppt_plot_objects <- list(
  ppt_total_infected_all_beta = ppt_total_infected_all_beta,
  ppt_prevalence_all_beta = ppt_prevalence_all_beta,
  ppt_hospitals_with_case_all_beta = ppt_hospitals_with_case_all_beta,
  ppt_total_infected_all_beta_faceted = ppt_total_infected_all_beta_faceted,
  ppt_prevalence_all_beta_faceted = ppt_prevalence_all_beta_faceted,
  ppt_hospitals_with_case_all_beta_faceted = ppt_hospitals_with_case_all_beta_faceted,
  ppt_total_infected_by_beta = ppt_total_infected_by_beta,
  ppt_prevalence_by_beta = ppt_prevalence_by_beta,
  ppt_hospitals_with_case_by_beta = ppt_hospitals_with_case_by_beta
)

saveRDS(
  ppt_plot_objects,
  file = file.path(save_dir, "ppt_plot_objects.rds"),
  compress = "xz"
)

```

### Overall epidemic trajectory

Plot total infected over time.

```{r plot-total-infected}
# TODO:
# - create line plot for total infected
# - optionally add confidence intervals if multiple runs are used
```

### Number of hospitals affected

Plot the number of hospitals with at least one case.

```{r plot-hospitals-affected}
# TODO:
# - summarize daily count of hospitals with infection
# - create time-series plot
```

### Export saved outputs

Write simulation outputs to file.

```{r save-outputs}
# TODO:
# - save daily results
# - save overall results
# - save infected transfer results if needed
```

## Intervention scenario engine

### IPC intervention implementation

Create functions that reduce within-hospital transmission in selected hospitals.

```{r ipc-scenarios}
# TODO:
# - define how beta_within changes under IPC scenarios
# - allow universal, hospital-type, network-based, and burden-based targeting
```

### Admission screening implementation

Create functions that reduce importation at admission or transfer-in.

```{r screening-scenarios}
# TODO:
# - define screening probability
# - define screening effectiveness
# - apply to all admissions, transfer-ins, or targeted groups
```

### Network modification implementation

Create functions that modify transfer matrices while preserving chosen constraints.

```{r network-modification-scenarios}
# TODO:
# - reroute selected transfers
# - preserve total transfer volume where required
# - preserve hospital type matching or geography where required
```

### Scenario grid

Build a master table of all scenarios to run.

```{r scenario-grid}
# TODO:
# - define scenario IDs
# - define scenario family
# - define target rule
# - define intervention intensity
# - define operational constraints
```

## Targeting algorithms

### Universal targeting

```{r universal-targeting}
# TODO:
# - define a function that targets all eligible units
```

### Hospital-type targeting

```{r hospital-type-targeting}
# TODO:
# - define facility categories
# - select eligible hospitals by type
```

### Network-informed targeting

```{r network-informed-targeting}
# TODO:
# - compute degree, weighted degree, betweenness, bridge status, hub status
# - rank hospitals and select top targets
```

### Epidemiologic targeting

```{r epidemiologic-targeting}
# TODO:
# - compute baseline prevalence, importation burden, acquisition burden
# - target high-burden hospitals
```

## Seeding event analyses

### Identify seeding events from observed data

```{r identify-seeding-events}
# TODO:
# - define operational criteria for a seeding event
# - apply to surveillance and epidemiologic data
```

### Attribute likely seeding sources

```{r source-attribution}
# TODO:
# - compare external importation versus domestic network spread
# - combine timing, transfer counts, and network proximity
```

### Identify candidate infector hospitals

```{r candidate-infector-hospitals}
# TODO:
# - rank candidate source hospitals
# - use time lag, patient sharing, and network distance
```

## Simulation experiments for seeding events

### Vary seed-location characteristics

```{r vary-seed-locations}
# TODO:
# - simulate seeding in different hospital types
# - simulate seeding in different network positions
# - simulate seeding in different geographic regions
```

### Vary pathogen-specific characteristics

```{r vary-pathogen-characteristics}
# TODO:
# - vary carriage duration
# - vary transmissibility
# - compare rare versus common ARB assumptions
```

### Cross-country comparison

```{r cross-country-comparison}
# TODO:
# - replicate workflow for France and Germany
# - harmonize outputs for comparison
```

## Statistical analysis of simulation outputs

### Simulation summary dataset

```{r simulation-summary-data}
# TODO:
# - construct one row per simulation run or scenario
# - include outcome metrics and explanatory variables
```

### Model explanatory factors

```{r explanatory-models}
# TODO:
# - fit regression or mixed models to quantify effects of seed and network characteristics
# - consider institution type, network metrics, geography, transmissibility, and carriage duration
```

### Outcome metrics

```{r outcome-metrics}
# TODO:
# - compute regional prevalence
# - compute cumulative acquisitions
# - compute cumulative importations
# - compute number of affected hospitals
# - compute speed and extent of spread
```

## Risk mapping

### Institution-level risk maps

```{r institution-risk-maps}
# TODO:
# - join institution-level risk estimates to geographic coordinates
# - produce maps for seeding-event risk
```

### Cross-pathogen and cross-country maps

```{r comparative-risk-maps}
# TODO:
# - compare maps across pathogens
# - compare maps across France and Germany
```

## Manuscript-ready tables and figures

### Table shells

```{r table-shells}
# TODO:
# - create table shells for scenario definitions
# - create table shells for seeding event summaries
# - create table shells for intervention effects
```

### Figure shells

```{r figure-shells}
# TODO:
# - epidemic trajectories
# - affected-hospital curves
# - network or map figures
# - risk maps
```



#### **Intervention definitions**
  
   organize intervention scenarios into three main classes.
  
  - **Improved IPC within hospitals** :  evaluate interventions that reduce within-hospital transmission risk.
  
  - **Admission screening and quarantine/isolation**: evaluate interventions that reduce pathogen importation at admission or transfer-in.
  
  - **Network-modifying transfer interventions**:  evaluate interventions that alter patient-transfer patterns across the healthcare network while preserving key system constraints.

####  **Scenario parameterization**
  
   define each scenario according to the dimensions below.
  
  - **Unit of intervention**:  specify whether the intervention acts at the level of hospital, admission, transfer route, source hospital, or destination hospital.
  
  - **Mechanism of action**:  specify whether the intervention changes within-hospital transmission, admission or transfer-related importation, or network connectivity and transfer probabilities.
  
  - **Intervention intensity**:  define the strength of each intervention, such as percent reduction in transmission, proportion of admissions screened, screening effectiveness, or proportion of transfers rerouted.
  
  - **Operational constraints**:  determine whether scenarios preserve total number of patients, total number of transfers, hospital type matching, and geographic or capacity constraints.

- **Targeting algorithms**: compare multiple targeting strategies across intervention classes.
  
  - **Universal targeting**:  apply the intervention to all hospitals, admissions, or eligible transfers.
  
  - **Hospital-type targeting**:  target selected facility categories, such as tertiary or referral hospitals.
  
  - **Network-informed targeting**:  target hospitals based on their role in the network, including measures such as degree or weighted degree, betweenness centrality, transfer volume, and bridge or hub status.
  
  - **Epidemiologic targeting**:  target hospitals based on epidemiologic burden, such as baseline prevalence, importation burden, and acquisition burden.

#### **Seeding event analyses**
  
  This section will define how observed epidemiologic data and surveillance data are used to identify and interpret seeding events.
  
  - **Definition and identification of seeding events**:     analyze epidemiologic and surveillance data to identify AMR seeding events at the regional or country level for different antibiotic-resistant bacteria.
  
  - **Source attribution of seeding events**:   disentangle the relative contribution of environmental sources, human population sources, importation from foreign countries, and transmission through the healthcare network.
  
  - **Identification of potential infector hospitals**:  identify candidate infector hospitals associated with newly colonized hospitals by considering temporal delay between reported cases, network distance, and number of transferred patients.
  
  - **Comparative role of importation versus within-network spread**:  assess whether observed seeding events are more consistent with external introduction into the region or country or with propagation through the domestic healthcare network.

#### **Simulation of seeding events and downstream spread**
  
  This section will describe how seeding events are imposed in the dynamic model and how their downstream consequences are evaluated.
  
  - **Simulation framework**:  use the network-based dynamic models developed in Task 3 to simulate outbreaks initiated by seeding events.
  
  - **Seed-location characteristics**: vary the characteristics of the healthcare institution where the pathogen is first seeded, including institution type, network position, and geographic area.
  
  - **Pathogen-specific characteristics**: perform these analyses for different antibiotic-resistant bacteria and vary bacterial characteristics such as carriage duration and transmissibility.
  
  - **Network-specific comparison across settings**: conduct the analyses in France and Germany to determine how pathogen characteristics and network structure influence the effect of seeding events on subsequent spread.

#### **Statistical analysis of simulation outputs**
  
  This section will describe how simulation results are summarized and modeled.
  
  - **Evaluation of spread patterns**: analyze simulation outputs to quantify how characteristics of the seeding event and seeded institution shape downstream epidemiologic patterns.
  
  - **Explanatory factors**: evaluate the impact of institution type, network position, geographic location, pathogen carriage duration, pathogen transmissibility, and network structure.
  
  - **Outcome metrics**: summarize spread using outcomes such as regional prevalence, cumulative acquisitions, cumulative importations, number of affected hospitals, and speed and extent of dissemination across the network.

#### **Risk mapping**
  
  This section will translate simulation outputs into spatially interpretable institution-level risk summaries.
  
  - **Institution-level risk maps**: generate risk maps quantifying the level of risk associated with a seeding event in a given institution.
  
  - **Cross-pathogen and cross-country comparison**   compare these risk maps across antibiotic-resistant bacteria and across France and Germany to identify settings in which seeding events are most likely to drive broader dissemination.

#### **Scenario families to pre-specify**
  
  This section will define the major intervention families that should be created before large simulation runs begin.
  
  - **IPC scenarios**
    
     evaluate IPC in all hospitals, IPC in selected hospital types, IPC in the most central hospitals, and IPC in hospitals with high baseline burden.
  
  - **Screening scenarios**
    
     evaluate screening at all admissions, screening at transfer-in admissions only, screening in selected hospital types, screening targeted to patients transferred from selected source hospitals, and screening targeted to high-risk hospitals.
  
  - **Network modification scenarios**
    
     evaluate rerouting transfers away from highly central hospitals, rerouting transfers from high-prevalence hospitals, rerouting selected high-volume edges, and rerouting within the same hospital type while preserving total patient flow.
