---
title: "ARCANE - Incidence Calibration and Seeding Analysis"
subtitle: "Novel pathogen introduction on the French inter-hospital transfer network"
author: "MESuRS/Cnam - Task 4.3"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: flatly
    highlight: tango
    code_folding: hide
    fig_width: 11
    fig_height: 5.5
  powerpoint_presentation:
    slide_level: 2
    fig_width: 11
    fig_height: 5.2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, dpi=150)
```

```{r libraries}
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(scales)

LOCAL_ROOT   <- "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/calibration_jobs"

# --- Calibration results (compile_prevalence.R output) ---
CALIB_DIR    <- file.path(LOCAL_ROOT, "Outputs", "prevalence_compiled")
calib_rds    <- list.files(CALIB_DIR, "compiled_prevalence.*\\.rds$", full.names=TRUE)
has_calib    <- length(calib_rds) > 0
if (has_calib) {
  calib      <- readRDS(tail(sort(calib_rds), 1))
  message("Calibration results loaded: ", nrow(calib$scalar_df), " simulations")
}

# --- Seeding results (compile_seeding_novel.R output) ---
SEEDING_DIR  <- file.path(LOCAL_ROOT, "Outputs", "seeding_novel", "compiled")
OUT_DIR      <- file.path(SEEDING_DIR, "analysis")
dir.create(OUT_DIR, recursive=TRUE, showWarnings=FALSE)

csv_file <- list.files(SEEDING_DIR, "seeding_summary_compiled\\.csv$", full.names=TRUE)
rds_file <- list.files(SEEDING_DIR, "compiled_seeding_novel.*\\.rds$",  full.names=TRUE)

if (length(csv_file) == 0)
  stop("seeding_summary_compiled.csv not found. Run compile_seeding_novel.R first.")

df_raw <- read.csv(tail(sort(csv_file), 1), stringsAsFactors=FALSE)

has_traj <- FALSE
if (length(rds_file) > 0) {
  tryCatch({
    res      <- readRDS(tail(sort(rds_file), 1))
    traj_raw <- res$traj_df
    has_traj <- !is.null(traj_raw) && nrow(traj_raw) > 0
    sources  <- res$sources
    message("Seeding results: ", nrow(df_raw), " sims | sources: ",
            paste(sources, collapse=", "))
  }, error=function(e) message("RDS load failed: ", e$message))
}
```

```{r prep-seeding}
df <- df_raw %>%
  mutate(
    tier = factor(tier, levels=c("Low","Moderate")),
    seed_type = factor(seed_type,
                       levels=c("fixed","type_random"),
                       labels=c("Network-central (NC)",
                                "Facility-type random (FTR)")),
    seed_rule_short = case_when(
      grepl("betweenness", seed_rule) ~ "Network hub",
      seed_rule == "random_MCO"       ~ "Random MCO",
      seed_rule == "random_SSR"       ~ "Random SSR",
      seed_rule == "random_MCO_SSR"   ~ "Random MCO/SSR",
      TRUE                            ~ seed_rule
    ),
    ever_extinct = as.logical(ever_extinct),
    net_ss_prev_capped = pmin(net_ss_prev_pct,      100),
    fac_ss_prev_capped = pmin(fac_ss_prev_mean_pct, 100),
    # SS will be computed from trajectories in traj-prep using
    # window-to-window comparison (last 15 vs previous 15 days).
    # Placeholder here so df_alive can be created before traj loads.
    ss_reached = NA
  )

df_alive <- df %>% filter(!ever_extinct)
tier_pal <- c(Low="#009E73", Moderate="#E69F00")
type_pal <- c(`Network-central (NC)`    = "#0057B8",
               `Facility-type random (FTR)` = "#C1392B")

theme_arc <- function(bs=12)
  theme_bw(base_size=bs) +
  theme(plot.title=element_text(face="bold"),
        plot.subtitle=element_text(colour="grey40", size=rel(0.85)),
        panel.grid.minor=element_blank(),
        legend.position="right",
        strip.background=element_rect(fill="grey92"),
        strip.text=element_text(face="bold"))

# Box + scatter helper (replaces violin)
geom_boxscatter <- function(fill_var, colour_var=fill_var,
                             dodge=0.7, jitter_w=0.08, pt_size=1.5,
                             pt_alpha=0.5, box_alpha=0.5) {
  list(
    geom_boxplot(aes_string(fill=fill_var),
                 position=position_dodge(dodge),
                 width=0.45, outlier.shape=NA,
                 alpha=box_alpha, colour="grey30", linewidth=0.5),
    geom_jitter(aes_string(colour=colour_var),
                position=position_jitterdodge(jitter.width=jitter_w,
                                               dodge.width=dodge),
                size=pt_size, alpha=pt_alpha)
  )
}
```

---

# Methodology

## Study population and network

The French inter-hospital transfer network was derived from 2024 PMSI (Programme de Medicalisation des Systemes d'Information) administrative discharge data. The network comprises **`r if(has_calib) format(calib$params$H, big.mark=",") else "2,519"` hospitals** (etablissements de soins) including acute care (MCO - Medecine, Chirurgie, Obstetrique), rehabilitation (SSR - Soins de Suite et de Readaptation), psychiatric (PSY), home hospitalisation (HAD - Hospitalisation a Domicile), and mixed (MCO/SSR) facilities. Daily transfer counts between each pair of facilities were derived from rolling 7-day sums, divided by 7 to give daily averages and rounded to the nearest integer (minimum 1). Total network beds: `r if(has_calib) format(calib$params$total_beds, big.mark=",") else "~500,000"`.

## Patient flow model

The model assumes **constant full bed occupancy** throughout the simulation. Daily patient turnover at each hospital is determined by observed daily admission counts from the 2024 PMSI (NO_ADMISSION_DAILY_DIRCT_HBN dataset; `r format(nrow(df_raw)*0, big.mark=",")`hospital-days). Because occupancy is assumed constant, daily discharges equal daily admissions at each facility. The pathogen transmission status of discharging patients is determined by a **hypergeometric draw** - sampling without replacement from the current colonised (I) and susceptible (S) patients at each facility - preserving the colonisation proportion among those leaving. Of discharged patients, a facility-specific fraction is transferred to other hospitals (via the transfer probability matrix P); the remainder are admitted from the community. The number of patients admitted from the community equals total admissions minus transfers received. If incoming transfers exceed a facility's admission quota on a given day, excess transfers are scaled down proportionally (capacity enforcement). Community-admitted patients may be colonised at admission with probability pi (pi\_vec).

## SIS transmission model

Within each hospital h on each day t, susceptible patients (S) can acquire colonisation from infected/colonised patients (I) according to a **frequency-dependent stochastic SIS (Susceptible-Infected-Susceptible)** process:

```
P(new colonisation | S, I, N) = 1 − exp(−beta x I/N)
```

where beta (beta) is the daily within-hospital transmission probability per susceptible-infectious contact (units: per day), N = S + I is total hospital occupancy, and new\_inf ~ Binomial(S, p\_inf). Biological decolonisation occurs at rate gamma (gamma) = 1/387 per day, corresponding to a mean carriage duration of 387 days for ESBL-producing Enterobacterales (ESBL-E). No patient isolation (alpha = 0) is assumed.

## Incidence calibration

**Incidence targets** were derived from ECDC EARS-Net 2022 antibiotic resistance carriage prevalence benchmarks, converted to hospital-acquired incidence per 1,000 patient-days using:

```
incidence = (gamma + 1/LOS) x (P_total − pi) x 1,000
```

where LOS is the network-weighted mean length of stay (9.28 days from PMSI data) and P_total is the ECDC carriage prevalence for each resistance tier. Three tiers are defined using ECDC official category boundaries:

```{r calib-targets-table}
tibble::tribble(
  ~Tier, ~`ECDC category`, ~`ECDC carriage range`, ~`Incidence target (/1,000 pd)`, ~`Epidemiological examples`,
  "Low",      "low (>1-10%)",      "1-10%",   "0.99-10.92",
    "CRE in France/Germany, VRE in Scandinavia, MRSA in low-burden Northern Europe",
  "Moderate", "moderate (>10-20%)", "10-20%", "10.92-21.96",
    "MRSA in moderate-burden settings, ESBL-E in Eastern EU",
  "High",     "high (>20-50%)",     "20-50%", "21.96-55.06",
    "MRSA in Southern/Eastern Europe (Greece, Romania), ESBL-E in high-burden settings"
) %>%
  kable(caption=paste0("Incidence calibration targets derived from ECDC EARS-Net 2022. ",
                        "CRE = Carbapenem-Resistant Enterobacterales. ",
                        "VRE = Vancomycin-Resistant Enterococci. ",
                        "MRSA = Methicillin-Resistant Staphylococcus aureus. ",
                        "ESBL-E = Extended-Spectrum Beta-Lactamase-producing Enterobacterales. ",
                        "pd = patient-days.")) %>%
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE) %>%
  column_spec(1, bold=TRUE)
```

beta was calibrated via **grid search** (beta = 0.005-0.120, step 0.005; 24 values) combined with three community carriage scenarios (pi = 0.001, 0.010, 0.050), run across `r if(has_calib) n_distinct(calib$scalar_df$job_index) else "10"` parallel cluster jobs (3 replicates per job = 30 total replicates per beta x pi combination). The best-fit beta per tier was defined as the replicate whose achieved incidence was closest to the tier midpoint.

## Seeding simulation

**Seeding rules** - eight candidate introduction hospitals were evaluated:

```{r seed-rules-table}
tibble::tribble(
  ~`Seed rule`, ~Type, ~`Selection criterion`,
  "Network hub (NC)", "Network-central (NC)",
    "Hospital ranking first on ALL five centrality metrics simultaneously: in-degree, out-degree, betweenness centrality, total bed count, and outgoing transfer volume. In this network, all five metrics identified the same facility (750100125, MCO/SSR, Ile-de-France, 1,713 beds), consistent with a scale-free network structure.",
  "Random MCO (FTR)", "Facility-type random (FTR)",
    "One acute care hospital (MCO) drawn uniformly at random per simulation replicate.",
  "Random SSR (FTR)", "Facility-type random (FTR)",
    "One rehabilitation hospital (SSR) drawn uniformly at random per simulation replicate.",
  "Random MCO/SSR (FTR)", "Facility-type random (FTR)",
    "One mixed acute/rehabilitation facility (MCO/SSR) drawn uniformly at random per simulation replicate."
) %>%
  kable(caption=paste0("Seeding rules. NC = Network-central. FTR = Facility-type random. ",
                        "MCO = Medecine Chirurgie Obstetrique (acute care). ",
                        "SSR = Soins de Suite et de Readaptation (rehabilitation). ",
                        "MCO/SSR = mixed facility. ",
                        "All centrality metrics computed on the directed transfer network ",
                        "using igraph (betweenness: directed, unnormalised).")) %>%
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE) %>%
  column_spec(1, bold=TRUE) %>%
  column_spec(2, width="18%")
```

**Simulation parameters:**

```{r sim-params-table}
tibble::tribble(
  ~Parameter, ~Value, ~Description,
  "N_SEED_INF",    "5",           "Index cases introduced on day 0 in the seed hospital",
  "Tmax",          "732 days",    "Simulation duration (2 x 366 days, cycling 2024 PMSI data annually)",
  "gamma (gamma)",     "1/387 per day","Daily biological decolonisation rate; mean carriage ~387 days (ESBL-E)",
  "pi_vec (pi)",    "0",           "Community carriage on admission - novel pathogen assumption (no external reservoir)",
  "N_REP",         "10 per job x 10 jobs = 100 total", "Replicates per (seed rule x tier) combination",
  "SS_WINDOW",     "30 days",     "Last N days used to compute steady-state (SS) incidence metrics",
  "Beta draws",    "Truncated normal (mean=mean_beta, sd from 95% CI width)",
                   "Per-hospital beta drawn independently; propagates calibration uncertainty"
) %>%
  kable(caption="Seeding simulation parameters. SS = steady state.") %>%
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE) %>%
  column_spec(1, bold=TRUE, monospace=TRUE)
```

## Outcome metric definitions

All outcomes are computed per simulation replicate. Analyses use non-extinct replicates only unless stated otherwise.

```{r metrics-table}
tibble::tribble(
  ~Metric, ~Abbreviation, ~Scale, ~`Exact formula`, ~`Time window`, ~`Interpretation`,

  "Network steady-state incidence",
    "net_ss_inc", "National\n(bed-weighted)",
    "mean[sum(new_inf_t)/sum(N_t) x 1,000] over last SS_WINDOW days",
    "Last 30 days",
    "National hospital-acquired incidence rate per 1,000 patient-days at near-endemic equilibrium. Directly comparable to SPARES and ECDC HAI surveillance.",

  "Facility-level mean steady-state incidence",
    "fac_ss_inc_mean", "Facility\n(unweighted)",
    "mean over active hospitals of [new_inf_t[h]/N_t[h] x 1,000], then mean over last 30 days",
    "Last 30 days",
    "Mean of per-hospital daily acquisition rates, giving equal weight to each facility regardless of size. Closer to facility-level HAI reporting.",

  "Network cumulative incidence",
    "net_cumul_inc", "National\n(bed-weighted)",
    "mean[sum(new_inf_t)/sum(N_t) x 1,000] over all Tmax days",
    "All 732 days",
    "Mean daily acquisition rate over the entire simulation. Reflects the integrated burden of colonisation throughout the epidemic trajectory, not just the end state.",

  "Network steady-state prevalence",
    "net_ss_prev_pct", "National\n(bed-weighted)",
    "mean[sum(I_loc_t)/total_beds x 100] over last 30 days",
    "Last 30 days",
    "Proportion of total network beds occupied by colonised patients at near-endemic equilibrium. NOTE: values above 100% indicate a simulation capacity overflow bug and are capped at 100% in all displays.",

  "Facility-level mean steady-state prevalence",
    "fac_ss_prev_mean_pct", "Facility\n(unweighted)",
    "mean over hospitals of [I_loc_t[h]/beds[h] x 100], then mean over last 30 days",
    "Last 30 days",
    "Mean of per-hospital colonisation proportions. Unweighted: a 10-bed rural facility counts the same as a 1,000-bed university hospital.",

  "Extinction",
    "ever_extinct", "-",
    "sum(I_loc) == 0 at any point during the simulation",
    "Any day 1-732",
    "Pathogen died out - no colonised patients remain. With pi=0 (novel pathogen), extinction occurs when the pathogen fails to establish through transfers and within-hospital transmission alone.",

  "Steady-state reached",
    "ss_reached", "-",
    "0.9 <= net_ss_inc / net_cumul_inc <= 1.1",
    "Ratio of last-30d mean to overall mean",
    "The epidemic has stabilised: the last 30-day incidence is within 10% of the overall mean. Ratio > 1.1 = still growing; ratio < 0.9 = declining."
) %>%
  kable(caption=paste0("Primary outcome metric definitions. ",
                        "I_loc = infected (colonised) patients per hospital. ",
                        "N_t = total occupied beds on day t. ",
                        "new_inf_t = new colonisations on day t. ",
                        "SS = steady state. pd = patient-days. ",
                        "HAI = healthcare-associated infection.")) %>%
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE) %>%
  column_spec(1, bold=TRUE) %>%
  column_spec(2, monospace=TRUE, width="14%") %>%
  column_spec(4, monospace=TRUE, width="28%") %>%
  row_spec(4:5, background="#fff3cd")
```

## Results compilation

Local (PSOCK, Windows) and cluster (FORK, Linux) simulation results were compiled by `compile_seeding_novel.R`. Each source is loaded separately, tagged with a source label, and row-bound into a single `sim_summary` data frame. Each simulation replicate receives a globally unique identifier (`global_sim_id`) to prevent collision between local and cluster job indices. The compiled file saved to `Outputs/seeding_novel/compiled/` is the single input to this report.

---

# Part 1 - Calibration results

```{r calib-note, results='asis'}
if (!has_calib)
  cat("> Calibration results not found - place compiled_prevalence_*.rds in Outputs/prevalence_compiled/\n")
```

```{r calib-beta-summary, eval=has_calib}
calib$beta_summary %>%
  select(beta_within, n_reps, pct_extinct, pct_ss,
         inc_median, inc_q25, inc_q75, prev_median) %>%
  mutate(across(where(is.numeric), ~round(.x, 4))) %>%
  kable(col.names=c("beta (beta)", "N reps", "Extinct (%)", "SS (%)",
                     "Inc median\n/1k pd", "Inc Q25", "Inc Q75",
                     "Prev median"),
        caption=paste0("Beta grid search results. ",
                        "Incidence (inc) per 1,000 patient-days among non-extinct reps. ",
                        "SS = % of non-extinct reps reaching steady state. ",
                        "Prev = network prevalence on final day.")) %>%
  kable_styling(bootstrap_options=c("striped","condensed"),
                full_width=TRUE, font_size=11)
```

```{r calib-tier, eval=has_calib, fig.height=5}
if (!is.null(calib$tier_analysis) && nrow(calib$tier_analysis) > 0) {
  calib_tier <- calib$tier_analysis %>%
    mutate(tier=factor(tier, levels=c("Low","Moderate","High")))

  ggplot(calib_tier, aes(x=tier, colour=tier)) +
    geom_linerange(aes(ymin=ci_lo_95, ymax=ci_hi_95),
                   linewidth=4, alpha=0.4) +
    geom_point(aes(y=mean_beta), size=6, shape=18) +
    geom_point(aes(y=best_beta), size=3.5, shape=1, colour="grey30") +
    scale_colour_manual(values=c(Low="#009E73",Moderate="#E69F00",High="#D55E00"),
                        guide="none") +
    scale_y_continuous(labels=scientific) +
    labs(title="Calibrated beta (beta) per incidence tier",
         subtitle="Diamond (*) = mean | Circle (o) = best-fit | Bar = 95% CI",
         x="Tier", y="beta (beta) per day") +
    theme_arc()
}
```

```{r calib-tier-table, eval=has_calib}
if (!is.null(calib$tier_analysis) && nrow(calib$tier_analysis) > 0) {
  calib$tier_analysis %>%
    select(tier, inc_low, inc_high, n_reps, n_jobs,
           best_beta, mean_beta, ci_lo_95, ci_hi_95, mean_inc_ach) %>%
    mutate(across(where(is.numeric), ~round(.x, 5))) %>%
    kable(col.names=c("Tier","Inc low\n/1k pd","Inc high\n/1k pd",
                       "N reps","N jobs","Best beta","Mean beta",
                       "95% CI low","95% CI high","Mean inc\nachieved"),
          caption="Tier analysis: recommended beta values per ECDC incidence tier.") %>%
    kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE)
}
```

---

# Part 2 - Seeding simulation overview

```{r overview, results='asis'}
pct_ext <- round(mean(df$ever_extinct)*100, 1)
pct_ss  <- round(mean(df_alive$ss_reached, na.rm=TRUE)*100, 1)
n_src   <- if(exists("sources")) paste(sources, collapse=", ") else "local"

cat(sprintf(
"**Scenario:** Novel pathogen | pi = 0 (no community importation)  \n
 **Sources:** %s  \n
 **Total simulations:** %d | **Tiers:** %s | **Seed rules:** %d  \n
 **Extinct:** %.1f%% | **Reached SS:** %.1f%% of non-extinct  \n
 **Key finding:** %d of %d non-extinct sims still growing at day 732",
  n_src, nrow(df),
  paste(levels(df$tier), collapse=" / "),
  n_distinct(df$seed_rule),
  pct_ext, pct_ss,
  sum(!df_alive$ss_reached, na.rm=TRUE), nrow(df_alive)
))
```

---

# Part 3 - Extinction and steady-state

## 3.1 Extinction probability by seed rule and tier

```{r extinction, fig.height=5}
ext_plot_df <- df %>%
  group_by(tier, seed_rule_short, seed_type) %>%
  summarise(pct=round(mean(ever_extinct)*100,1), n=n(), .groups="drop")

ext_max <- max(ext_plot_df$pct, na.rm=TRUE)

ext_plot_df %>%
  ggplot(aes(x=reorder(seed_rule_short, pct), y=pct, fill=tier)) +
  geom_col(position=position_dodge(0.7), width=0.6, alpha=0.88) +
  geom_text(aes(label=paste0(pct,"%")),
            position=position_dodge(0.7), hjust=-0.1, size=3) +
  scale_fill_manual(values=tier_pal, name="Tier") +
  coord_flip() +
  scale_y_continuous(limits=c(0, min(100, ext_max*1.15)),
                     expand=expansion(mult=c(0,0.05))) +
  labs(title="Extinction probability by seed rule and tier",
       subtitle="pi = 0: no community re-importation - ARB spreads only via transfers and within-hospital transmission",
       x=NULL, y="Simulations extinct (%)") +
  theme_arc()
```

## 3.2 Steady-state indicator distribution

```{r ss-indicator, fig.height=4}
# ss_reached and pct_change are populated in traj-prep.
# Show a fallback message if trajectories were not loaded.
if (!has_traj || !"pct_change" %in% names(df_alive)) {
  cat("> Steady-state indicator requires daily trajectories (traj_df). Load compiled RDS to enable.\n")
} else {
  df_alive %>%
    filter(!is.na(pct_change)) %>%
    ggplot(aes(x=pct_change, fill=tier)) +
    geom_histogram(bins=40, alpha=0.7, position="identity") +
    geom_vline(xintercept=5, linetype="dashed",
               colour="grey30", linewidth=0.8) +
    annotate("text", x=5, y=Inf,
             label="SS threshold\n(<5% change)", size=3,
             colour="grey30", vjust=2, hjust=-0.1) +
    scale_fill_manual(values=tier_pal, name="Tier") +
    labs(title="Steady-state indicator: % change between last two 15-day windows",
         subtitle="pct_change = |mean(days 718-732) - mean(days 703-717)| / mean(days 718-732) x 100  |  < 5% = stable (SS reached)",
         x="% change between windows", y="Count of simulations") +
    theme_arc()
}
```

---

# Part 4 - Primary outcome: Incidence per 1,000 patient-days

*Box = IQR (25th-75th percentile). Whiskers = 1.5 x IQR. Each dot = one simulation replicate. Non-extinct replicates only.*

## 4.1 National steady-state incidence (net_ss_inc) by seed rule

```{r net-inc-box, fig.height=5.5}
ggplot(df_alive, aes(x=reorder(seed_rule_short, net_ss_inc),
                      y=net_ss_inc, fill=tier)) +
  geom_boxplot(position=position_dodge(0.7), width=0.45,
               outlier.shape=NA, alpha=0.6,
               colour="grey30", linewidth=0.5) +
  geom_jitter(aes(colour=tier),
              position=position_jitterdodge(jitter.width=0.08,
                                             dodge.width=0.7),
              size=1.8, alpha=0.55) +
  stat_summary(fun=mean, geom="label",
               aes(label=sprintf("%.3f", after_stat(y))),
               position=position_dodge(0.7), size=2.3,
               fill="white", colour="grey20",
               label.size=0.15, label.padding=unit(0.12,"lines"),
               show.legend=FALSE) +
  scale_fill_manual(values=tier_pal,   name="Tier") +
  scale_colour_manual(values=tier_pal, name="Tier", guide="none") +
  coord_flip() +
  labs(title="National (network-level) steady-state incidence (net_ss_inc) by seed rule",
       subtitle="sum(new_inf)/sum(N) x 1,000 | last 30 days | bed-weighted | each dot = 1 replicate",
       x=NULL, y="net_ss_inc (per 1,000 patient-days)") +
  theme_arc()
```

## 4.2 Facility-level mean steady-state incidence (fac_ss_inc_mean) by seed rule

```{r fac-inc-box, fig.height=5.5}
ggplot(df_alive, aes(x=reorder(seed_rule_short, fac_ss_inc_mean),
                      y=fac_ss_inc_mean, fill=tier)) +
  geom_boxplot(position=position_dodge(0.7), width=0.45,
               outlier.shape=NA, alpha=0.6,
               colour="grey30", linewidth=0.5) +
  geom_jitter(aes(colour=tier),
              position=position_jitterdodge(jitter.width=0.08,
                                             dodge.width=0.7),
              size=1.8, alpha=0.55) +
  stat_summary(fun=mean, geom="label",
               aes(label=sprintf("%.3f", after_stat(y))),
               position=position_dodge(0.7), size=2.3,
               fill="white", colour="grey20",
               label.size=0.15, label.padding=unit(0.12,"lines"),
               show.legend=FALSE) +
  scale_fill_manual(values=tier_pal,   name="Tier") +
  scale_colour_manual(values=tier_pal, name="Tier", guide="none") +
  coord_flip() +
  labs(title="Facility-level mean steady-state incidence (fac_ss_inc_mean) by seed rule",
       subtitle="mean[new_inf[h]/N[h] x 1,000] over active hospitals | last 30 days | unweighted",
       x=NULL, y="fac_ss_inc_mean (per 1,000 patient-days)") +
  theme_arc()
```

## 4.3 National vs facility-level incidence - seeding type comparison

```{r inc-compare, fig.height=5}
df_alive %>%
  select(tier, seed_type,
         `National\n(net_ss_inc, bed-weighted)`      = net_ss_inc,
         `Facility-level\n(fac_ss_inc_mean, unweighted)` = fac_ss_inc_mean) %>%
  pivot_longer(-c(tier, seed_type), names_to="scale", values_to="inc") %>%
  ggplot(aes(x=tier, y=inc, fill=seed_type)) +
  geom_boxplot(position=position_dodge(0.7), width=0.45,
               outlier.shape=NA, alpha=0.6,
               colour="grey30", linewidth=0.5) +
  geom_jitter(aes(colour=seed_type),
              position=position_jitterdodge(jitter.width=0.07,
                                             dodge.width=0.7),
              size=1.5, alpha=0.45) +
  stat_summary(fun=mean, geom="label",
               aes(label=sprintf("%.3f", after_stat(y))),
               position=position_dodge(0.7), size=2.3,
               fill="white", colour="grey20",
               label.size=0.15, label.padding=unit(0.12,"lines"),
               show.legend=FALSE) +
  scale_fill_manual(values=type_pal,   name="Seeding type") +
  scale_colour_manual(values=type_pal, name="Seeding type", guide="none") +
  facet_wrap(~scale) +
  labs(title="National (NC) vs facility-level (FTR) steady-state incidence by tier and seeding type",
       subtitle="NC = Network-central | FTR = Facility-type random | each dot = 1 replicate",
       x="Tier", y="Incidence (per 1,000 patient-days)") +
  theme_arc() +
  theme(legend.position="bottom")
```

## 4.4 Cumulative incidence (net_cumul_inc) over 732 days

```{r cumul-inc-box, fig.height=4.5}
ggplot(df_alive, aes(x=tier, y=net_cumulative_inc, fill=seed_type)) +
  geom_boxplot(position=position_dodge(0.7), width=0.45,
               outlier.shape=NA, alpha=0.6,
               colour="grey30", linewidth=0.5) +
  geom_jitter(aes(colour=seed_type),
              position=position_jitterdodge(jitter.width=0.07,
                                             dodge.width=0.7),
              size=1.5, alpha=0.45) +
  stat_summary(fun=mean, geom="label",
               aes(label=sprintf("%.3f", after_stat(y))),
               position=position_dodge(0.7), size=2.3,
               fill="white", colour="grey20",
               label.size=0.15, label.padding=unit(0.12,"lines"),
               show.legend=FALSE) +
  scale_fill_manual(values=type_pal,   name="Seeding type (NC / FTR)") +
  scale_colour_manual(values=type_pal, name="Seeding type", guide="none") +
  labs(title="Cumulative incidence (net_cumul_inc) over 732-day simulation",
       subtitle="Mean daily rate over ALL 732 days | per 1,000 patient-days | NC = Network-central | FTR = Facility-type random",
       x="Tier", y="net_cumul_inc (per 1,000 patient-days)") +
  theme_arc() +
  theme(legend.position="bottom")
```

---

# Part 5 - Prevalence (capped at 100%)

> **Note:** Network-level prevalence (net_ss_prev_pct) and facility-level prevalence (fac_ss_prev_mean_pct) values above 100% are a **simulation capacity overflow artefact**: inter-hospital transfers can temporarily exceed a hospital's bed capacity when multiple source hospitals simultaneously route patients to the same destination. All prevalence values are capped at 100% in displays below. Incidence metrics (Part 4) are not affected.

## 5.1 National prevalence (net_ss_prev_pct, capped) by seed rule

```{r net-prev-box, fig.height=5.5}
ggplot(df_alive, aes(x=reorder(seed_rule_short, net_ss_prev_capped),
                      y=net_ss_prev_capped, fill=tier)) +
  geom_boxplot(position=position_dodge(0.7), width=0.45,
               outlier.shape=NA, alpha=0.6,
               colour="grey30", linewidth=0.5) +
  geom_jitter(aes(colour=tier),
              position=position_jitterdodge(jitter.width=0.08,
                                             dodge.width=0.7),
              size=1.8, alpha=0.55) +
  scale_fill_manual(values=tier_pal,   name="Tier") +
  scale_colour_manual(values=tier_pal, name="Tier", guide="none") +
  scale_y_continuous(labels=function(x) paste0(x,"%"), limits=c(0,105)) +
  coord_flip() +
  labs(title="National prevalence (net_ss_prev_pct, capped at 100%) by seed rule",
       subtitle="sum(I_loc)/total_beds x 100 | last 30 days | bed-weighted | capped at 100%",
       x=NULL, y="net_ss_prev_pct (%)") +
  theme_arc()
```

## 5.2 Facility-level prevalence (fac_ss_prev_mean_pct, capped) by seed rule

```{r fac-prev-box, fig.height=5.5}
ggplot(df_alive, aes(x=reorder(seed_rule_short, fac_ss_prev_capped),
                      y=fac_ss_prev_capped, fill=tier)) +
  geom_boxplot(position=position_dodge(0.7), width=0.45,
               outlier.shape=NA, alpha=0.6,
               colour="grey30", linewidth=0.5) +
  geom_jitter(aes(colour=tier),
              position=position_jitterdodge(jitter.width=0.08,
                                             dodge.width=0.7),
              size=1.8, alpha=0.55) +
  scale_fill_manual(values=tier_pal,   name="Tier") +
  scale_colour_manual(values=tier_pal, name="Tier", guide="none") +
  scale_y_continuous(labels=function(x) paste0(x,"%"), limits=c(0,105)) +
  coord_flip() +
  labs(title="Facility-level prevalence (fac_ss_prev_mean_pct, capped at 100%) by seed rule",
       subtitle="mean[I_loc[h]/beds[h]] x 100 | last 30 days | unweighted across hospitals",
       x=NULL, y="fac_ss_prev_mean_pct (%)") +
  theme_arc()
```

---

# Part 6 - Epidemic trajectories

```{r traj-note, results='asis'}
if (!has_traj)
  cat("> Daily trajectories (traj_df) not available in compiled RDS - place RDS in COMPILED_DIR.\n")
```

```{r traj-prep, eval=has_traj}
# global_sim_id is the true unique key across local + cluster jobs.
# sim_id alone repeats across jobs (each job has sim_ids 1-120).
# Filter extinct reps using global_sim_id when available, otherwise
# use terminal net_inc == 0 as a fallback (safe for pi = 0 runs).

traj_raw_labelled <- traj_raw %>%
  mutate(
    tier = factor(tier, levels=c("Low","Moderate")),
    seed_type = factor(seed_type,
                       levels=c("fixed","type_random"),
                       labels=c("Network-central (NC)",
                                "Facility-type random (FTR)")),
    seed_rule_short = case_when(
      grepl("betweenness", seed_rule) ~ "Network hub",
      seed_rule == "random_MCO"       ~ "Random MCO",
      seed_rule == "random_SSR"       ~ "Random SSR",
      seed_rule == "random_MCO_SSR"   ~ "Random MCO/SSR",
      TRUE                            ~ seed_rule
    ),
    sim_key = paste0(tier,"_",seed_rule_short,"_",
                     if("source" %in% names(.)) source else "",
                     "_",rep_id)
  )

# Choose filtering strategy
if ("global_sim_id" %in% names(traj_raw_labelled) &&
    "global_sim_id" %in% names(df)) {
  extinct_ids <- df$global_sim_id[as.logical(df$ever_extinct)]
  traj <- traj_raw_labelled %>%
    filter(!global_sim_id %in% extinct_ids)
  message("Traj filter: global_sim_id | removed ",
          length(extinct_ids), " extinct IDs")
} else {
  # Fallback: identify extinct trajectories by terminal-day net_inc = 0
  Tmax_val_tmp <- max(traj_raw_labelled$day)
  extinct_sims <- traj_raw_labelled %>%
    filter(day == Tmax_val_tmp, net_inc == 0) %>%
    pull(sim_id) %>% unique()
  traj <- traj_raw_labelled %>%
    filter(!sim_id %in% extinct_sims)
  message("Traj filter: terminal net_inc == 0 | removed ",
          length(extinct_sims), " sim_ids")
}

message("Non-extinct traj rows: ", format(nrow(traj), big.mark=","),
        " | unique sims: ", n_distinct(
          if("global_sim_id" %in% names(traj)) traj$global_sim_id else traj$sim_id))

Tmax_val <- max(traj$day)
HALF_WIN  <- 15L    # split last 30 days into two 15-day halves

# =============================================================
# STEADY-STATE: window-to-window comparison
# Split the last 30 days into two equal 15-day windows.
# If mean incidence in the later window is within 5% of the
# earlier window, the epidemic has stabilised (SS reached).
#   pct_change = |mean(last 15) - mean(prev 15)| / mean(last 15) x 100
#   ss_reached = pct_change < 5
# All computation uses ONLY the last 30 days - no cumulative values.
# =============================================================

ss_key <- if ("global_sim_id" %in% names(traj)) "global_sim_id" else "sim_id"

ss_window <- traj %>%
  filter(day > Tmax_val - 30) %>%
  mutate(window = if_else(day > Tmax_val - HALF_WIN, "last15", "prev15")) %>%
  group_by(across(all_of(ss_key)), window) %>%
  summarise(mean_inc = mean(net_inc, na.rm=TRUE), .groups="drop") %>%
  tidyr::pivot_wider(names_from=window, values_from=mean_inc) %>%
  mutate(
    pct_change = if_else(
      !is.na(last15) & last15 > 0,
      abs(last15 - prev15) / last15 * 100,
      NA_real_),
    ss_reached = !is.na(pct_change) & pct_change < 5
  )

# Join back to df so summary table and overview use new SS definition
df <- df %>%
  select(-ss_reached) %>%   # drop NA placeholder from prep-seeding
  left_join(ss_window %>% select(all_of(ss_key), pct_change, ss_reached),
            by=ss_key) %>%
  mutate(ss_reached = coalesce(ss_reached, FALSE))
df_alive <- df %>% filter(!ever_extinct)

message(sprintf("SS (window-to-window <5%%): %d of %d non-extinct (%.1f%%)",
                sum(df_alive$ss_reached, na.rm=TRUE), nrow(df_alive),
                mean(df_alive$ss_reached, na.rm=TRUE)*100))

traj_stat <- traj %>%
  group_by(tier, seed_type, seed_rule_short, day) %>%
  summarise(
    mean_net_inc  = mean(net_inc,       na.rm=TRUE),
    lo_net_inc    = quantile(net_inc,   0.025, na.rm=TRUE),
    hi_net_inc    = quantile(net_inc,   0.975, na.rm=TRUE),
    mean_fac_inc  = mean(fac_inc_mean,  na.rm=TRUE),
    lo_fac_inc    = quantile(fac_inc_mean, 0.025, na.rm=TRUE),
    hi_fac_inc    = quantile(fac_inc_mean, 0.975, na.rm=TRUE),
    mean_net_prev = pmin(mean(net_prev_pct, na.rm=TRUE), 100),
    lo_net_prev   = pmin(quantile(net_prev_pct, 0.025, na.rm=TRUE), 100),
    hi_net_prev   = pmin(quantile(net_prev_pct, 0.975, na.rm=TRUE), 100),
    .groups="drop"
  )

ss_per_sim <- df %>%
  filter(!as.logical(ever_extinct)) %>%
  select(any_of(c("sim_id","global_sim_id","net_ss_inc",
                   "tier","seed_type","seed_rule"))) %>%
  mutate(seed_type=factor(seed_type,
                           levels=c("fixed","type_random"),
                           labels=c("Network-central (NC)",
                                    "Facility-type random (FTR)")),
         seed_rule_short=case_when(
           grepl("betweenness",seed_rule)~"Network hub",
           seed_rule=="random_MCO"~"Random MCO",
           seed_rule=="random_SSR"~"Random SSR",
           seed_rule=="random_MCO_SSR"~"Random MCO/SSR",
           TRUE~seed_rule))

# Join traj to ss incidence using best available key
join_key <- if ("global_sim_id" %in% names(traj) &&
                "global_sim_id" %in% names(ss_per_sim))
              "global_sim_id" else "sim_id"

ss_days_sim <- traj %>%
  left_join(ss_per_sim %>%
              select(all_of(join_key), net_ss_inc) %>%
              distinct(),
            by=join_key) %>%
  filter(!is.na(net_ss_inc), net_ss_inc > 0,
         net_inc >= 0.90 * net_ss_inc) %>%
  group_by(across(all_of(join_key))) %>%
  summarise(ss_day=min(day), .groups="drop")

ss_day_mean <- ss_per_sim %>%
  left_join(ss_days_sim, by=join_key) %>%
  group_by(tier, seed_type, seed_rule_short) %>%
  summarise(mean_ss_day = round(mean(ss_day, na.rm=TRUE)),
            pct_reached  = round(mean(!is.na(ss_day))*100, 1),
            .groups="drop")

n_sims_total <- n_distinct(
  if("global_sim_id" %in% names(traj)) traj$global_sim_id else traj$sim_id)
sim_id_col <- if("global_sim_id" %in% names(traj)) "global_sim_id" else "sim_id"
plot_ids <- if (n_sims_total > 200) sample(unique(traj[[sim_id_col]]), 200) else unique(traj[[sim_id_col]])
traj_sub <- traj %>% filter(.data[[sim_id_col]] %in% plot_ids)
```

## 6.1 National incidence trajectory (net_inc)

*Thin lines = individual replicates. Thick line = mean. Shaded = 95% CI. Vertical dashed = mean day reaching SS (90% of final level).*

```{r traj-net-inc, eval=has_traj, fig.height=8}
ggplot() +
  geom_line(data=traj_sub,
            aes(x=day,y=net_inc,group=sim_key,colour=seed_type),
            alpha=0.07, linewidth=0.2) +
  geom_ribbon(data=traj_stat,
              aes(x=day,ymin=lo_net_inc,ymax=hi_net_inc,fill=seed_type),
              alpha=0.2) +
  geom_line(data=traj_stat,
            aes(x=day,y=mean_net_inc,colour=seed_type),
            linewidth=1.3) +
  geom_vline(data=ss_day_mean,
             aes(xintercept=mean_ss_day,colour=seed_type),
             linetype="dashed",linewidth=0.7,alpha=0.8) +
  geom_label(data=ss_day_mean,
             aes(x=mean_ss_day, y=Inf,
                 label=paste0("d",mean_ss_day,"\n(",pct_reached,"%)"),
                 colour=seed_type),
             vjust=1.3, hjust=-0.05, size=2.2,
             fill="white", label.size=0, show.legend=FALSE) +
  scale_colour_manual(values=type_pal, name="Seeding type (NC/FTR)") +
  scale_fill_manual(values=type_pal,   name="Seeding type (NC/FTR)") +
  facet_grid(tier ~ seed_rule_short, scales="free_y") +
  labs(title="National incidence (net_inc) trajectory - non-extinct replicates",
       subtitle="Thin = individual sim | Thick = mean | Shaded = 95% CI | Dashed = mean day reaching 90% of SS level",
       x="Day", y="net_inc (per 1,000 patient-days)") +
  theme_arc(bs=10) +
  theme(legend.position="bottom", strip.text=element_text(size=8))
```

## 6.2 Facility-level incidence trajectory (fac_inc_mean)

```{r traj-fac-inc, eval=has_traj, fig.height=8}
ggplot() +
  geom_line(data=traj_sub,
            aes(x=day,y=fac_inc_mean,group=sim_key,colour=seed_type),
            alpha=0.07, linewidth=0.2) +
  geom_ribbon(data=traj_stat,
              aes(x=day,ymin=lo_fac_inc,ymax=hi_fac_inc,fill=seed_type),
              alpha=0.2) +
  geom_line(data=traj_stat,
            aes(x=day,y=mean_fac_inc,colour=seed_type),
            linewidth=1.3) +
  geom_vline(data=ss_day_mean,
             aes(xintercept=mean_ss_day,colour=seed_type),
             linetype="dashed",linewidth=0.7,alpha=0.8) +
  scale_colour_manual(values=type_pal, name="Seeding type (NC/FTR)") +
  scale_fill_manual(values=type_pal,   name="Seeding type (NC/FTR)") +
  facet_grid(tier ~ seed_rule_short, scales="free_y") +
  labs(title="Facility-level mean incidence (fac_inc_mean) trajectory - non-extinct replicates",
       subtitle="Unweighted mean across active hospitals | Thin = individual | Thick = mean | Shaded = 95% CI",
       x="Day", y="fac_inc_mean (per 1,000 patient-days)") +
  theme_arc(bs=10) +
  theme(legend.position="bottom", strip.text=element_text(size=8))
```

## 6.3 Steady-state day summary

```{r ss-table, eval=has_traj}
ss_day_mean %>% arrange(tier,seed_type) %>%
  kable(col.names=c("Tier","Seeding type","Seed rule",
                     "Mean SS day","% reps reached SS"),
        caption=paste0("Steady state (SS) day per simulation cell. ",
                        "SS = first day net_inc >= 90% of that replicate's net_ss_inc. ",
                        "NC = Network-central. FTR = Facility-type random. ",
                        "% reps reached SS = fraction of non-extinct replicates ",
                        "crossing the threshold before day ", Tmax_val, ".")) %>%
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE) %>%
  collapse_rows(columns=1:2, valign="top")
```

---

# Part 7 - Summary table

```{r summary-table}
tbl <- df %>%
  group_by(Tier=tier, `Seeding type`=seed_type,
           `Seed rule`=seed_rule_short) %>%
  summarise(
    N                        = n(),
    `Extinct (%)`            = paste0(round(mean(ever_extinct)*100,1),"%"),
    `SS reached (%)`         = paste0(round(mean(ss_reached,na.rm=TRUE)*100,1),"%"),
    `net_ss_inc\n/1k pd`     = sprintf("%.3f (%.3f)",
      mean(net_ss_inc[!ever_extinct],    na.rm=TRUE),
      sd(net_ss_inc[!ever_extinct],      na.rm=TRUE)),
    `fac_ss_inc_mean\n/1k pd`= sprintf("%.3f (%.3f)",
      mean(fac_ss_inc_mean[!ever_extinct], na.rm=TRUE),
      sd(fac_ss_inc_mean[!ever_extinct],   na.rm=TRUE)),
    `net_cumul_inc\n/1k pd`  = sprintf("%.3f (%.3f)",
      mean(net_cumulative_inc[!ever_extinct], na.rm=TRUE),
      sd(net_cumulative_inc[!ever_extinct],   na.rm=TRUE)),
    `net_ss_prev\n% (capped)`= sprintf("%.1f (%.1f)",
      mean(net_ss_prev_capped[!ever_extinct], na.rm=TRUE),
      sd(net_ss_prev_capped[!ever_extinct],   na.rm=TRUE)),
    .groups="drop"
  )

tbl %>%
  kable(caption=paste0(
    "Summary table. Mean (SD) across non-extinct replicates. ",
    "NC = Network-central. FTR = Facility-type random. ",
    "net_ss_inc = national bed-weighted SS incidence. ",
    "fac_ss_inc_mean = facility-level unweighted SS incidence. ",
    "net_cumul_inc = mean daily national incidence over 732 days. ",
    "net_ss_prev = national prevalence (capped at 100%). ",
    "/1k pd = per 1,000 patient-days. SS = last 30 days.")) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"),
                full_width=TRUE, font_size=11) %>%
  collapse_rows(columns=1:2, valign="top")
```

---



```{r abstract-stats, eval = FALSE, include=FALSE}
# Per-rule stats: mean and 95% CI (t-based)
ci95 <- function(x) {
  x <- x[!is.na(x)]
  if (length(x) < 2) return(c(NA_real_, NA_real_))
  se <- sd(x) / sqrt(length(x))
  t  <- qt(0.975, df=length(x)-1)
  round(c(mean(x) - t*se, mean(x) + t*se), 3)
}

# net_ss_inc by tier x seed_rule
inc_rule <- df_alive %>%
  group_by(tier, seed_rule_short) %>%
  summarise(
    n     = n(),
    mn    = round(mean(net_ss_inc), 3),
    ci_lo = ci95(net_ss_inc)[1],
    ci_hi = ci95(net_ss_inc)[2],
    .groups = "drop"
  )

# cumulative incidence by tier x seed_type
cum_type <- df_alive %>%
  group_by(tier, seed_type) %>%
  summarise(
    mn    = round(mean(net_cumulative_inc), 3),
    ci_lo = ci95(net_cumulative_inc)[1],
    ci_hi = ci95(net_cumulative_inc)[2],
    .groups = "drop"
  )

# extinction by tier x seed_rule
ext_rule <- df %>%
  group_by(tier, seed_rule_short) %>%
  summarise(pct = round(mean(ever_extinct)*100, 1), .groups="drop")

# helpers
get_inc <- function(t, r) inc_rule[inc_rule$tier==t & inc_rule$seed_rule_short==r, ]
get_cum <- function(t, s) cum_type[cum_type$tier==t & cum_type$seed_type==s, ]
get_ext <- function(t, r) ext_rule$pct[ext_rule$tier==t & ext_rule$seed_rule_short==r]

# Pre-fetch all rows used in abstract-para
nc_mod  <- get_inc("Moderate", "Network hub")
mco_mod <- get_inc("Moderate", "Random MCO")
ssr_mod <- get_inc("Moderate", "Random SSR")
msr_mod <- get_inc("Moderate", "Random MCO/SSR")
nc_low  <- get_inc("Low", "Network hub")
mco_low <- get_inc("Low", "Random MCO")
ssr_low <- get_inc("Low", "Random SSR")
msr_low <- get_inc("Low", "Random MCO/SSR")
cum_nc_mod  <- get_cum("Moderate", "Network-central (NC)")
cum_nc_low  <- get_cum("Low",      "Network-central (NC)")

calib_low <- if (has_calib && !is.null(calib$tier_analysis))
  calib$tier_analysis[calib$tier_analysis$tier=="Low",] else
  data.frame(mean_beta=0.055, ci_lo_95=0.030, ci_hi_95=0.080, mean_inc_ach=9.99)
calib_mod <- if (has_calib && !is.null(calib$tier_analysis))
  calib$tier_analysis[calib$tier_analysis$tier=="Moderate",] else
  data.frame(mean_beta=0.178, ci_lo_95=0.085, ci_hi_95=0.350, mean_inc_ach=19.97)
```

```{r abstract-para, results='asis', eval=FALSE, include=FALSE}
calib_low <- if (has_calib && !is.null(calib$tier_analysis))
  calib$tier_analysis[calib$tier_analysis$tier=="Low",] else
  data.frame(mean_beta=0.055, ci_lo_95=0.030, ci_hi_95=0.080)
calib_mod <- if (has_calib && !is.null(calib$tier_analysis))
  calib$tier_analysis[calib$tier_analysis$tier=="Moderate",] else
  data.frame(mean_beta=0.178, ci_lo_95=0.085, ci_hi_95=0.350)

cat(sprintf(
"**Abstract results paragraph:**

Calibration yielded a within-hospital transmission rate of %.3f/day
(95%% CI %.3f-%.3f) for the Low burden tier and %.3f/day
(95%% CI %.3f-%.3f) for the Moderate burden tier.
Among %d simulations of novel pathogen introduction (no community importation),
extinction was most common following introduction into a random acute care
hospital under the Low tier (%.1f%%) and least common following introduction
into a random rehabilitation hospital under the Moderate tier (%.1f%%).
Introduction site strongly influenced cumulative incidence over the 732-day
simulation window. Under the Moderate tier, introduction at the most highly
connected hospital in the network produced a mean cumulative incidence of
%.3f per 1,000 patient-days (pd) (95%% CI %.3f-%.3f), compared with
%.3f (95%% CI %.3f-%.3f) for random acute care, %.3f (95%% CI %.3f-%.3f)
for random rehabilitation, and %.3f (95%% CI %.3f-%.3f) for random
mixed-type introduction - a %.1f-fold difference between the highest and
lowest seeding sites. Under the Low tier, the corresponding values were
%.3f (95%% CI %.3f-%.3f) for network hub introduction versus
%.3f-%.3f per 1,000 pd across random introduction sites.
None of the non-extinct simulations reached epidemic steady state
within the observation window, indicating ongoing growth at day 732
across all introduction scenarios.",
  calib_low$mean_beta, calib_low$ci_lo_95, calib_low$ci_hi_95,
  calib_mod$mean_beta, calib_mod$ci_lo_95, calib_mod$ci_hi_95,
  nrow(df),
  get_ext("Low",      "Random MCO"),
  get_ext("Moderate", "Random SSR"),
  # Moderate cumulative
  cum_nc_mod$mn,  cum_nc_mod$ci_lo,  cum_nc_mod$ci_hi,
  mco_mod$mn, mco_mod$ci_lo, mco_mod$ci_hi,
  ssr_mod$mn, ssr_mod$ci_lo, ssr_mod$ci_hi,
  msr_mod$mn, msr_mod$ci_lo, msr_mod$ci_hi,
  round(nc_mod$mn / min(mco_mod$mn, ssr_mod$mn, msr_mod$mn), 1),
  # Low cumulative
  cum_nc_low$mn,  cum_nc_low$ci_lo,  cum_nc_low$ci_hi,
  min(mco_low$mn, ssr_low$mn, msr_low$mn),
  max(mco_low$mn, ssr_low$mn, msr_low$mn)
))
```




---

# Part 9 - Export

```{r export}
report_df <- df %>%
  group_by(tier, seed_type, seed_rule=seed_rule_short) %>%
  summarise(
    n_total=n(), n_alive=sum(!ever_extinct),
    pct_extinct         =round(mean(ever_extinct)*100,1),
    pct_ss_reached      =round(mean(ss_reached,na.rm=TRUE)*100,1),
    mean_net_ss_inc     =round(mean(net_ss_inc[!ever_extinct],na.rm=TRUE),4),
    sd_net_ss_inc       =round(sd(net_ss_inc[!ever_extinct],na.rm=TRUE),4),
    mean_fac_ss_inc     =round(mean(fac_ss_inc_mean[!ever_extinct],na.rm=TRUE),4),
    sd_fac_ss_inc       =round(sd(fac_ss_inc_mean[!ever_extinct],na.rm=TRUE),4),
    mean_net_cumul_inc  =round(mean(net_cumulative_inc[!ever_extinct],na.rm=TRUE),4),
    sd_net_cumul_inc    =round(sd(net_cumulative_inc[!ever_extinct],na.rm=TRUE),4),
    mean_net_prev_capped=round(mean(net_ss_prev_capped[!ever_extinct],na.rm=TRUE),2),
    sd_net_prev_capped  =round(sd(net_ss_prev_capped[!ever_extinct],na.rm=TRUE),2),
    .groups="drop"
  )

write.csv(report_df, file.path(OUT_DIR,"seeding_novel_report_table.csv"),
          row.names=FALSE)
report_df %>%
  kable(caption="Saved to seeding_novel_report_table.csv") %>%
  kable_styling(bootstrap_options=c("striped","condensed"),
                full_width=TRUE, font_size=10)
```

---

*`r format(Sys.time(),"%Y-%m-%d %H:%M")` | Sims: `r nrow(df)` | Non-extinct: `r nrow(df_alive)` (`r round((1-mean(df$ever_extinct))*100,1)`%) | SS: `r sum(df_alive$ss_reached,na.rm=TRUE)` of `r nrow(df_alive)` | Traj: `r if(has_traj) format(nrow(traj_raw),big.mark=",") else "not loaded"`*
