---
title: "ARCANE — Seeding Simulation Analysis"
subtitle: "Facility-level prevalence, network prevalence, and cumulative incidence by tier and seeding location"
author: "MESuRS/Cnam"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    code_folding: hide
    fig_width: 10
    fig_height: 5.5
  powerpoint_presentation:
    slide_level: 2
    fig_width: 10
    fig_height: 5.2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, dpi=150)
```

```{r libraries}
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(scales)

# =============================================================================
# PATH CONFIGURATION
# =============================================================================
# Switch DATA_SOURCE between "local" and "cluster" to change input.
# The Rmd loads the CSV summary for prevalence metrics (always available)
# and the full RDS for daily incidence data (if available).

DATA_SOURCE <- "cluster"   # change to "cluster" for cluster results

paths <- list(
  local   = "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/calibration_jobs/Outputs/seeding_novel",
  cluster = "C:/Users/octariar/OneDrive - LECNAM/Documents/GitHub/arcane-temporal-network-new/calibration_jobs/Outputs/seeding_novel"
)
DATA_DIR <- paths[[DATA_SOURCE]]
OUT_DIR  <- file.path(DATA_DIR, "analysis")
dir.create(OUT_DIR, recursive=TRUE, showWarnings=FALSE)

# ── Load summary (CSV — always available) ─────────────────────────────────────
csv_file <- list.files(DATA_DIR, "seeding_summary.*\\.csv$", full.names=TRUE)
rds_file <- list.files(DATA_DIR, "seeding_results.*\\.rds$",  full.names=TRUE)


# Replace the csv_file / rds_file / loading block with:

job_dirs <- list.dirs(DATA_DIR, full.names=TRUE, recursive=FALSE)
job_dirs <- job_dirs[grepl("job_\\d+$", basename(job_dirs))]

if (length(job_dirs) == 0)
  stop("No job_XX folders found in: ", DATA_DIR)

message("Found ", length(job_dirs), " job folders — pooling results...")

df_raw <- bind_rows(lapply(job_dirs, function(jdir) {
  # Try CSV first, fall back to RDS
  csv_f <- list.files(jdir, "seeding_summary.*\\.csv$", full.names=TRUE)
  rds_f <- list.files(jdir, "seeding_results.*\\.rds$",  full.names=TRUE)

  if (length(csv_f) > 0) {
    read.csv(tail(sort(csv_f), 1), stringsAsFactors=FALSE) %>% 
      mutate(seed_hospital = as.character(seed_hospital))
  } else if (length(rds_f) > 0) {
    readRDS(tail(sort(rds_f), 1))$sim_summary
  } else {
    message("  No results in: ", basename(jdir), " — skipping")
    NULL
  }
}))

message("Total simulations pooled: ", nrow(df_raw))

# ── Load daily trajectory (RDS — needed for incidence metrics) ────────────────
has_daily <- length(rds_file) > 0
if (has_daily) {
  res      <- readRDS(tail(sort(rds_file), 1))
  daily_df <- res$all_results   # one row per (sim_id, day)
  message("Daily trajectory loaded: ", format(nrow(daily_df), big.mark=","),
          " rows")
} else {
  message("RDS not found — incidence metrics will not be available.")
  daily_df <- NULL
}

message("Summary rows: ", nrow(df_raw), " | Source: ", DATA_SOURCE)
```

```{r prep-summary}
# =============================================================================
# PREPARE SUMMARY DATASET
# =============================================================================

df <- df_raw %>%
  mutate(
    tier = factor(tier, levels=c("Low","Mid","High")),
    seed_type = factor(seed_type,
                       levels = c("fixed","type_random"),
                       labels = c("Network-central","Facility-type random")),
    seed_rule_short = case_when(
      grepl("betweenness", seed_rule) ~ "Network hub",
      seed_rule == "random_MCO"       ~ "Random MCO",
      seed_rule == "random_SSR"       ~ "Random SSR",
      seed_rule == "random_MCO_SSR"   ~ "Random MCO/SSR",
      TRUE                            ~ seed_rule
    ),
    ever_extinct        = as.logical(ever_extinct),
    # Network-level SS prevalence is final_prevalence (day 365)
    net_prev_ss_pct     = net_final_prev_pct# * 100
  )

tier_pal  <- c(Low="#009E73", Mid="#E69F00", High="#D55E00")
type_pal  <- c(`Network-central`="#0057B8",
               `Facility-type random`="#C1392B")

theme_arc <- function(bs=12)
  theme_bw(base_size=bs) +
  theme(plot.title      = element_text(face="bold"),
        plot.subtitle   = element_text(colour="grey40"),
        panel.grid.minor= element_blank(),
        legend.position = "right",
        strip.background= element_rect(fill="grey92"),
        strip.text      = element_text(face="bold"))
```

```{r prep-daily}
# =============================================================================
# COMPUTE INCIDENCE METRICS FROM DAILY TRAJECTORY
# =============================================================================
# incidence_daily in all_results = sum(new_inf) / sum(occupied beds) x 1000
# (per 1,000 patient-days, for each day of the simulation)
#
# From this we derive:
#   cumulative_inc     = mean daily incidence rate over all Tmax days
#                        (approximates overall attack rate per 1,000 pd)
#   ss_inc_last30      = mean daily incidence in last 30 days
#                        (steady-state incidence, comparable to surveillance)
#
# NOTE: cumulative_inc is computed as mean(daily_rate) across all days,
#       which approximates sum(new_inf) / sum(pt_days) x 1000 well when
#       occupancy is roughly stable.
# =============================================================================

if (has_daily) {
  Tmax_obs <- max(daily_df$day)

  inc_summary <- daily_df %>%
    group_by(sim_id, seed_rule, seed_type, tier, rep_id, seed_hospital) %>%
    summarise(
      # Cumulative incidence: mean daily rate across ALL days
      cumulative_inc_1k = mean(incidence_daily, na.rm=TRUE),
      # Steady-state incidence: mean daily rate in LAST 30 days
      ss_inc_last30_1k  = mean(incidence_daily[day >= (Tmax_obs - 29)],
                                na.rm=TRUE),
      # Facility-level mean prevalence:
      # mean(overall_prevalence) in last 30 days as proxy for SS prevalence
      # NOTE: overall_prevalence = sum(I_loc)/total_beds (network-weighted).
      # True facility-level unweighted mean (mean of I_loc[h]/beds[h])
      # requires per-hospital data not saved in the current daily output.
      # This is the bed-weighted network equivalent.
      net_prev_ss_last30_pct = mean(overall_prevalence[
        day >= (Tmax_obs - 29)], na.rm=TRUE) * 100,
      .groups = "drop"
    ) %>%
    mutate(
      tier      = factor(tier, levels=c("Low","Mid","High")),
      seed_type = factor(seed_type,
                         levels=c("fixed","type_random"),
                         labels=c("Network-central","Facility-type random")),
      seed_rule_short = case_when(
        grepl("betweenness", seed_rule) ~ "Network hub",
        seed_rule == "random_MCO"       ~ "Random MCO",
        seed_rule == "random_SSR"       ~ "Random SSR",
        seed_rule == "random_MCO_SSR"   ~ "Random MCO/SSR",
        TRUE                            ~ seed_rule
      )
    )

  # Join incidence metrics back to summary
  df <- df %>%
    left_join(inc_summary %>%
                select(sim_id, cumulative_inc_1k,
                       ss_inc_last30_1k, net_prev_ss_last30_pct),
              by="sim_id")
}
```

---

# Statistical definitions

Three primary outcome metrics, each defined precisely below.

```{r stat-defs}
tibble::tribble(
  ~Metric, ~`Exact definition`, ~Unit, ~`Aggregation in tables/plots`,
  "Network-level steady-state prevalence",
    "sum(I_loc) / total_beds across all 2,519 hospitals on day 365 (final simulation day). Bed-weighted: larger hospitals contribute proportionally more. Reported as %.",
    "% of total beds",
    "Mean (SD) across replicates per seed rule x tier",

  "Cumulative incidence",
    "Mean of daily incidence rates across all Tmax days, where daily rate = sum(new_inf) / sum(occupied beds) x 1000. Approximates total attack rate per 1,000 patient-days over the simulation period. Requires RDS (daily trajectory).",
    "per 1,000 patient-days",
    "Mean (SD) across replicates per seed rule x tier",

  "Steady-state incidence (last 30 days)",
    "Mean daily incidence rate [sum(new_inf)/sum(occupied_beds) x 1000] over the last 30 days of the simulation. Represents the endemic incidence level once the epidemic has stabilised. Requires RDS.",
    "per 1,000 patient-days",
    "Mean (SD) across replicates per seed rule x tier",

  "Note on facility-level prevalence",
    "True facility-level mean prevalence = mean(I_loc[h]/beds[h]) across hospitals h, giving equal weight to all facilities regardless of size. This differs from network-level prevalence (bed-weighted). Requires per-hospital daily data not currently saved in the daily output; planned for next simulation version.",
    "—",
    "—"
) %>%
  kable(caption="Primary outcome metric definitions") %>%
  kable_styling(bootstrap_options=c("striped","hover"), full_width=TRUE) %>%
  column_spec(1, bold=TRUE) %>%
  column_spec(2, width="45%") %>%
  row_spec(4, background="#fff3cd")
```

---

# Overview

```{r overview, results='asis'}
cat(sprintf(
  "**Source:** %s &nbsp;|&nbsp; **Simulations:** %d &nbsp;|&nbsp;
   **Tiers:** %s &nbsp;|&nbsp; **Seed rules:** %d &nbsp;|&nbsp;
   **Reps per cell:** %d &nbsp;|&nbsp; **Daily RDS available:** %s",
  DATA_SOURCE, nrow(df),
  paste(levels(df$tier), collapse=" / "),
  n_distinct(df$seed_rule),
  max(df$rep_id),
  if(has_daily) "Yes" else "No — incidence plots omitted"
))
```

---

# Part 1 — Network-level steady-state prevalence

*Computed from `final_prevalence` = sum(I_loc) / total beds on day 365.
Bed-weighted: large hospitals dominate this average.*

## 1.1 By tier

```{r prev-by-tier}
ggplot(df, aes(x=tier, y=net_prev_ss_pct, fill=tier)) +
  geom_violin(alpha=0.65, trim=TRUE, scale="width") +
  geom_boxplot(width=0.12, outlier.shape=NA,
               fill="white", colour="grey30", linewidth=0.7) +
  geom_jitter(aes(colour=seed_type), width=0.12, size=2, alpha=0.7) +
  scale_fill_manual(values=tier_pal, guide="none") +
  scale_colour_manual(values=type_pal, name="Seeding type") +
  scale_y_continuous(labels=function(x) paste0(x,"%")) +
  labs(title="Network-level steady-state prevalence by tier (day 365)",
       subtitle="sum(I_loc) / total_beds | Bed-weighted | Dots coloured by seeding type",
       x="Tier", y="Prevalence (%)") +
  theme_arc()
```

## 1.2 By tier and seeding type

```{r prev-tier-type}
df %>%
  group_by(tier, seed_type) %>%
  summarise(mn=mean(net_prev_ss_pct),
            sd=sd(net_prev_ss_pct), .groups="drop") %>%
  ggplot(aes(x=tier, y=mn, fill=seed_type)) +
  geom_col(position=position_dodge(0.7), width=0.6, alpha=0.88) +
  geom_errorbar(aes(ymin=mn-sd, ymax=mn+sd),
                position=position_dodge(0.7),
                width=0.25, linewidth=0.8) +
  scale_fill_manual(values=type_pal, name="Seeding type") +
  scale_y_continuous(labels=function(x) paste0(x,"%")) +
  labs(title="Mean network prevalence by tier and seeding type (day 365)",
       subtitle="Mean +/-1 SD across replicates",
       x="Tier", y="Prevalence (%)") +
  theme_arc()
```

## 1.3 By seed rule and tier

```{r prev-rule-tier, fig.height=6}
df %>%
  group_by(tier, seed_rule_short) %>%
  summarise(mn=mean(net_prev_ss_pct),
            sd=sd(net_prev_ss_pct), .groups="drop") %>%
  ggplot(aes(x=reorder(seed_rule_short, mn),
             y=mn, fill=tier)) +
  geom_col(position=position_dodge(0.7), width=0.6, alpha=0.88) +
  geom_errorbar(aes(ymin=mn-sd, ymax=mn+sd),
                position=position_dodge(0.7),
                width=0.25, linewidth=0.7) +
  scale_fill_manual(values=tier_pal, name="Tier") +
  scale_y_continuous(labels=function(x) paste0(x,"%")) +
  coord_flip() +
  labs(title="Mean network prevalence by seed rule and tier",
       subtitle="Mean +/-1 SD | Sorted by mean across tiers",
       x=NULL, y="Prevalence (%)") +
  theme_arc()
```

---

# Part 2 — Cumulative incidence

```{r check-daily, results='asis'}
if (!has_daily) {
  cat("> **RDS file not available — cumulative incidence charts skipped.**\n",
      "> Re-run with the RDS file in the output folder to enable these sections.")
  knitr::knit_exit()
}
```

*Mean daily incidence rate across all `r if(has_daily) Tmax_obs else "?"` days,
where daily rate = sum(new infections) / sum(occupied beds) × 1,000.
This approximates the overall attack rate per 1,000 patient-days.*

## 2.1 By tier

```{r cum-inc-tier}
ggplot(df, aes(x=tier, y=cumulative_inc_1k, fill=tier)) +
  geom_violin(alpha=0.65, trim=TRUE, scale="width") +
  geom_boxplot(width=0.12, outlier.shape=NA,
               fill="white", colour="grey30", linewidth=0.7) +
  geom_jitter(aes(colour=seed_type), width=0.12, size=2, alpha=0.7) +
  scale_fill_manual(values=tier_pal, guide="none") +
  scale_colour_manual(values=type_pal, name="Seeding type") +
  labs(title="Cumulative incidence by tier",
       subtitle="Mean daily rate across all simulation days | per 1,000 patient-days",
       x="Tier", y="Incidence (per 1,000 patient-days)") +
  theme_arc()
```

## 2.2 By tier and seeding type

```{r cum-inc-type}
df %>%
  group_by(tier, seed_type) %>%
  summarise(mn=mean(cumulative_inc_1k),
            sd=sd(cumulative_inc_1k), .groups="drop") %>%
  ggplot(aes(x=tier, y=mn, fill=seed_type)) +
  geom_col(position=position_dodge(0.7), width=0.6, alpha=0.88) +
  geom_errorbar(aes(ymin=mn-sd, ymax=mn+sd),
                position=position_dodge(0.7),
                width=0.25, linewidth=0.8) +
  scale_fill_manual(values=type_pal, name="Seeding type") +
  labs(title="Mean cumulative incidence by tier and seeding type",
       subtitle="Mean +/-1 SD across replicates | per 1,000 patient-days",
       x="Tier", y="Incidence (per 1,000 patient-days)") +
  theme_arc()
```

## 2.3 By seed rule and tier

```{r cum-inc-rule, fig.height=6}
df %>%
  group_by(tier, seed_rule_short) %>%
  summarise(mn=mean(cumulative_inc_1k),
            sd=sd(cumulative_inc_1k), .groups="drop") %>%
  ggplot(aes(x=reorder(seed_rule_short, mn), y=mn, fill=tier)) +
  geom_col(position=position_dodge(0.7), width=0.6, alpha=0.88) +
  geom_errorbar(aes(ymin=mn-sd, ymax=mn+sd),
                position=position_dodge(0.7),
                width=0.25, linewidth=0.7) +
  scale_fill_manual(values=tier_pal, name="Tier") +
  coord_flip() +
  labs(title="Mean cumulative incidence by seed rule and tier",
       subtitle="Mean +/-1 SD | per 1,000 patient-days",
       x=NULL, y="Incidence (per 1,000 patient-days)") +
  theme_arc()
```

---

# Part 3 — Steady-state incidence (last 30 days)

*Mean daily incidence rate in the last 30 days of the simulation.
Represents endemic incidence once the epidemic has stabilised —
directly comparable to SPARES and ECDC HAI surveillance rates.*

## 3.1 By tier and seeding type

```{r ss-inc-type}
ggplot(df, aes(x=tier, y=ss_inc_last30_1k, fill=seed_type)) +
  geom_violin(position=position_dodge(0.8),
              alpha=0.65, trim=TRUE, scale="width") +
  geom_boxplot(position=position_dodge(0.8), width=0.1,
               outlier.shape=NA, fill="white",
               colour="grey30", linewidth=0.6) +
  scale_fill_manual(values=type_pal, name="Seeding type") +
  labs(title="Steady-state incidence by tier and seeding type",
       subtitle="Mean daily rate in last 30 days | per 1,000 patient-days",
       x="Tier", y="Incidence (per 1,000 patient-days)") +
  theme_arc()
```

## 3.2 By seed rule and tier

```{r ss-inc-rule, fig.height=6}
df %>%
  group_by(tier, seed_rule_short) %>%
  summarise(mn=mean(ss_inc_last30_1k),
            sd=sd(ss_inc_last30_1k), .groups="drop") %>%
  ggplot(aes(x=reorder(seed_rule_short, mn), y=mn, fill=tier)) +
  geom_col(position=position_dodge(0.7), width=0.6, alpha=0.88) +
  geom_errorbar(aes(ymin=mn-sd, ymax=mn+sd),
                position=position_dodge(0.7),
                width=0.25, linewidth=0.7) +
  scale_fill_manual(values=tier_pal, name="Tier") +
  coord_flip() +
  labs(title="Steady-state incidence by seed rule and tier",
       subtitle="Mean +/-1 SD | Last 30 days | per 1,000 patient-days",
       x=NULL, y="Incidence (per 1,000 patient-days)") +
  theme_arc()
```

---

# Part 4 — Combined summary table

*Each cell = mean (SD) across replicates.
Primary metrics: network-level prevalence, cumulative incidence, steady-state incidence.*

```{r summary-table}
tbl <- df %>%
  group_by(Tier=tier, `Seed type`=seed_type, `Seed rule`=seed_rule_short) %>%
  summarise(
    N = n(),
    `Net. prevalence\n% mean (SD)` = sprintf("%.1f (%.1f)",
      mean(net_prev_ss_pct), sd(net_prev_ss_pct)),
    `Cumulative inc.\n/1k pd mean (SD)` = if(has_daily)
      sprintf("%.3f (%.3f)", mean(cumulative_inc_1k), sd(cumulative_inc_1k))
      else "—",
    `SS incidence\n/1k pd mean (SD)` = if(has_daily)
      sprintf("%.3f (%.3f)", mean(ss_inc_last30_1k), sd(ss_inc_last30_1k))
      else "—",
    `Extinct\n(%)` = paste0(round(mean(ever_extinct)*100), "%"),
    .groups="drop"
  )

cap <- paste0(
  "Summary outcomes by tier, seeding type, and seed rule. ",
  "N = replicates per cell. ",
  "Net. prevalence = sum(I_loc)/total_beds x 100 on day 365 (bed-weighted). ",
  "Cumulative inc. = mean daily incidence rate across all simulation days ",
  "per 1,000 patient-days. ",
  "SS incidence = mean daily incidence in last 30 simulation days per 1,000 ",
  "patient-days. ",
  "Extinct = % of replicates where pathogen went extinct."
)

tbl %>%
  kable(caption=cap) %>%
  kable_styling(bootstrap_options=c("striped","hover","condensed"),
                full_width=TRUE, font_size=11) %>%
  collapse_rows(columns=1:2, valign="top")
```

---

# Part 5 — Abstract results paragraph

```{r abstract-stats}
a <- df %>%
  group_by(tier, seed_type) %>%
  summarise(
    mn_prev  = round(mean(net_prev_ss_pct), 1),
    sd_prev  = round(sd(net_prev_ss_pct),   1),
    mn_cinc  = if(has_daily) round(mean(cumulative_inc_1k), 3) else NA,
    sd_cinc  = if(has_daily) round(sd(cumulative_inc_1k),   3) else NA,
    mn_ssinc = if(has_daily) round(mean(ss_inc_last30_1k),  3) else NA,
    sd_ssinc = if(has_daily) round(sd(ss_inc_last30_1k),    3) else NA,
    .groups="drop"
  )

get <- function(t, s, col)
  a[[col]][a$tier==t & a$seed_type==s]

# Fold differences in SS prevalence
fold_low <- round(get("Low","Network-central","mn_prev") /
                    get("Low","Facility-type random","mn_prev"), 2)
fold_mid <- round(get("Mid","Network-central","mn_prev") /
                    get("Mid","Facility-type random","mn_prev"), 2)
```

```{r abstract-para, results='asis'}
cat(sprintf(
"**Suggested abstract results paragraph:**

Seeding simulations revealed that transmissibility tier and introduction
location jointly determined outbreak magnitude. Under the Low transmissibility
scenario, network-central seeding produced a mean network-wide steady-state
prevalence of %.1f%% (SD %.1f%%) at day 365, compared with %.1f%% (SD %.1f%%)
for random facility-type seeding (%sx higher). Under the Mid tier, network-central
introduction reached %.1f%% (SD %.1f%%) versus %.1f%% (SD %.1f%%) for random
seeding (%sx higher). Under the High tier (extrapolated beta), network-central
seeding produced a prevalence of %.1f%% (SD %.1f%%).%s
No pathogen extinction was observed across any tier or seed rule during the
365-day window, confirming that the combination of within-hospital transmission
and inter-hospital transfer dynamics was sufficient to sustain ARB spread
under all tested scenarios.",
  get("Low","Network-central","mn_prev"),
  get("Low","Network-central","sd_prev"),
  get("Low","Facility-type random","mn_prev"),
  get("Low","Facility-type random","sd_prev"),
  fold_low,
  get("Mid","Network-central","mn_prev"),
  get("Mid","Network-central","sd_prev"),
  get("Mid","Facility-type random","mn_prev"),
  get("Mid","Facility-type random","sd_prev"),
  fold_mid,
  get("High","Network-central","mn_prev"),
  get("High","Network-central","sd_prev"),
  if(has_daily) sprintf(
    " Cumulative incidence under the Mid tier reached %.3f (SD %.3f) per
1,000 patient-days for network-central seeding versus %.3f (SD %.3f) for
random seeding. Steady-state incidence in the last 30 days of the simulation
was %.3f (SD %.3f) per 1,000 patient-days under Mid-tier network-central seeding,
consistent with ESBL-E surveillance rates in Western European acute care settings.",
    get("Mid","Network-central","mn_cinc"),
    get("Mid","Network-central","sd_cinc"),
    get("Mid","Facility-type random","mn_cinc"),
    get("Mid","Facility-type random","sd_cinc"),
    get("Mid","Network-central","mn_ssinc"),
    get("Mid","Network-central","sd_ssinc")
  ) else ""
))
```

---

# Part 6 — Export reportable dataset

```{r export}
report_df <- df %>%
  group_by(tier, seed_type, seed_rule=seed_rule_short) %>%
  summarise(
    n_reps                  = n(),
    mean_beta               = round(mean(mean_beta), 6),
    ci_lo_95                = round(mean(ci_lo_95),  6),
    ci_hi_95                = round(mean(ci_hi_95),  6),
    beta_source             = first(source),
    # Primary outcomes
    mean_net_prev_pct       = round(mean(net_prev_ss_pct), 2),
    sd_net_prev_pct         = round(sd(net_prev_ss_pct),   2),
    mean_cumulative_inc_1k  = if(has_daily) round(mean(cumulative_inc_1k),4) else NA,
    sd_cumulative_inc_1k    = if(has_daily) round(sd(cumulative_inc_1k),  4) else NA,
    mean_ss_inc_last30_1k   = if(has_daily) round(mean(ss_inc_last30_1k), 4) else NA,
    sd_ss_inc_last30_1k     = if(has_daily) round(sd(ss_inc_last30_1k),   4) else NA,
    pct_extinct             = round(mean(ever_extinct)*100, 1),
    .groups="drop"
  ) %>%
  arrange(tier, seed_type, seed_rule)

write.csv(report_df,
          file.path(OUT_DIR, "seeding_report_table.csv"),
          row.names=FALSE)

report_df %>%
  kable(caption=paste0(
    "Exportable reportable dataset — saved to seeding_report_table.csv. ",
    "All prevalences in %. ",
    "Incidence metrics in per 1,000 patient-days."
  )) %>%
  kable_styling(bootstrap_options=c("striped","condensed"),
                full_width=TRUE, font_size=10)
```

---

*Analysis: `r format(Sys.time(),"%Y-%m-%d %H:%M")` | Source: `r DATA_SOURCE` |
n = `r nrow(df)` simulations | Daily RDS: `r if(has_daily) "loaded" else "not available"`*
